### 2021-05-26 memo.tex
Update on Overleaf.

\RequirePackage[T1]{fontenc}
\documentclass[12pt]{article}

\usepackage[height=8.85in,width=6.45in]{geometry}
%\usepackage{showkeys}
\renewcommand{\baselinestretch}{1.08}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\numberwithin{equation}{section}
\usepackage{slashed}
\usepackage{braket}
\usepackage[svgnames]{xcolor}
\usepackage[colorlinks,citecolor=DarkGreen,linkcolor=FireBrick,urlcolor=FireBrick,linktocpage,unicode]{hyperref}
\urlstyle{rm}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{times}
\usepackage{courier}
\usepackage{bm}
\usepackage{subfig}

\usepackage{xcolor}
\usepackage{mdframed}
\newenvironment{claim}{  \begin{mdframed}[linecolor=black!0,backgroundcolor=black!10]\noindent\itshape\ignorespaces}{\end{mdframed}}

\let\originalfigure=\figure
\let\endoriginalfigure=\endfigure

\renewenvironment{figure}[1][]{
  \begin{originalfigure}[#1]
    \begin{mdframed}[linecolor=black!0,backgroundcolor=black!1]
}{
    \end{mdframed}
  \end{originalfigure}
}
%% Comment
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}

%% Yuji's macros
%%list ???
\begin{document}

\if0
\begin{titlepage}

\begin{flushright}
IPMU-18-????
\end{flushright}

\vskip 3cm

\begin{center}

{\Large \bfseries Title}

\vskip 1cm
Yuji Tachikawa and friends
\vskip 1cm

\begin{tabular}{ll}
 & Kavli Institute for the Physics and Mathematics of the Universe, \\
& University of Tokyo,  Kashiwa, Chiba 277-8583, Japan
\end{tabular}

\vskip 1cm

\end{center}

\noindent
Abstract comes here.

\end{titlepage}

\setcounter{tocdepth}{2}
\tableofcontents

\newpage

\fi

\bibliographystyle{ytphys}
\baselineskip=.95\baselineskip
\bibliography{ref}

\end{document}

### 2021-05-26 memo.tex
initial commit

@@
 %% Yuji's macros
-%%list ???
+%%list SeibergDual
+
+\def\bZ{\mathbb{Z}}
+\def\diag{\mathop{\mathrm{diag}}}
+
 \begin{document}
@@
 
+This file is to collect various notes on our project on the higher symmetry and Seiberg duality.
+
+\section{Explicit configurations detecting anomalies}
+
+Here we describe geometries detecting $\int_{M_5} B\beta E$, $\int_{M_4} B\beta w_2$, etc.
+All cohomologies in this section is $\bZ_2$-valued.
+
+\paragraph{Klein bottle:}
+
+We start from the Klein bottle $K$ as a nontrivial $S^1$ bundle over $S^1$.
+Let us denote by $a$ the Poincar\'e dual to the fiber $S^1$,
+and $t$ the Poincar\'e dual to the base $S^1$.
+
+We have $\beta a=ta$, since $\int_K \beta a = \int_K w_1 a$.
+
+\paragraph{$T^4$ bundle over $S^1$:}
+
+We now consider a $T^4$ bundle over $S^1$. 
+We denote four directions of $T^4$ as $1$, $2$, $3$ and $4$,
+and we let the directions $1$ and $3$ to flip the orientation when we go around $S^1$.
+We let $a_{1,2,3,4}\in H^1(T^4)$ be the dual basis to the $S^1$ along four directions.
+
+We now take $B=a_1a_2$ and $E=a_3 a_4$.
+Then $\beta B=tB$ and $\beta E=tE$, and $\int B\beta E=1$.
+
+\paragraph{Realizing as $SO(3)$ bundles}
+
+We now look for $SO(3)$ bundles realizing these $B$ and $E$ as $w_2$ in this $T^4$ bundle over $S^1$.
+
+We note that an $SO(3)$ bundle over $T^2$ with two commuting holonomies around two directions \[
+R_x = \diag(+1,-1,-1),\qquad
+R_y = \diag(+1,-1,-1)
+\] has a nontrivial $w_2$, since their lift to $SU(2)$ is given by $i\sigma_x$ and $i\sigma_y$ which anticommute.
+
+Luckily, these $R_x$ and $R_y$ are of order two, so we can put it over our $T^4$ bundle. Done.
+
+\section{Anomaly of trifundamental}
+
+Lee-kun's computation says that \[
+(D\Omega^\text{spin})^6 (B[SU(2)^3/\bZ_2^2]) = \bZ_2 
+\] generated by \[
+\int w_2 \beta w_2'.
+\]
+
+We would like to know if a trifundamental fermion has this anomaly.
+
+To see this, we need to compute the eta invariant under an explicit configuration where $\int w_2 \beta w_2'=1$. 
+Such a configuration is constructed above. 
+Let us first find an explicit configuration of $SU(2)^{(1)}\times SU(2)^{(2)} \times SU(2)^{(3)}$ commuting up to $\bZ_2\times \bZ_2$, which is generated by $(-1,-1,+1)$ and $(-1,+1,-1)$.
+So we just have to choose, say, \begin{align}
+\text{holonomy around direction 1} &= (i\sigma_x, i\sigma_x, 1), \\
+\text{holonomy around direction 2} &= (i\sigma_y, i\sigma_y, 1), \\
+\text{holonomy around direction 3} &= (i\sigma_x, 1,i\sigma_x), \\
+\text{holonomy around direction 4} &= (i\sigma_y, 1,i\sigma_y).
+\end{align}
+
+Furthermore, the spinor on our $T^4$ bundle over $S^1$ is glued around $S^1$ via the action of $\Gamma_1\Gamma_3$, 
+since we flip the directions $1$ and $3$.
+
+These are enough data to construct the fermion bundle over our $T^4$ bundle over $S^1$. 
+Since the Euclidean spinor in 5d is pseudoreal, and our trifundamental is also pseudoreal,
+the tensor product is strictly real.
+The Dirac operator is therefore a real antisymmetric matrix, and the eigenvalues come in pairs $\pm \lambda$
+except the zero modes.
+Therefore in our case the eta invariant reduces to the mod-2 index,
+and we just have to count the zero modes.
+
 \bibliographystyle{ytphys}

### 2021-05-27 memo.tex
bordism computation pasted

@@
 \usepackage{subfig}
+\usepackage{ascmac}
+\usepackage{spectralsequences}
+\usepackage{dashbox}
+
+\DeclareSseqGroup\tower {} {
+	\class(0,0)\foreach \i in {1,...,8} {
+		\class(0,\i)
+		\structline(0,\i-1,-1)(0,\i,-1)
+	}
+}
 
 \usepackage{xcolor}
+\usepackage{colortbl}
+\usepackage{arydshln}
+\definecolor{lightyellow}{rgb}{1.0, 0.95, 0.7}
+\definecolor{blue}{rgb}{0.0, 0.4, 1.0}
+\definecolor{Blue}{rgb}{0,0,1}
+\definecolor{darkgreen}{rgb}{0.,0.6,0.}
+\newcommand*{\red}[1]{\textcolor{red}{#1}}
+\newcommand*{\Blue}[1]{\textcolor{Blue}{#1}}
+\newcommand*{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand*{\green}[1]{\textcolor{darkgreen}{#1}}
+\newcommand*{\black}[1]{\textcolor{black}{#1}}
+
+\definecolor{colorA}{rgb}{1,0,0}
+\definecolor{colorB}{rgb}{0,0.3,1}
+\definecolor{colorC}{rgb}{0.9,0.8,0.2}
+\definecolor{colorD}{rgb}{0,0.65,0}
+
+\newcommand*{\colorA}[1]{\textcolor{colorA}{#1}}
+\newcommand*{\colorB}[1]{\textcolor{colorB}{#1}}
+\newcommand*{\colorC}[1]{\textcolor{colorC}{#1}}
+\newcommand*{\colorD}[1]{\textcolor{colorD}{#1}}
+
 \usepackage{mdframed}
@@
 
+\appendix
+
+\section{Computation of $\Omega_5^{\mathrm{spin}}\big(
+	B\big(
+		\tfrac{SO(4)\times SU(2)}{\bZ_2}
+	\big)
+\big)$}
+
+Let us consider the simplest case of the Seiberg duality and examine the anomaly consequences.
+For $SO(4)$ gauge theory with $N_f=2$ flavors, fermions are charged under $\tfrac{SO(4)\times SU(2)}{\bZ_2}$.
+\subsection{Leray-Serre SS (preparatory)}
+For the various input of cohomology groups, see Appendix A of our WZW paper.
+For the fibration
+\begin{equation}
+	BSO(3)
+	\ \to\ 
+	B\left(SO(3)\times SO(3)\right)
+	=
+	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+	\ \to\ 
+	BSO(3)
+\end{equation}
+one has
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(BSO(3);H^q(BSO(3);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6 & \bZ_2 && \ast & \ast & \ast & \ast & \ast \\
+			5  & \hphantom{\bZ_2}\cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast && \ast\\
+			3  & \bZ_2 && \bZ_2\cellcolor{lightyellow} & \bZ_2 & \ast & \ast & \ast \\
+			2  & &  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_2 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  &\bZ_2^{\oplus 3}\\
+			5  & \bZ_2\cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 2}\\
+			3  & \bZ_2^{\oplus 2}\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+Here we expect non-trivial differentials to be absent (for the region of interest)
+from the explicit consideration of generators (since there are $W_3$ and $W'_3$, there should be $(W_3)^2$, $(W'_3)^2$, and $W_3W'_3$)
+or by requiring proper reproduction of the $\bZ_2$ cohomology (which we expect to be generated by $w_2$, $w'_2$, $w_3$, and $w'_3$).
+Then, for the fibration
+\begin{equation}
+	BSU(2)
+	\ \to\ 
+	B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right)
+	\ \to\ 
+	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+\end{equation}
+we can further plug it into
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(B\left(\tfrac{SO(4)}{\bZ_2}\right);H^q(BSU(2);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \red{\fbox{\black{$\bZ$}}} & \cellcolor{lightyellow} && \ast & \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  &&  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_2^{\oplus 2} & \bZ^{\oplus 2} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & \bZ_2^{\oplus 3}\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 3}\\
+			3  & \bZ_2^{\oplus 2}\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+Taking the normalization of instanton number into account (see Ohmori-san's e-mail on 2020-08-19),
+the differential \red{\fbox{\black{$d_2 : E_{0,4} \to E_{5,0}$}}} seems to be non-trivial.
+
+So we believe the integral cohomology structure to be
+\begin{equation}
+	\label{case1}
+	\renewcommand{\arraystretch}{1.2}
+	\begin{array}{c|cccccccccccccccc}
+		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
+		\hline
+		H^d(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ) & \bZ & 0 & 0 & \bZ_2^{\oplus 2} & \bZ^{\oplus 3} & 0 & \bZ_2^{\oplus 3} & \cdots\\
+		\hline
+		\text{generator} & 1 & - & - & W_3 & p_1 & - & (W_3)^2 & \cdots\\
+		&&&& W'_3 & p'_1 && (W'_3)^2\\
+		&&&&& 2c_2 && W_3W'_3
+	\end{array}
+\end{equation}
+where the reduction to $\bZ_2$ cohomology are
+\begin{equation}
+	\begin{array}{ccc}
+		W_3 & \to & w_3\\
+		p_1 & \to & (w_2)^2\\
+%		y_5 & \to & w_2w'_3 + w_3w'_2 \,(?)\\
+	\end{array}
+\end{equation}
+
+\subsection{Atiyah-Hirzebruch SS}
+%Turning cohomology groups into homology groups via the universal coefficient theorem,
+Having obtained (co)homology groups,
+one can fill in the $E^2$-page of the AHSS:
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right))\vspace{4mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2} && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3} & \ast & \ast\\
+			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 3}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} & \ast\\
+			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\fbox{\black{$\bZ^{\oplus 3}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & ?\\
+			5  & ?\cellcolor{lightyellow}\\
+			4  & ?\\
+			3  & ?\\
+			2  & \bZ_2^{\oplus 2}\\
+			1  & \\
+			0 & \\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+Based on our belief, 
+\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
+\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 w_2 & = & (w_2)^2 \\
+		Sq^2 w'_2 & = & (w'_2)^2
+	\end{array}
+\end{equation}
+and also
+\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
+\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 w_3 & = & w_2w_3\\
+		Sq^2 w'_3 & = & w'_2w'_3
+	\end{array}
+\end{equation}
+and finally \green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 (w_2w'_2) & = & w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2
+	\end{array}
+\end{equation}
+then %one can proceed, and 
+the would-be-$E_3$-page is given by
+\begin{equation}
+	\label{e3page1}
+	\begin{array}{c|c:cccccccccccc}
+		6  &&&&&& \\
+		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
+		2  & \bZ_2 &  && \cellcolor{lightyellow} & \ast & \ast & \ast\\
+		1  & \bZ_2 &&  && \cellcolor{lightyellow} & \ast & \ast\\
+		0 & \bZ &  & \bZ_2^{\oplus 2} &  & \bZ^{\oplus 3} & \bZ_2\cellcolor{lightyellow} & \ast\\
+		\hline
+		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+	\end{array}
+\end{equation}
+
+\subsection{Adams SS}
+According to our naive guess, the module $\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
+\begin{equation}
+	\begin{tikzpicture}[thick,baseline=(m-2-1.south)]
+		\matrix (m) [
+			matrix of math nodes,
+			row sep= 1em,
+			column sep=6em,
+		]{
+			&&& \colorB{\bullet}\\
+			&&& \colorB{\bullet}\\
+			&&& \colorB{\bullet}\\
+			&& \colorB{\bullet} & \colorB{\bullet}\\
+			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
+		    \colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet} & \colorD{\bullet}\\
+			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
+			\colorA{\bullet} &&&& \colorC{\bullet}\\
+			\colorA{\bullet} &&&& \colorC{\bullet}\\
+		};
+		\draw[colorA] (m-7-1.center) to [out=200, in=160] (m-9-1.center);
+		\draw[colorA] (m-9-1.center) to (m-8-1.center);
+		\draw[colorA] (m-5-1.center) to [out=200, in=160] (m-7-1.center);
+		\draw[colorA] (m-6-1.center) to (m-5-1.center);
+		\draw[colorA] (m-6-1.center) to [out=340, in=20] (m-8-1.center);
+		%
+		\node[colorA, right=4pt] at (m-9-1) {$w_2$};
+		\node[colorA, right=6pt] at (m-8-1) {$w_3$};
+		\node[colorA, left=6pt] at (m-7-1) {$(w_2)^2$};
+		\node[colorA, right=6pt] at (m-6-1) {$w_2w_3$};
+		\node[colorA, left=4pt] at (m-5-1) {$(w_3)^2$};
+		%
+		\draw[colorB] (m-7-3.center) to [out=160, in=200] (m-5-3.center);
+		\draw[colorB, dotted] (m-7-3.center) to (m-6-3.center);
+		\draw[colorB, dotted] (m-6-3.center) to [out=5, in=185] (m-4-4.center);
+		\draw[colorB] (m-5-3.center) to (m-4-3.center);
+		\draw[colorB, dotted] (m-5-3.center) to [out=5, in=185] (m-3-4.center);
+		\draw[colorB, dotted] (m-4-4.center) to (m-3-4.center);
+		\draw[colorB] (m-4-3.center) to [out=5, in=185] (m-2-4.center);
+		\draw[colorB, dotted] (m-2-4.center) to (m-1-4.center);
+		\draw[colorB, dotted] (m-3-4.center) to [out=5, in=355] (m-1-4.center);
+		%
+		\node[colorB, right=4pt] at (m-7-3) {$w_2w'_2$};
+		\node[colorB, right=4pt] at (m-6-3) {$w_3w'_2 + w_2w'_3$};
+		\node[colorB, left=4pt] at (m-5-3) {$w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2$};
+		\node[colorB, left=4pt] at (m-4-3) {$(w_2)^2w'_3 + w_3(w'_2)^2$};
+		%
+		\node[colorB, right=4pt] at (m-4-4) {$\begin{array}{r}
+			w_2w_3w'_2 + w_3(w'_2)^2
+			+ (w_2)^2w'_3 + w_2w'_2w'_3
+		\end{array}$};
+		\node[colorB, right=4pt] at (m-3-4) {$\begin{array}{r}
+			(w_3)^2w'_2 + w_2w_3w'_3
+			+ w_3w'_2w'_3 + w_2(w'_3)^2
+		\end{array}$};
+		\node[colorB, left=4pt] at (m-2-4) {$\begin{array}{r}
+			(w_3)^2w'_3 + (w_2)^2w'_2w'_3
+			+ w_2w_3(w'_2)^2 + w_3(w'_3)^2
+		\end{array}$};
+		\node[colorB, right=4pt] at (m-1-4) {$\begin{array}{r}
+			(w_2)^2(w'_3)^2 + (w_3)^2(w'_2)^2
+		\end{array}$};
+		%
+		\draw[colorC] (m-7-5.center) to [out=200, in=160] (m-9-5.center);
+		\draw[colorC] (m-9-5.center) to (m-8-5.center);
+		\draw[colorC] (m-5-5.center) to [out=200, in=160] (m-7-5.center);
+		\draw[colorC] (m-6-5.center) to (m-5-5.center);
+		\draw[colorC] (m-6-5.center) to [out=340, in=20] (m-8-5.center);
+		%
+		\node[colorC, right=4pt] at (m-9-5) {$w'_2$};
+		\node[colorC, right=6pt] at (m-8-5) {$w'_3$};
+		\node[colorC, left=6pt] at (m-7-5) {$(w'_2)^2$};
+		\node[colorC, right=6pt] at (m-6-5) {$w'_2w'_3$};
+		\node[colorC, left=4pt] at (m-5-5) {$(w'_3)^2$};
+		%
+		\node[colorD, right=4pt] at (m-6-6) {(*)};
+	\end{tikzpicture}
+\end{equation}
+To be consistent with the AHSS computation,
+it seems that $w_3w_2' + w_2w'_3$ should be modded out
+(is it an obvious consequence of the transgression in LSSS...?)
+and the remaing part \colorD{(*)} turns out to be
+\begin{equation}
+	\begin{tikzpicture}[colorD, thick,baseline=(m-2-1.south)]
+		\matrix (m) [
+			matrix of math nodes,
+			row sep= 1em,
+			column sep=6em,
+		]{
+			\bullet\\
+		    \bullet\\
+			\bullet\\
+			\bullet\\
+			\bullet\\
+		};
+		\draw (m-3-1.center) to [out=200, in=160] (m-5-1.center);
+		\draw (m-5-1.center) to (m-4-1.center);
+		\draw (m-1-1.center) to [out=200, in=160] (m-3-1.center);
+		\draw (m-2-1.center) to (m-1-1.center);
+		\draw (m-2-1.center) to [out=340, in=20] (m-4-1.center);
+		%
+		\node[right=4pt] at (m-5-1) {$w_2w'_3 = w_3w'_2$};
+		\node[right=6pt] at (m-4-1) {$w_3w'_3$};
+		\node[left=6pt] at (m-3-1) {$(w_2)^2w'_3 + w_2w'_2w'_3$};
+		\node[right=6pt] at (m-2-1) {$w_2w_3w'_3 + w_3w'_2w'_3$};
+		\node[left=4pt] at (m-1-1) {$(w_3)^2w'_3 + w_3(w'_3)^2$};
+	\end{tikzpicture}
+\end{equation}
+and therefore one concludes
+\begin{equation}
+	\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
+\end{equation}
+This leads to the following Adams chart:
+\begin{center}
+	\begin{sseqdata}[
+		name=M,
+		Adams grading,
+		classes = fill,
+		xrange = {0}{5},
+		yrange = {0}{3},
+		%,x label = {$t-s$}, y label = {$s$}
+	]
+		\tower[colorB](4,0)
+		\class[white](4,0)
+		\class[white](4,0)
+		\class[colorA](2,0)
+		\class[colorC](2,0)
+		\tower[colorA](4,1)
+		\tower[colorC](4,1)
+		\class[colorD](5,0)
+	\end{sseqdata}
+	\printpage[name = M,page = 2]
+\end{center}
+and it indeed seems to be compatible with the AHSS computation.
+If the above argument (and beliefs) is correct, then the anomaly should be captured by
+\begin{equation}
+	w_2w'_3\ (= w_3w'_2).
+\end{equation}
+
+\subsection{Seiberg dual}
+The dual theory is $SO(2)$ gauge theory with $N_f = 2$ flavors, and the fermions are charged under
+\begin{equation}
+	\frac{SO(2)\times SU(2)}{\bZ_2}
+	=
+	U(2)
+\end{equation}
+Its spin bordism is known, and the relevant group turns out to be trivial:
+\begin{equation}
+	\Omega_5^{\mathrm{spin}}\big(BU(2)\big) = 0.
+\end{equation}
+This means there is no anomaly for fermions on the dual side,
+and thus the $B\beta E$ anomaly cannot be canceled by fermions.
+
+\newpage
+
 \bibliographystyle{ytphys}

### 2021-06-01 dualitypaper.tex
old paper

\RequirePackage[T1]{fontenc}
\documentclass[12pt]{article}

\usepackage[height=8.85in,width=6.45in]{geometry}
%\usepackage{showkeys}
\renewcommand{\baselinestretch}{1.08}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\numberwithin{equation}{section}
\usepackage{slashed}
\usepackage{braket}
\usepackage[svgnames,psnames]{xcolor}
\usepackage[colorlinks,citecolor=DarkGreen,linkcolor=FireBrick,linktocpage]{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{times}
\usepackage{courier}
\usepackage{bm}
\usepackage{subfig}
\usepackage{ascmac}

\usepackage{mdframed}
\newenvironment{claim}{  \begin{mdframed}[linecolor=black!0,backgroundcolor=black!10]\noindent\itshape\ignorespaces}{\end{mdframed}}

\let\originalfigure=\figure
\let\endoriginalfigure=\endfigure
\let\originaltable=\table
\let\endoriginaltable=\endtable

\renewenvironment{figure}[1][]{
  \begin{originalfigure}[#1]
    \begin{mdframed}[linecolor=black!0,backgroundcolor=black!1]
}{
    \end{mdframed}
  \end{originalfigure}
}
\renewenvironment{table}[1][]{
  \begin{originaltable}[#1]
    \begin{mdframed}[linecolor=black!0,backgroundcolor=black!1]
}{
    \end{mdframed}
  \end{originaltable}
}%% Comment
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}

%% Color
\usepackage{colortbl}
\definecolor{lightyellow}{rgb}{1.0, 0.95, 0.7}
\definecolor{lightblue}{rgb}{0.7, 0.9, 1.0}
\definecolor{lightpink}{rgb}{1.0, 0.85, 0.95}
\definecolor{lightgreen}{rgb}{0.7, 1.0, 0.4}

%% Yuji's macros
%%list HigherSymmetriesAndDuality
\newcommand*{\bZ}{\mathbb{Z}}
\newcommand*{\bR}{\mathbb{R}}
\newcommand*{\dint}{\displaystyle\int}
\newcommand*{\cP}{\mathcal{P}}
\newcommand*{\fP}{\mathfrak{P}}
\def\Nequals#1{$\mathcal{N}{=}#1$}
\def\SO{\mathrm{SO}}
\def\so{\mathfrak{so}}
\def\Spin{\mathrm{Spin}}

\def\boo{0.0}

\def\xlattice#1#2#3{
\begin{tikzpicture}[scale=.5]
\filldraw[color=black!5!white](-.5,-.5) rectangle (1.5,1.5);
\draw[->] (-1,0) -- (2,0);
\draw[->] (0,-1) -- (0,2);
\foreach \x in {0,1} {
	\foreach \y in {0,1}{
		\pgfmathsetmacro\a{mod(#1 * \x - #2 * \y,2)}
		\ifx\a\boo
			\filldraw[color=#3] (\x,\y) circle (.5em);
		\else
			\filldraw[fill=white,draw=gray] (\x,\y) circle (.5em);
		\fi
	}
}
\end{tikzpicture}
}

\begin{document}

\begin{titlepage}

\begin{flushright}
IPMU-19-0124
\end{flushright}

\vskip 3cm

\begin{center}

{\Large \bfseries Matching higher symmetries across Seiberg duality}

\vskip 1cm
Yasunori Lee$^1$, Kantaro Ohmori$^2$, and Yuji Tachikawa$^1$
\vskip 1cm

\begin{tabular}{ll}
$^1$ & Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\
& University of Tokyo,  Kashiwa, Chiba 277-8583, Japan\\
$^2$ & Simons Center for Geometry and Physics, \\
& SUNY, Stony Brook, NY 11794, USA
\end{tabular}

\vskip 1cm

\end{center}

\noindent 
We study the generalized symmetries of 4d \Nequals1 supersymmetric $\mathfrak{so}(2n_c)$ gauge theory with $N_f=2n_f$ flavors and their anomalies.
We find that they depend on the parity of $n_c$ and $n_f$ 
and also on the choice of the global form of the gauge group and the discrete theta angle,
and that they agree across Seiberg duality.
In particular, when $n_c$ is odd and $n_f$ is even, 
the $\bZ_2$ one-form symmetry nontrivially extends the 0-form flavor symmetry to form a 2-group for $\Spin$ or $\SO_-$ theories,
while the $\bZ_2$ one-form symmetry and the 0-form flavor symmetry remains a direct product but has a nontrivial mixed anomaly for $\SO_+$ theories.

\end{titlepage}

\setcounter{tocdepth}{2}
\tableofcontents

%\newpage

\section{Introduction and summary}
Our understanding of the concept of symmetries in quantum field theories has been greatly improved in the last several years.
We now have the concept of $p$-form symmetries acting on $p$-dimensional objects \cite{Gaiotto:2014kfa}.
This concept  gives a unifying point of view to both
ordinary symmetries acting on point operators for $p=0$
and center symmetries of gauge theories acting on Wilson line operators for $p=1$.
In addition, the 't Hooft magnetic flux \cite{tHooft:1979rtg} can now be thought of as a background gauge field for the 1-form center symmetry.
It is also realized more recently that 0-form symmetries and 1-form symmetries can not only coexist in a direct product but also mix in a more intricate manner, defining a symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.

These new concepts can be used very effectively to constrain the dynamics of various strongly-coupled systems,
as demonstrated beautifully in \cite{Gaiotto:2017yup} and later works inspired by it.
These were mostly done on non-supersymmetric quantum field theories,
for which the concept of generalized symmetries is a big new addition to the few analytical tools already available.
This should not, however, stop us to apply this new tool to the study of supersymmetric systems.
There are indeed  many existing techniques to study them exactly,
but the concept of generalized symmetries might shed a somewhat different light on them from a different angle.

In this short note we intend to initiate such a study, 
by having a look at the generalized symmetries of 4d \Nequals1 supersymmetric $\mathfrak{so}(2n_c)$ QCD with $N_f=2n_f$ flavors.
It is  a classic fact \cite{Intriligator:1995id} that this theory has a Seiberg dual description as an $\mathfrak{so}(2n_c')$ QCD with $N_f=2n_f$ flavors with additional singlets and a superpotential term, where $n_c'=n_f+2-n_c$.
To fully specify the theory, one needs to pick the global structure of the gauge group and the discrete theta angle.
In the case of $\mathfrak{so}$ QCD,
there are three choices\footnote{%
Here we made a simplifying assumption that the spacetime has a spin structure,
the gauge group and the spacetime symmetry forms a direct product,
and the gauge group is connected.
}, namely $\Spin(2n_c)$, $\SO(2n_c)_+$ and $\SO(2n_c)_-$,
and the Seiberg duality exchanges $\Spin$ and $\SO_-$ while keeping $\SO_+$ fixed \cite{Aharony:2013hda}.
This action of the Seiberg duality was deduced by studying the behavior of line operators acted on by a $\bZ_2$ 1-form symmetry,
and was given a more detailed check by a study of the supersymmetric index on the lens space \cite{Razamat:2013opa}.
Our concrete objective in this paper is to understand the interplay of this $\bZ_2$ 1-form symmetry and the 0-form flavor symmetry acting on $N_f=2n_f$ flavors.

More concretely, we find that interesting phenomena happen when $n_f$ is even and $n_c$ is odd.
We will find that when the gauge group is either $\Spin$ or $\SO_-$, the 0-form flavor symmetry is extended by the $\bZ_2$ one-form symmetry to become a genuine 2-group.
We will also find that when the gauge group is $\SO_+$, the 0-form flavor symmetry
and the $\bZ_2$ one-form symmetry remains a direct product
but that there is a mixed anomaly between them.
We will see that this distribution of the extension and the anomaly is consistent with the action of Seiberg duality.
We will also see that it is consistent also under the gauging of one-form symmetries to go back and forth among various choices of the gauge groups.

The rest of this short note contains two sections. 
In Sec.~\ref{sec:known}, 
we recall the properties of $\bZ_2$ 1-form symmetries of the $\Spin$, $\SO_+$ and $\SO_-$ quantum chromodynamics,
and the properties of groups whose Lie algebra is $\so(2n_c)$.
Then in Sec.~\ref{sec:unknown},
we study whether the $\bZ_2$ 1-form symmetry extends the 0-form flavor symmetry,
or there is a mixed anomaly between them,
in the three cases of $\Spin$, $\SO_+$ and $\SO_-$.
Finally we check that our findings are consistent with the action of Seiberg duality.

Before proceeding we note that except at the very end we do not use any property of Seiberg duality.
The bulk of the paper is about the study of the global structure formed by the $\bZ_2$ 1-form symmetry and the 0-form flavor symmetry and its anomaly in each of the three choices.
We will also see that the cross-check provided by our analysis on the Seiberg duality of $\so$ theories is not trivial but not strong either.
That said,  the authors believe that it can be fruitfully applied to many other known and unknown \Nequals1 duality pairs.

\section{Known facts}
\label{sec:known}
Let us quickly summarize known facts we will make use of in the rest of the paper.
We are interested in $\mathfrak{so}$ gauge theories with matter fields in the vector representation.

\subsection{Line operators and the three choices $\Spin/\SO_+/\SO_-$}
\label{sec:lines}
Consider an electric Wilson line operator in the spinor representation $W$.
Its square is in the vector representation, and can be screened by the dynamical matter field.
This means that the electric lines can be labeled by  $\bZ_2$.
Let us next consider a magnetic 't Hooft line operator $H$,
which has a minimal unit of allowed magnetic charge with respect to the matter in the vector representation.
It is characterized by a nontrivial Stiefel-Whitney class $w_2\in H^2(S^2,\bZ_2)$ of  the gauge bundle on the $S^2$ around the line operator,
meaning that the magnetic lines can also be labeled by $\bZ_2$.
In total the topological classification of the line operators in an $\mathfrak{so}$ theory with matter fields in the vector representation is given by $\bZ_2\times \bZ_2=\{1,W\}\times \{1,H\}$,
but $W$ and $H$ are mutually non-local.

\begin{figure}
\centering
\begin{tabular}{c@{\qquad}c@{\qquad}c}
\xlattice01{Red} & \xlattice10{Green} & \xlattice11{Blue} \\
$\Spin$ & $\SO_+$ & $\SO_-$
\end{tabular}
\caption{The line operators present in $\Spin$, $\SO_+$, $\SO_-$ quantum chromodynamics.
The horizontal  axis and the vertical axis measure the electric charge and the magnetic charge, respectively.
In all cases, the group of lines is a $\bZ_2$ subgroup of the $\bZ_2\times \bZ_2$ group of possibly mutually-nonlocal lines of $\mathfrak{so}$ quantum chromodynamics.
The $\Spin$, $\SO_+$, $\SO_-$ theory contains an electric line,
a magnetic line, and a dyonic line, respectively.
\label{fig:lines}
}
\end{figure}

To fully specify a quantum field theory, we need to pick a maximal set of mutually-local line operators.
There are three choices: $\{1,W\}$, $\{1,H\}$ and $\{1,D:=WH\}$.
The first choice is the $\Spin$ gauge theory, and the second is the standard $\SO$ gauge theory.
The existence of the third choice was more recently noticed
and is given by an $\SO$ gauge theory with a discrete theta term \begin{equation}
\exp\left(2\pi i \frac14 \int_X \mathfrak{P}(w_2)\right)
\label{pont}
\end{equation} 
in the exponentiated action, where $\mathfrak{P}(w_2)\in H^4(X,\bZ_4)$ is the Pontryagin square of the Stiefel-Whitney class $w_2\in H^2(X,\bZ_2)$ of the gauge bundle on the spacetime $X$.
When $X$ is spin as we assume throughout in the paper,
the integral of $\mathfrak{P}(w_2)$ is even,
producing a sign in the integrand of the path integral.
This makes the 't Hooft line to acquire an electric charge $W$.
For details, we refer the reader to \cite{Aharony:2013hda}.
We summarized the choice of line operators in Fig.~\ref{fig:lines}.

It is a classic result in the study of 4d \Nequals1 supersymmetric theories
that the Seiberg dual of the $\so(N_c)$ gauge theory with $N_f$ flavors
is given by an $\so(N_c')$ gauge theory with  $N_f$ flavors 
with an additional gauge singlet meson fields and a superpotential term,
where $N_c'=N_f+4-N_c$ \cite{Intriligator:1995id}.
In \cite{Aharony:2013hda} the action of the Seiberg duality was refined to take into account the three possibilities $\Spin$, $\SO_+$ and $\SO_-$;
it was found there that $\SO_+$ is self-dual while $\Spin$ and $\SO_-$ are exchanged.
This was indirectly argued in \cite{Aharony:2013hda} from the behavior of the line operators,
and was later given a more direct check via the computation of the supersymmetric index on the lens spaces in \cite{Razamat:2013opa}.

\subsection{Facts concerning $\so(2n)$}
\label{sec:math}
We are going to refine the understanding reviewed above when $N_c$ and $N_f$ are both even.
For this we need to recall a few facts concerning $\so(2n)$.
This is mostly to set the notations;
a reader might want to skip the rest of this section and come back only when an unfamiliar symbol is used.

The simply-connected group $\Spin(2n)$ has a center  of order four,
given by $\bZ_4=\{0,s,v=s^2,c=s^3\}$ when $n$ is odd
and $\bZ_2\times \bZ_2=\{0,s\}\times \{0,c\}$ when $n$ is even;
we define $v=s+c$ for the latter case.
The representations of $\Spin(2n)$ can be classified into four classes $0$, $S$, $C$, $V$
according to how the center acts on them.

\begin{figure}
\[
\begin{tikzpicture}[scale=.5,baseline=(SO.base)]
\node(Spin) at (0,0) {$\Spin(2n)$};
\node(Ss) at (-8,-2) {$\mathrm{Ss}(2n)$};
\node(SO) at (0,-2) {$\SO(2n)$};
\node(Ss') at (+8,-2) {$\mathrm{Ss}'(2n)$};
\node(PSO) at (0,-4) {$\SO(2n)/\bZ_2$};
\node(legend) at (0,-6) {$n$ even};
\draw[->] (Spin) to node[above]{\footnotesize $v_2{=}w_2'$}  (Ss); 
\draw[->] (Spin) to node[left]{\footnotesize $w_2{=}w_2'$}  (SO); 
\draw[->] (Spin) to node[above]{\footnotesize $v_2{=}w_2$}  (Ss'); 
\draw[->] (Ss) to node[below]{\footnotesize $w_2$} (PSO);
\draw[->] (SO) to node[left]{\footnotesize $v_2$} (PSO);
\draw[->] (Ss') to node[below]{\footnotesize $w_2'$} (PSO);
\end{tikzpicture}
\qquad\qquad
\begin{tikzpicture}[scale=.5,baseline=(SO.base)]
\node(Spin) at (0,0) {$\Spin(2n)$};
\node(SO) at (0,-2) {$\SO(2n)$};
\node(PSO) at (0,-4) {$\SO(2n)/\bZ_2$};
\node(legend) at (0,-6) {$n$ odd};
\draw[->] (Spin) to node[left]{\footnotesize $w_2$}  (SO); 
\draw[->] (SO) to node[left]{\footnotesize $v_2$} (PSO);
\draw[->,dashed,out=-10,in=10] (Spin.east) to node[right]{\footnotesize $\tilde v_2$}  (PSO.east); 
\end{tikzpicture}
\]
\caption{%
Various quotients of $\Spin(2n)$ and the characteristic classes associated to their bundles. 
Solid arrows are $\bZ_2$ quotients and the dashed arrow is a $\bZ_4$ quotient.
Each arrow is labeled by the corresponding obstruction classes.
\label{fig:classes}}
\end{figure}

The quotient of $\Spin(2n)$ by $\bZ_2=\{0,v\}$ is $\SO(2n)$.
Accordingly, an $\SO(2n)$ bundle $A$ on a space $X$ has the second Stiefel-Whitney class $w_2(A)\in H^2(X,\bZ_2)$, which is trivial if and only if the bundle $A$ lifts to a $\Spin(2n)$ bundle.
The group $\SO(2n)$ has the center $\bZ_2=\{0,s=c\}$,
and we can form a further quotient $\SO(2n)/\bZ_2$.
Analogously to the case just mentioned above,
an $\SO(2n)/\bZ_2$ bundle $A'$ on a space $X$ has an obstruction class in $H^2(X,\bZ_2)$, which is trivial if and only if the bundle $A'$ lifts to an $\SO(2n)$ bundle.
There does not seem to be a common name for this class; 
we denote it by $v_2(A')\in H^2(X,\bZ_2)$.

When $n$ is odd, $\pi_1(\SO(2n)/\bZ_2)=\bZ_4$, and therefore
there is an obstruction class $\tilde v_2(A')\in H^2(X,\bZ_4)$ which controls if $A'$ lifts all the way to $\Spin(2n)$,
and $v_2(A')$ is simply the mod-2 reduction of $\tilde v_2(A')$.
When $n$ is even, $\pi_1(\SO(2n)/\bZ_2)=\bZ_2\times \bZ_2$.
Correspondingly, we have two classes $w_2(A')$, $w_2'(A')\in H^2(X,\bZ_2)$
controlling whether the bundle $A'$ lifts to 
an $\mathrm{Ss}(2n)=\Spin(2n)/\{0,s\}$ bundle or  
an $\mathrm{Ss}'(2m)=\Spin(2n)/\{0,c\}$ bundle.\footnote{%
$\mathrm{Ss}$ stands for semi-spin.
}
Here we have  $v_2(A')=w_2(A')+w_2'(A')$.
The information are summarized in Fig.~\ref{fig:classes}.

\section{The mixed anomaly and the 2-group}
\label{sec:unknown}
Let us now consider $\so(2n_c)$ gauge theory with $2n_f$ flavors in the vector representation.
We chose the number of colors $N_c$ to be even, $N_c=2n_c$,
to see the effect of the larger center of $\Spin(2n_c)$ which is order 4.
When the matter fields are massless, the system has $\mathfrak{su}(2n_f)$ flavor symmetry,
but we choose to use only the $\mathfrak{so}(2n_f)$ sub-symmetry, which is compatible with a nonzero mass term.
Our motivation to let the number of flavors $N_f$ to be even, $N_f=2n_f$, is again the same.

Now the matter field is in the bivector representation of $\so(2n_c)$ and $\so(2n_f)$.
Let us then take the global form of the combined gauge and flavor group to be 
\begin{equation}
\frac{\Spin(2n_c)\times \SO(2n_f)}{\bZ_2},\quad
\frac{\SO(2n_c)_+\times \SO(2n_f)}{\bZ_2},\quad
\frac{\SO(2n_c)_-\times \SO(2n_f)}{\bZ_2} 
\label{foo}
\end{equation}
where the quotient is in general with respect to the diagonal subgroup of $\bZ_2$ centers which act trivially on the bivector representation, 
with the exception that we consider \begin{equation}
\frac{\Spin(2n_c)\times \SO(2n_f)}{\bZ_4}
\label{bar}
\end{equation}
when $n_c$  is odd, for which we use the $\bZ_4$ subgroup generated by $(1,1) \in \{0,1,2,3\}\times \{0,1\}$.

The 0-form part of the flavor symmetry is then $\SO(2n_f)/\bZ_2$,
and we are interested in its interrelationship with the $\bZ_2$ 1-form symmetries of the gauge part we reviewed in Sec.~\ref{sec:lines}.

\subsection{Appearance of 2-group in the $\Spin(2n_c)$ theory}
Let us start by analyzing the charge of the line operators of the $\Spin(2n_c)$ theory.
An important step in our brief review in Sec.~\ref{sec:lines}
was to declare that the Wilson line in the vector representation is considered topologically trivial
since there are dynamical fields in the vector representation.
We now take into account the flavor symmetry.
The dynamical fields are in the bivector representation of $\so(2n_c)$ and $\so(2n_f)$.
This means that a gauge Wilson line in the vector of $\so(2n_c)$
and a flavor Wilson line in the vector of $\so(2n_f)$ are considered topologically identical.

Consider then a gauge Wilson line $W$ in the spinor of $\so(2n_c)$,
which is charged under the $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory.
When $n_c$ is odd, $W^2$ is in the vector representation of $\so(2n_c)$,
which is then equivalent to a flavor Wilson line in the vector of $\so(2n_f)$.
Let us furthermore assume that $n_f$ is even.
Then there is no flavor Wilson line such that its square is in the vector of $\so(2n_f)$.
We find that a flavor Wilson line in the vector of $\so(2n_f)$,
which is not divisible by two if we only consider flavor Wilson lines,
becomes divisible by two if we consider gauge Wilson lines.
This means that the $\bZ_2$ 1-form symmetry extends the 0-form flavor symmetry nontrivially.

To see why, consider an ordinary group extension \begin{equation}
0\to \bZ_2\to \bZ_8 \to \bZ_4 \to 0.
\end{equation} Taking the Pontryagin duals (i.e.~the groups formed by one-dimensional representations), we have \begin{equation}
0\to \hat\bZ_4\to \hat\bZ_8 \to \hat\bZ_2 \to 0.
\end{equation}
In words,  a charge-1 representation of $\bZ_4$ corresponds to a charge-2 representation of $\bZ_8$,  which is clearly divisible by 2 as a $\bZ_8$ representation.
In our case, the role of $\bZ_2$ is played by the 1-form $\bZ_2$ symmetry
and the role of $\bZ_4$ is played by the flavor symmetry $\SO(2n_f)/\bZ_2$.
The extension can be written as \begin{equation}
0\to \bZ_2[1] \to  H \to \SO(2n_f)/\bZ_2 \to 0
\label{2group}
\end{equation} where $[1]$ after $\bZ_2$ is to signify it is a one-form symmetry;
$H$ is a nontrivial extension of a continuous flavor symmetry by a discrete one-form symmetry,
and is an example of a genuine 2-group.
We note that in general an extension \begin{equation}
0\to A[p] \to H \to G \to 0
\end{equation} of a 0-form symmetry $G$ by an Abelian $p$-form symmetry $A$ is specified by a class \begin{equation}
e\in H^{2+p} (BG,A)
\end{equation} known as the Postnikov class of the extension;
this reduces to the ordinary extension class in $H^2(BG,A)$ in the case of an extension of a 0-form symmetry by another 0-form symmetry.
We will determine $e$ below.

The appearance of a nontrivial 2-group can also be seen from the point of view of the background fields coupled to the symmetry.
This point of view allows us to find the Postnikov class of the extension.
The background $E\in H^2(X,\bZ_2)$ for the $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2(c)\in H^2(X,\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2(c)$.
In the presence of a nontrivial $\SO(2n_f)/\bZ_2$ background $f$, however, 
the gauge bundle is not necessarily an $\SO(2n_c)$ bundle.
Rather, it is in general an $\SO(2n_c)/\bZ_2$ bundle such that $v_2(c)=v_2(f)$,
where $v_2$ is the obstruction class controlling the lift from $\SO/\bZ_2$ to $\SO$.

When $n_c$ is even this poses no problem since the classes $v_2$ and $w_2$ exist independently in $\SO(2n_c)/\bZ_2$.
When $n_c$ is odd, however, there is a problem, since the $(\bZ_2)_{w_2}$ controlling $\Spin(2n_c)\to \SO(2n_c)$
and $(\bZ_2)_{v_2}$ controlling $\SO(2n_c) \to \SO(2n_c)/\bZ_2$ form a nontrivial extension \begin{equation}
0\to (\bZ_2)_{w_2} \to (\bZ_4)_{\tilde v_2} \to (\bZ_2)_{v_2} \to 0.
\end{equation}
This is reflected in the fact that the quotient is by $\bZ_4$ in \eqref{bar} when $n_c$ is odd.
In this case, what is guaranteed to exist is the $\bZ_4$ class $\tilde v_2(c) \in H^2(X,\bZ_4)$.

The data contained in $\tilde v_2(c)$ can be encoded by a closed cochain $v_2(c)\in H^2(X,\bZ_2)$
and  a not-necessarily-closed cochain $w_2(c)\in C^2(X,\bZ_2)$ satisfying \begin{equation}
\delta w_2(c) = \beta v_2(c).\label{asin}
\end{equation} where $\delta$ is the coboundary and $\beta$ is the Bockstein.
Recalling $v_2(c)=v_2(f)$, and $E=w_2(c)$, we see that the background fields for the $\Spin(2n_c)$ theory are given by a pair of an $\SO(2n_f)/\bZ_2$ bundle $f$
and a cochain $E\in C^2(X,\bZ_2)$ satisfying the relation \begin{equation}
\delta E= \beta v_2(f).
\label{ext}
\end{equation}
This means that the 2-group extension \eqref{2group} is specified by the extension class \begin{equation}
\beta v_2 \in H^3(B\SO(2n_f)/\bZ_2, \bZ_2).
\end{equation}
Recall that  the Bockstein $\beta x$ of a mod-2 class $x$ is defined so that it controls whether $x$ is a mod-2 reduction of the $\bZ_4$.
When $n_f$ is odd, $v_2$ is a mod-2 reduction of the $\bZ_4$ class $\tilde v_2$ controlling the lift from $\SO(2n_f)/\bZ_2$  all the way to $\Spin(2n_f)$.
Therefore the extension class $\beta v_2$ is trivial when $n_f$ is odd,
whereas it  is nontrivial when $n_f$ is even.
We conclude that we have a nontrivial 2-group only when $n_c$ is odd and $n_f$ is even.

\subsection{Mixed anomaly in the $\SO(2n_c)_+$ theory}
Let us next consider the $\SO(2n_c)_+$ theory.
Here, the charged objects under the $\bZ_2$ one-form symmetry are the 't Hooft loops $H$.
The background field $B\in H^2(X,\bZ_2)$ of the $\bZ_2$ one-form symmetry then enters in the exponentiated action as \begin{equation}
\exp\left( 2\pi i \frac12 \int_X B w_2(c) \right)\label{magnetic}
\end{equation} where $c$ is the $\SO(2n_c)$ gauge bundle.

We now introduce a background bundle $f$  for the flavor symmetry $\SO(2n_f)/\bZ_2$.
Recall that the matter fields are in the bivector of $\SO(2n_c)\times \SO(2n_f)$.
Therefore, the gauge bundle $c$ is in general an $\SO(2n_c)/\bZ_2$ bundle, such that $v_2(c)=v_2(f)$.
This does not pose a problem when $n_c$ is even, since $w_2$ and $v_2$ exist independently as a $\bZ_2$-valued class, as we recalled in Sec.~\ref{sec:math}.
When $n_c$ is odd, however, there is a potential problem, since $w_2(c)$ is no longer a closed cochain in general, but satisfies $\delta w_2(c)=\beta v_2(c)=\beta v_2(f)$ as in \eqref{asin}.
Therefore we find that \begin{equation}
\delta (B w_2(c)) = B \beta v_2(f).
\end{equation}
This means that the non-closed-ness of the coupling \eqref{magnetic}
is purely given by a combination of the background fields,
and can be cancelled by putting the 4d theory on the boundary $X$ of the 5d bulk $Y$ with the coupling \begin{equation}
\exp\left(2\pi i \frac12 \int_Y B \beta v_2(f)\right)
\label{anom}
\end{equation}
We again note that $\beta v_2(f)=0$ when $n_f$ is odd while it is nontrivial when $n_f$ is even.
We should also pose here to mention that the analysis up to this point shows that
the $\bZ_2$ one-form symmetry and the $\SO(2n_f)/\bZ_2$ flavor symmetry remain a direct product,
and do not form a nontrivially-extended 2-group.

Summarizing, we found that the $\SO(2n_c)_+$ theory has a mixed anomaly when $n_c$ is odd and $n_f$ is even, and anomaly-free otherwise.
The anomaly is between the $\bZ_2$ 1-form symmetry and the $\SO(2n_f)/\bZ_2$ 0-form flavor symmetry  and is given by \eqref{anom}.

Before continuing, we recall that the $\SO(2n_c)_+$ theory is obtained by gauging the electric $\bZ_2$ 1-form symmetry (with the background field $E$) of the $\Spin(2n_c)$ theory,
while the $\Spin(2n_c)$ theory is obtained by gauging the magnetic $\bZ_2$ 1-form symmetry (with the background field $B$) of the $\SO(2n_c)_+$ theory \cite{Kapustin:2014gua}. 
In Sec.~3.2 of \cite{Tachikawa:2017gyf}, it was already shown that when the electric background $E$ satisfies the extension of the form \eqref{ext}, the magnetic background $B$ have the anomaly of the form \eqref{anom}, 
where a general element $\Omega\in H^3(BG,\bZ_2)$ was used instead of our specific choice $\beta v_2(f)$.
The analysis in \cite{Tachikawa:2017gyf} was general but no concrete example was provided.
The new point here is that a 4d $\so$ quantum chromodynamics provides a concrete example.

\newpage

\subsection{Appearance of 2-group in the $\SO(2n_c)_-$ theory}
Let us finally study the $\SO(2n_c)_-$ theory.
This theory has a $\bZ_2$ 1-form symmetry,
whose charged object is the dyonic line $WH$.
Its square $(WH)^2$ when $n_c$ is odd is a gauge Wilson line in the vector representation,
which is equivalent to a flavor Wilson line in the vector representation.
This behavior is the same as the $\Spin(2n_c)$ theory with odd $n_c$,
and therefore we have the same nontrivial extension \eqref{2group}:
\begin{equation}
0\to \bZ_2[1] \to  H \to \SO(2n_f)/\bZ_2 \to 0.
\end{equation}
The extension should then be given by \eqref{ext}: \begin{equation}
\delta B= \beta v_2(f),
\label{ext-}
\end{equation} where we denoted the background field for $\bZ_2$ 1-form symmetry by $B$.

Let us see how the relation \eqref{ext-} can be understood from the point of view of the Lagrangian.
The issue is the discrete theta angle term \eqref{pont}.
Together with the magnetic coupling to $B$, we have the following contribution to the exponentiated action \begin{equation}
\exp\left(2\pi i\int_X ( \frac14 \mathfrak{P}(w_2(c)) +\frac12 B w_2(c))\right).
\label{boo}
\end{equation}
When $n_c$ is odd, $w_2(c)$ is not necessarily closed.
Then the second term in \eqref{boo} is not closed, 
and to even talk about the first term in \eqref{boo}, one first needs to extend the definition of the Pontryagin square $\fP$ to non-closed cochains.

Let us show that the coupling \eqref{boo} can be made a well-defined, non-anomalous coupling after an addition of a counterterm, when $B$ satisfies the extension condition \eqref{ext-}.
To do this, we recall that the non-closed-ness of $w_2(c)$ is governed by the \begin{equation}
\delta w_2(c)=\beta v_2(c)= \beta v_2(f), 
\end{equation} see \eqref{asin}.
Combining with \eqref{ext-}, we see $w_2(c)+B$  is closed. 
Therefore we can always consider the well-defined coupling \begin{equation}
\exp \left(2\pi i \frac14 \int_X \fP(w_2(c)+B)\right) .
\label{aho}
\end{equation}
In the special case when $B$ and $w_2(c)$ are closed, we can use the standard formula $\fP(x+y)=\fP(x)+\fP(y)+2 xy$ to show that the expression \eqref{aho} equals
\begin{equation}
= \exp\left(2\pi i \int_X 
 ( \frac14 \mathfrak{P}(w_2(c)) +\frac12 B w_2(c) +\frac14 \mathfrak{P}(B) )
\right) .
\label{fPB}
\end{equation}

This means that the well-defined expression \eqref{aho} equals the naive expression \eqref{boo} 
up to an addition of the Pontryagin square of the background field $B$ and the terms which vanish when $ w_2(c)$ and/or $B$ are closed.
This is what we wanted to demonstrate.
Note that the $\SO_-$ theory with a general 0-form symmetry background necessarily involves the pure background term $\fP(B)$ in it.
We will come back to this point in Sec.~\ref{sec:last}.

\begin{table}
\centering
\begin{tabular}{ll}
				$\Spin$: &
\begin{tabular}{l|cc}
	 & $n_c$ even & $n_c$ odd\\
		\hline
		$n_f$ even   & -- &  extension \\
		$n_f$ odd    & -- & --
\end{tabular} \\[2em]
 $\SO_+$:  &
\begin{tabular}{l|cc}
		 & $n_c$ even & $n_c$ odd\\
		\hline
		$n_f$ even   & -- &  anomaly \\
		$n_f$ odd    & -- & --
\end{tabular} \\[2em]
$\SO_-$: &
\begin{tabular}{l|cc}
				 & $n_c$ even & $n_c$ odd\\
		\hline
		$n_f$ even   & -- &  extension \\
		$n_f$ odd    & -- & --
\end{tabular} 
\end{tabular} 
\caption{The extension and the anomaly of the $\so(2n_c)$ gauge theory with $N_f=2n_f$ flavors, in the three cases $\Spin$, $\SO_+$ and $\SO_-$.
The symbol -- signifies that there is neither nontrivial extension nor nontrivial anomaly.
\label{tab}}
\end{table}

\subsection{Summary}
Let us summarize what we found. 
We studied the interrelationship of the $\bZ_2$ 1-form symmetry of the $\Spin(2n_c)$, $\SO(2n_c)_+$ and $\SO(2n_c)_-$ theories and 
their $\SO(2n_f)/\bZ_2$ flavor symmetry. 
We found the  behavior summarized in Table~\ref{tab}.

The Seiberg duality maps $\mathfrak{so}(N_c)$ with $N_f$ flavors with $\mathfrak{so}(N_c')$ with $N_f$ flavors,
where $N_c'=N_f+4-N_c$.
In terms of $N_c=2n_c$ and $N_f=2n_f$, this means $n_c'=n_f+2-n_c$.
Therefore it acts on the parity of $n_c$ and $n_f$  as 
\begin{center}
	\begin{tabular}{l|cc}
		& $n_c$ even & $n_c$ odd\\
		\hline
		$n_f$ even   & $\circlearrowleft$ & $\circlearrowleft$\\
		$n_f$ odd    & \multicolumn{2}{c}{$\xleftrightarrow{\qquad\ }$}
	\end{tabular},
\end{center}
and we also know that $\Spin$ and $\SO_-$ are exchanged while $\SO_+$ is self-dual.
We see that the information summarized in Table~\ref{tab} is consistent with this action of the Seiberg duality.

\subsection{A comment on $\Spin\leftrightarrow\SO_-$ duality}
\label{sec:last}
Let us consider the situation with a general flavor background $f$ for the 0-form $\SO(2n_f)/\bZ_2$ symmetry.
The analysis in this paper shows, at least when $n_f$ is even and $n_c$ is odd, 
that the $\SO_-$ theory requires the coupling $\fP(B)$ to be present in the action, 
see the discussions around \eqref{fPB}.
Conversely, we can \emph{not} introduce the coupling $\fP(E)$ in the dual $\Spin$ theory, 
since $E$ is not closed in general and $\fP(E)$ alone does not make sense.
This means the following, even after turning off the 0-form flavor background $f$, at least when $n_f$ is even and $n_c$ is odd:
\begin{claim}
The $\Spin\leftrightarrow\SO_-$ duality maps
the $\Spin$ theory \emph{without} the $\fP(E)$ discrete theta angle to
the $\SO$ theory \emph{with} the $\fP(B)$ discrete theta angle,
where the background fields $E$ and $B$ are of course identified across the duality.
\end{claim}
Let us show that this property holds generally under the Seiberg duality between the $\Spin(N_c)$ theory with $N_f$ flavors and the $\SO(N_c')_-$ theory with $N_f$ flavors, where $N_c+N_c'=N_f+4$,
without any restriction on the values of $N_c$ and $N_f$.

To see this, we first give a large non-zero mass term to the flavors in the electric description,
and perform the corresponding deformation on the magnetic side.
The system is in the confined phase. 
We put the system in a large compact spacetime, and 
study the dependence of the phase of the partition function on the background field $E$ or $B$ for the 1-form symmetry.

Consider the $\Spin$ theory without the $\fP(E)$ discrete theta term.
Recall that the 1-form symmetry background $E$ is the Stiefel-Whitney class $w_2(c)$ of the gauge bundle $c$,
which is physically known as the 't Hooft flux. 
The system is confining, and therefore the 't Hooft flux is screened,
and the phase of the partition function on a large compact spacetime is independent of it, i.e.~
\begin{equation}
\text{$Z^\Spin(E=w_2(c))$ is independent of $E$.}
\label{AAA}
\end{equation}

Consider next the $\SO_-$ theory without the $\fP(B)$ discrete theta term.
The partition function is of the form \begin{equation}
	Z^{\SO_-}(B)\propto \sum_{w_2(c)}  Z^\Spin(w_2(c)) e^{2\pi i \int (\frac14 \mathfrak{P}(w_2(c)) +\frac12 B w_2(c)) }
	 \propto e^{2\pi i \frac14 \int \mathfrak{P}(B)} \label{BBB}
\end{equation} which also means that  \begin{equation}
\text{$Z^{\SO_-}(B) e^{2\pi i \frac14 \mathfrak{P}(B)} $ is independent of $B$.}
\label{CCC}
\end{equation}
Comparing \eqref{AAA}, \eqref{BBB} and \eqref{CCC},
we see that the dual of the $\Spin$ theory without $\fP(E)$ is the $\SO_-$ theory with $\fP(B)$.

This simple argument does not determine how the $\SO_+$ theories with and without $\fP(B)$ interaction are mapped among themselves.
This is because \begin{equation}
	Z^{\SO_+}(B)\propto \sum_{w_2(c)}  Z^\Spin(w_2(c)) e^{2\pi i \int \frac12 B w_2(c) } 
	 \propto \delta(B)
\end{equation} and therefore both $Z^{\SO_+}(B)$ 
and $Z^{\SO_+}(B) e^{2\pi i \frac14 \int \fP(B)}$ 
are proportional to a delta function $\delta(B)$ of the background field $B$.

\section*{Acknowledgements}
Y.L.~is partially supported by the Programs for Leading Graduate Schools, MEXT, Japan, via the Leading Graduate Course for Frontiers of Mathematical Sciences and Physics. 
Y.T.~is partially supported  by JSPS KAKENHI Grant-in-Aid (Wakate-A), No.17H04837 
and JSPS KAKENHI Grant-in-Aid (Kiban-S), No.16H06335,
and also by WPI Initiative, MEXT, Japan at IPMU, the University of Tokyo.

\bibliographystyle{ytphys}
\baselineskip=.95\baselineskip
\bibliography{ref}

\end{document}

### 2021-06-01 memo.tex
minor changes to compile cleanly
some references on monopoles

@@
 %% Comment
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
+%\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
 
@@
 
+\section{Duality map}
+
+The duality map among $Spin$, $SO_+$ and $SO_-$ was first found in \cite{Aharony:2013hda}
+ \begin{equation}
+\begin{array}{ccc}
+	Spin(N_c) & \leftrightarrow & SO_-(N_c'),\\
+	SO_+(N_c) & \leftrightarrow & SO_+(N_c'),\\
+	SO_-(N_c) & \leftrightarrow & Spin(N_c')
+\end{array}
+\end{equation} where $N_c'=N_f-N_c+4$.
+
+Razamat-Willett \cite{Razamat:2013opa} performed a rather extensive check of this mapping by means of localization on the lens space times $S^1$.
+
+Note that there is a natural action of $SL(2,\bZ)$ on the theories with $\bZ_2$ 1-form symmetry.
+Requiring that this is compatible with the Seiberg duality, one finds that the mapping should in fact be  \begin{equation}
+\begin{array}{ccc}
+	Spin(N_c) & \leftrightarrow & T(SO_-(N_c')),\\
+	SO_+(N_c) & \leftrightarrow & T(SO_+(N_c')),\\ 
+	SO_-(N_c) & \leftrightarrow & T(Spin(N_c'))
+\end{array}
+\end{equation} 
+as discussed in \cite[Sec.~6]{Gaiotto:2014kfa} and \cite{Bhardwaj:2020ymp}.
+
+\section{References on fermionic zero modes on monopoles}
+
+Index theorem on the monopole background: 
+Callias \cite{Callias:1977kg} Bott and Seeley \cite{Bott:1978bw}\footnote{%
+These are on CMP. 
+Papers on CMP are not open access via Springer (which is reachable by doi) but is open access at Project Euclid. 
+I'd like a way to include links in the references appropriately.
+}
+
+General reviews: Harvey \cite[Lecture 4]{Harvey:1996ur}.
+
 \section{Explicit configurations detecting anomalies}
@@
 All cohomologies in this section is $\bZ_2$-valued.
+
+This is to confirm that these expressions are not secretly trivial.
 
@@
 
+\if0
 To see this, we need to compute the eta invariant under an explicit configuration where $\int w_2 \beta w_2'=1$. 
@@
 and we just have to count the zero modes.
+\fi
 
@@
 \begin{equation}
-	\begin{tikzpicture}[thick,baseline=(m-2-1.south)]
+	\begin{tikzpicture}[thick,baseline=(m-2-4.south)]
 		\matrix (m) [

### 2021-06-02 memo.tex
spin bordism of K(Z4,2)

@@
 
+\section{misc}
+
+\subsection{$\bZ_4$ 1-form symmetry}
+According to \cite[Appendix C.3]{Clement2002} and \cite[Eq.\,(6.3)]{Wan:2018bns}, it seems that we have
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(K(\bZ_4,2);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_4,2))\vspace{4mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2$}}} & \ast\\
+			0 & \bZ &  & \bZ_4 &  & \red{\dbox{\black{$\bZ_8$}}} & \Blue{\dbox{\black{$\bZ_2$}}} \cellcolor{lightyellow} & \ast\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & \ast\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ_4\\
+			3  & \\
+			2  & \bZ_4\\
+			1  & \\
+			0 & \\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+
+\newpage
+
 \bibliographystyle{ytphys}

### 2021-06-03 memo.tex
't Hooft-Polyakov monopole argument

@@
 
+\section{'t Hooft-Polyakov monopole argument}
+For an $SU(2)$ gauge theory Higgssed by an adjoint ($\bm{3}$, spin-$1$, isovector) scalar,
+the gauge group is broken down to $U(1)$, and correspondingly it accommodates topological solitons (monopoles):
+\begin{equation*}
+	\pi_2\left(
+		\dfrac{SU(2)}{U(1)}
+	\right) = \bZ.
+\end{equation*}
+In the presence of (additional) fermions, this monopole might acquire non-trivial charge under
+spacetime-Lorentz or flavor symmetries, depending on the representation of the fermions under $SU(2)$ gauge symmetry:
+\begin{equation*}
+	\begin{tabular}{c||cccc}
+		fermion gauge rep. & number of zero-modes & spin of zero-modes& spin of monopole & flavor rep.\\
+		\hline
+		$\bm{2}$ & $1$ & $0$ & $0$ & spinor\\
+		$\bm{3}$ & $2$ & $\tfrac{1}{2}$ & \\
+		$\bm{4}$ & $4$ & $0\oplus 1$ & $\tfrac{1}{2}$\\
+	\end{tabular}
+\end{equation*}
+The numbers of zero-modes can be computed from the Callias index theorem\cite{Callias:1977kg}.
+
+According to \cite{Wang:2018qoy},
+there is a $w_2(TM_4)\beta w_2(SU(2)_{\text{gauge}})$ anomaly for a fermion in $\bm{4}$ charged under
+\begin{equation*}
+	\dfrac{Spin(4)_{\text{spacetime}} \times SU(2)_{\text{gauge}}}{\bZ_2},
+\end{equation*}
+which incarnates in the IR as an ill-definition of the effective interaction $w_2(TM) c_1(U(1)_{\text{gauge}})$,
+emerging after integrating out the fermion which obtained mass through Yukawa coupling.
+This effective interaction term should arise in order to make the monopole a fermion,
+but is not well-defined without a trivialization of $w_2(TM_4)$ or equivalently a spin structure.
+
+This situation looks quite similar to our problem where the fermions are charged under
+\begin{equation*}
+	\dfrac{SO(4)_{\text{gauge}} \times SU(2)_{\text{flavor}}}{\bZ_2}.
+\end{equation*}
+Therefore, by breaking $SU(2)_{\text{flavor}}$ to $U(1)_{\text{flavor}}$
+and examining the charge of the corresponding monopole under the remaining gauge group,
+one might be able to find out that there is a similar problem,
+which implies the existence of $w_2\beta w_2$ anomaly in the first place as desired.
+
+Also, one should be able to generalize this whole argument to the case of fermions charged under
+\begin{equation*}
+	\dfrac{SO(2n_c)_{\text{gauge}} \times SU(2n_f)_{\text{flavor}}}{\bZ_2}
+\end{equation*}
+by breaking $SU(2n_f)_{\text{flavor}}$ to $SO(2n_f)_{\text{flavor}}$,
+since there are monopoles characterized by
+\begin{equation*}
+	\pi_2\left(
+		\dfrac{SU(2n_f)}{SO(2n_f)}
+	\right)
+	=
+	\left\{
+		\begin{array}{cl}
+			\bZ_2 & (n_f \geq 2)\\
+			\bZ & (n_f = 1)
+		\end{array}
+	\right..
+\end{equation*}
+
+\newpage
+
 \section{misc}

### 2021-06-03 memo.tex
't Hooft-Polyakov monopole argument v2

@@
 	\begin{tabular}{c||cccc}
-		fermion gauge rep. & number of zero-modes & spin of zero-modes& spin of monopole & flavor rep.\\
+		fermion gauge rep. & number of zero-modes & spin of zero-modes& spin of monopole\\
 		\hline
-		$\bm{2}$ & $1$ & $0$ & $0$ & spinor\\
-		$\bm{3}$ & $2$ & $\tfrac{1}{2}$ & \\
+		$\bm{2}$ & $1$ & $0$ & $0$\\
+		$\bm{3}$ & $2$ & $\tfrac{1}{2}$\\
 		$\bm{4}$ & $4$ & $0\oplus 1$ & $\tfrac{1}{2}$\\
@@
 According to \cite{Wang:2018qoy},
-there is a $w_2(TM_4)\beta w_2(SU(2)_{\text{gauge}})$ anomaly for a fermion in $\bm{4}$ charged under
+there is $w_2(TM_4)\beta w_2(SU(2)_{\text{gauge}})$ anomaly for a fermion in $\bm{4}$ charged under
 \begin{equation*}
@@
 emerging after integrating out the fermion which obtained mass through Yukawa coupling.
-This effective interaction term should arise in order to make the monopole a fermion,
+This effective interaction term should arise in order to make the monopole a fermion
+(\textit{i.e.}\,spinor representation of $Spin(4)_{\text{spacetime}}$),
 but is not well-defined without a trivialization of $w_2(TM_4)$ or equivalently a spin structure.
@@
 \end{equation*}
-Therefore, by breaking $SU(2)_{\text{flavor}}$ to $U(1)_{\text{flavor}}$
-and examining the charge of the corresponding monopole under the remaining gauge group,
-one might be able to find out that there is a similar problem,
-which implies the existence of $w_2\beta w_2$ anomaly in the first place as desired.
+Since fermions are in the fundamental representation of the flavor symmetry,
+breaking $SU(2)_{\text{flavor}}$ to $U(1)_{\text{flavor}}$ gives rise to
+a monopole in the spinor representation this time of the $SO(4)_{\text{gauge}}$\cite{Harvey:1996ur}.
+Therefore by the same logic, one can deduce that there should be
+$w_2(SO(4)_{\text{gauge}})\beta w_2(SU(2)_{\text{flavor}})$ anomaly in the first place, as desired.
 
@@
 by breaking $SU(2n_f)_{\text{flavor}}$ to $SO(2n_f)_{\text{flavor}}$,
-since there are monopoles characterized by
+where we have monopoles characterized by
 \begin{equation*}

### 2021-06-04 memo.tex
spin bordism of K(Z2×Z2,2)

@@
 		\end{array}
-		& \longrightarrow & 
+		& \quad\longrightarrow & 
 		\begin{array}{c|c}
@@
 
+\subsection{$\bZ_2\times \bZ_2$ 1-form symmetry}
+Exploiting the fact that $K(\bZ_2\times \bZ_2, 2) = K(\bZ_2, 2) \times K(\bZ_2, 2)$,
+it seems that we have
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(K(\bZ_2\times \bZ_2,2);\Omega_q^{\text{spin}}\big)
+		&& \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_2\times \bZ_2,2))\vspace{4mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\red{\fbox{\black{$\bZ_2^{\oplus 3}$}}}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2^{\oplus 6}$}}} & \ast\\
+			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\dbox{\black{$\bZ_4^{\oplus 2}\oplus \bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \quad\longrightarrow & 
+		\begin{array}{c|c}
+			6  & \ast\\
+			5  & \bZ_2\cellcolor{lightyellow}\\
+			4  & \bZ_2^{\oplus 3}\\
+			3  & \\
+			2  & \bZ_2^{\oplus 2}\\
+			1  & \\
+			0 & \\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+The $\bZ$ homology of $K(\bZ_2, 2)$ is again read off from \cite{Clement2002},
+while the $\bZ_2$ (co)homology is known \cite{Serre1953} to be
+\begin{equation*}
+	H^\ast(K(\bZ_2,2);\bZ_2)
+	=
+	\bZ_2[x_2, Sq^1 x_2, Sq^2Sq^1 x_2, \cdots].
+\end{equation*}
+
 \newpage

### 2021-06-04 memo.tex
explicit bordism invariants

@@
 
+The corresponding invariant in 4d is simply \begin{equation}
+\exp(2\pi i \frac{p}{4} \int \frac12\mathfrak{P}(a) )
+\end{equation}
+where $\mathfrak{P}:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
+which is even mod 8 on a spin manifold.
+
 \subsection{$\bZ_2\times \bZ_2$ 1-form symmetry}
@@
 
+The corresponding bordism invariants in 4d are $\mathfrak{P}(a)/2$, $ab$, $\mathfrak{P}(b)/2$, 
+and the one in 5d is $a\beta b$.
+
 \newpage

### 2021-06-07 memo.tex
alternative approach

@@
 \fi
+
+\section{Via direct study of line operators}
+
+Let's determine the anomaly/extension of so SQCD by studying the line operators.
+Here I concentrate on the case of $SO(2n_c)_\pm$ with $2n_f$ flavors.
+
+Let us first consider the case of pure $SO(2n_c)_\pm$ with $n_c$ odd,
+and recall how to distinguish $\bZ_2\times \bZ_2$ or $\bZ_4$.
+
+In either case, the group of the charges of the line operators has the structure \[
+0\to \bZ_2 \to G \to \bZ_2 \to 0
+\] where the $\bZ_2$ subgroup is generated by the 't Hooft line
+and the $\bZ_2$ quotient is generated by the Wilson line in the vector representation.
+To tell whether $G$ is $\bZ_2\times \bZ_2$ or $\bZ_4$,
+we simply take two 't Hooft lines.
+When combined, it is a charge-2 't Hooft line, which can be screened by the dynamical monopole of this charge.
+In the $SO_+$ theory, this dynamical monopole is electrically neutral,
+while the $SO_-$ theory, it has the electric charge equal to the vector representation.
+Therefore, the charge-2 't Hooft line is equivalent to having no line operator in $SO_+$ theory,
+while it is equivalent to having a Wilson line in the vector representation in $SO_-$.
+We find that $G$ is $\bZ_2\times \bZ_2$ for $SO_+$ and $\bZ_4$ for $SO_-$.
+
+We learned the important lesson: 
+the 1-form symmetry group is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on 
+whether the electric charge of the dynamical monopole of an appropriate charge is 
+neutral or vector.
+
+So we would like to determine that in the $SO$ SQCD,
+but the direct analysis of dynamical monopoles in this theory is hard.
+For this purpose, we make the following deformations which do not change the symmetry structure:
+\begin{itemize}
+\item We reduce the flavor symmetry from $su(2n_f)$ to $usp(2n_f)$.
+\item We add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +cc$, where $J_{[ij]}$ is the constant matrix for the $usp(2n_f)$ part.
+\item We give a vev to $\Phi_{ab}$ to break $so(2n_c)$ to $so(2)^{n_c}$.
+\end{itemize}
+The 't Hooft line of the original $SO(2n_c)$ theory is in the `vector' class
+$(1,0,\ldots,0)$ under $so(2)^{n_c}$,
+and therefore the dynamical monopole we need to analyze has the charge $(2,0,\ldots,0)$.
+
+Since the fermions are in the vector representation of $so(2n_c)$,
+they are charge 2 under the $so(2)$, and should give rise to fermionic zero modes transforming in \begin{equation}
+V_{2} \otimes R_{2n_f} 
+\end{equation} where $V_2$ is the doublet of spacetime $so(3)$, 
+$R_{2n_f}$ is the fundamental of $usp(2n_f)$,
+and we need to impose the reality condition using the pseudoreality of both factors,
+so that there are $4n_f$ Majorana fermion in total.
+
+I haven't analyzed the general case; let's take $n_f=1$ and $n_f=2$ as examples.
+When $n_f=1$, there are $4$ Majorana fermions.
+Quantizing them, we find the monopoles in \begin{equation}
+V_2 \otimes \mathbf{1} \oplus \mathbf{1}\otimes R_2.
+\end{equation}
+I think we should take the spacetime scalar as indicative, (which needs to be justified)
+so it has the `vector' charge under $usp(2)$ flavor symmetry.
+Therefore the 1-form symmetry is extended.
+
+When $n_f=2$, there are $8$ Majorana fermions, 
+and spatial $su(2)$ and flavor $usp(4)$ are embedded into $so(8)$ via \begin{equation}
+su(2)\times usp(4) \simeq so(3)\times so(5) \subset so(8).
+\end{equation}
+Therefore, the monopoles are easily seen to be in \begin{equation}
+V_3\otimes \mathbf{1} \oplus V_2\otimes R_2 \oplus V_1\otimes R_5.
+\end{equation}
+Again taking the spacetime scalar part, it is in the `adjoint' charge under the $usp(4)$ flavor symmetry.
+Therefore the 1-form symmetry is not extended.
+
+So far we considered $SO_+$ theories. 
+In $SO_-$ theories, we need to add electric charges coming from the discrete theta angle.
+This is trivial if $n_c$ is even, but is the `vector' charge if $n_c$ is odd.
 

### 2021-06-08 memo.tex
better treatment of monopoles of so(2nc)

@@
 $(1,0,\ldots,0)$ under $so(2)^{n_c}$,
-and therefore the dynamical monopole we need to analyze has the charge $(2,0,\ldots,0)$.
+and therefore the dynamical monopole we need to analyze has the charge in the `adjoint' class.
+
+The monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, see e.g.~\cite{Gauntlett:1996cw}.\footnote{%
+There were many competing papers from the same period concerning the application to Seiberg-Witten;
+the analysis of the monopoles itself is much older and I should find proper original references for it too.
+}
+The upshot is that you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole using any simple root into $G$ and have a monopole solution without additional bosonic moduli.
+
+So we consider a monopole with the charge $(1,1,0,\ldots,0)$.
+This uses $su(2)_1$ within $so(4)\simeq su(2)_1\times su(2)_2$ within $so(2n_c)\subset so(4)\times so(4n_c-4)$.
 
 Since the fermions are in the vector representation of $so(2n_c)$,
-they are charge 2 under the $so(2)$, and should give rise to fermionic zero modes transforming in \begin{equation}
+the charged part under $su(2)_1$ is of charge 1 and in the doublet of $su(2)_2$.
+Therefore it gives rise to fermionic zero modes transforming in \begin{equation}
 V_{2} \otimes R_{2n_f} 
-\end{equation} where $V_2$ is the doublet of spacetime $so(3)$, 
+\end{equation} where $V_2$ is the doublet of $su(2)_2$, 
 $R_{2n_f}$ is the fundamental of $usp(2n_f)$,
@@
 \end{equation}
-I think we should take the spacetime scalar as indicative, (which needs to be justified)
-so it has the `vector' charge under $usp(2)$ flavor symmetry.
-Therefore the 1-form symmetry is extended.
+%I think we should take the spacetime scalar as indicative, (which needs to be justified)
+It has the `vector' charge under $usp(2)$ flavor symmetry or is a doublet under $su(2)_2$.
+In either case, the $-1$ in $SO(2n_c)\times USp(2n_f)$ acts nontrivially,
+and the 1-form symmetry is extended.
 
 When $n_f=2$, there are $8$ Majorana fermions, 
-and spatial $su(2)$ and flavor $usp(4)$ are embedded into $so(8)$ via \begin{equation}
+and  $su(2)_2$ and flavor $usp(4)$ are embedded into $so(8)$ via \begin{equation}
 su(2)\times usp(4) \simeq so(3)\times so(5) \subset so(8).
@@
 \end{equation}
-Again taking the spacetime scalar part, it is in the `adjoint' charge under the $usp(4)$ flavor symmetry.
+Again,
+it is in the `adjoint' charge under the $usp(4)$ flavor symmetry.
 Therefore the 1-form symmetry is not extended.

### 2021-06-09 memo.tex
spin bordism of B([SO(4n+2)×SU(2m)]/Z2)

@@
 	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right))\vspace{4mm}\\
+		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
 		\begin{array}{c|c:cccccccccccc}
@@
 			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \longrightarrow & 
-		\begin{array}{c|c}
-			6  & ?\\
-			5  & ?\cellcolor{lightyellow}\\
-			4  & ?\\
-			3  & ?\\
-			2  & \bZ_2^{\oplus 2}\\
-			1  & \\
-			0 & \\
-			\hline\\
 		\end{array}
@@
 
+\section{Computation of $\Omega_5^{\mathrm{spin}}\big(
+	B\big(
+		\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}
+	\big)
+\big)$}
+
+\subsection{Cohomology of $BPSO(4n'_c+2)$}
+Recalling that the $\bZ_2$ cohomology read off from \cite{KonoMimura1974}
+allowed us to determine the $\bZ$ cohomology by using Bockstein SS
+(see \texttt{wzw-memo.pdf}, copy later), we had
+\begin{equation}
+	\renewcommand{\arraystretch}{1.2}
+	\begin{array}{c|cccccccccccccccc}
+		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
+		\hline
+		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ)} & \bZ & 0 & 0 & \bZ_4 & \bZ & 0 & \bZ_2 & \cdots\\
+		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ_2)} & \bZ_2 & 0 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2^{\oplus 2} & \cdots\\
+		\hline
+		\text{generator} \,(\bZ_2) & 1 & - & a_2 & y'(1) & (a_2)^2 & y'(2) & (a_2)^3 & \cdots\\
+		&&&&&&& y'(1)^2\\
+	\end{array}
+\end{equation}
+and if we assume the suspension $\bar\theta: H^\ast(PSO(4n'_c+2);\bZ_2) \to H^\ast(BPSO(4n'_c+2);\bZ_2)$
+to commute with Steenrod squares (which seems to be true according to Nishimoto-san's notes),
+then these elements are supposed to be related as
+\begin{equation*}
+	\begin{array}{ccl}
+		\beta_2 a_2 & = & y'(1)\\
+		Sq^2 y'(1) & = & y'(2)\\
+		Sq^1 y'(2) & = & y'(1)^2\\
+	\end{array}
+\end{equation*}
+where $\beta_f$ is a higher Bockstein operator, whose image corresponds to $\bZ_{2^f}$ in integral cohomology.
+
+\subsection{Leray-Serre SS (preparatory)}
+For the fibration
+\begin{equation}
+	BSU(2n_f)
+	\ \to\ 
+	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
+	\ \to\ 
+	BPSO(4n'_c+2)
+\end{equation}
+we have
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6  & \bZ &&& \ast & \ast && \ast\\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast & & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  &&  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & \bZ\oplus \bZ_2^{\oplus 2}\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 2}\\
+			3  & \bZ_4\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+
+\subsection{Atiyah-Hirzebruch SS}
+Having obtained (co)homology groups,
+one can fill in the $E^2$-page of the AHSS:
+\begin{equation}
+	\begin{array}{c}
+		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
+			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+	\end{array}
+\end{equation}
+Based on our belief, 
+\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
+\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 a_2 & = & (a_2)^2
+	\end{array}
+\end{equation}
+and also
+\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
+\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 y'(1) & = & y'(2)\\
+	\end{array}
+\end{equation}
+and finally
+\green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 c_2 & = & c_3
+	\end{array}
+\end{equation}
+then %one can proceed, and 
+the would-be-$E_3$-page is given by
+\begin{equation}
+	\begin{array}{c|c:cccccccccccc}
+		6  &&&&&& \\
+		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
+		2  & \bZ_2 &&& \cellcolor{lightyellow} & \ast & \ast & \ast\\
+		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
+		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \bZ_2\cellcolor{lightyellow} & \ast\\
+		\hline
+		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+	\end{array}
+\end{equation}
+
+%\subsection{Adams SS}
+%The above analysis might be complemented by Adams SS.
+%According to our naive guess,
+%the module $\widetilde H^\ast(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
+%\begin{equation}
+%	\begin{tikzpicture}[thick,baseline=(m-2-4.south)]
+%		\matrix (m) [
+%			matrix of math nodes,
+%			row sep= 1em,
+%			column sep=6em,
+%		]{
+%			& \colorB{\bullet} \\
+%			& \colorB{\bullet} & \colorC{\bullet}\\
+%		    & \colorB{\bullet} & \\
+%			\colorA{\bullet} && \colorC{\bullet}\\
+%			& \colorB{\bullet} & \\
+%			\colorA{\bullet} &&\\
+%		};
+%		\draw[colorA] (m-4-1.center) to [out=200, in=160] (m-6-1.center);
+%		%
+%		\node[colorA, right=4pt] at (m-6-1) {$a_2$};
+%		\node[colorA, right=4pt] at (m-4-1) {$(a_2)^2$};
+%		%
+%		\draw[colorB] (m-5-2.center) to [out=160, in=200] (m-3-2.center);
+%		\draw[colorB] (m-3-2.center) to (m-2-2.center);
+%		\draw[colorB] (m-3-2.center) to [out=160, in=200] (m-1-2.center);
+%		%
+%		\node[colorB, right=4pt] at (m-5-2) {$y'(1)$};
+%		\node[colorB, right=4pt] at (m-3-2) {$y'(2)$};
+%		\node[colorB, right=4pt] at (m-2-2) {$y'(1)^2$};
+%		\node[colorB, right=4pt] at (m-1-2) {$y'(3)$};
+%		%
+%		\draw[colorC] (m-2-3.center) to [out=200, in=160] (m-4-3.center);
+%		%
+%		\node[colorC, right=4pt] at (m-4-3) {$c_2$};
+%		\node[colorC, right=4pt] at (m-2-3) {$c_3$};
+%	\end{tikzpicture}
+%\end{equation}
+%This leads to the following Adams chart:
+%\begin{center}
+%	\begin{sseqdata}[
+%		name=M2,
+%		Adams grading,
+%		classes = fill,
+%		xrange = {0}{5},
+%		yrange = {0}{3},
+%		%,x label = {$t-s$}, y label = {$s$}
+%	]
+%		\tower[colorA](2,0)
+%		\tower[colorA](4,1)
+%		\class[white](4,0)
+%		\tower[colorC](4,0)
+%	\end{sseqdata}
+%	\printpage[name = M2,page = 2]
+%\end{center}
+
+\newpage
+
 \section{'t Hooft-Polyakov monopole argument}

### 2021-06-10 memo.tex
refinements in counting zero modes

@@
 
-The monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, see e.g.~\cite{Gauntlett:1996cw}.\footnote{%
-There were many competing papers from the same period concerning the application to Seiberg-Witten;
-the analysis of the monopoles itself is much older and I should find proper original references for it too.
-}
-The upshot is that you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole using any simple root into $G$ and have a monopole solution without additional bosonic moduli.
+The monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, 
+e.g.~in \cite{Weinberg:1979zt}.
+There, the following was shown.
+Let $\phi$ be the scalar vev in the real Cartan subalgebra $\mathfrak{h}\subset \mathfrak{g}$.
+This determines the simple roots $\alpha$.
+Then you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole and have a monopole solution without additional bosonic moduli.
 
-So we consider a monopole with the charge $(1,1,0,\ldots,0)$.
-This uses $su(2)_1$ within $so(4)\simeq su(2)_1\times su(2)_2$ within $so(2n_c)\subset so(4)\times so(4n_c-4)$.
+Let us say we chose the standard $\phi$ such that the simple roots are $(1,-1,\ldots,0)$,
+$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)$.
+They generate the sublattice $\Lambda$ of $\bZ^n$.
+The group of the 't Hooft line operators up to the screening by the dynamical monopoles is then \begin{equation}
+\bZ^n / \Lambda = \bZ_2.
+\end{equation}
+What we want to do is take into account the center charge $\bZ_2$ of $USp(2n_f)$. 
+For this, we consider $\bZ^n\times \bZ_2$,
+and divide it by the subgroup generated by the charges of the monopoles associated to the simple roots,
+which we denote by $(1,-1,\ldots, 0; q_1)$, $(0,1,-1,\ldots, 0; q_2)$, \ldots,
+$(0,\ldots, 1,-1; q_{n-1})$ and $(0,\ldots,1,+1; q_n)$.
 
-Since the fermions are in the vector representation of $so(2n_c)$,
-the charged part under $su(2)_1$ is of charge 1 and in the doublet of $su(2)_2$.
-Therefore it gives rise to fermionic zero modes transforming in \begin{equation}
+We do not have to determine $q_1$ to $q_{n-1}$. We simply use them to rewrite any charge vector \begin{equation}
+(m_1,\ldots, m_{n-2}, m_{n-1},m_n; q)
+\end{equation} 
+into \begin{equation}
+(0,\ldots,0, m, m' ; q')
+\end{equation}
+We then have to determine $q_{n-1}$ and $q_n$.
+
+This reduces the study to the case of $so(4)\simeq su(2)_1 \times su(2)_2$.
+The monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $su(2)$'s.
+The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume $a_1>a_2>0$.
+The fermion is in the vector representation of $so(4)$.
+Under the monopole in $su(2)_1$, it is a doublet coupled to an adjoint vev of size $a_1$ with bare mass $a_2$,
+and similarly for the monopole in $su(2)_2$.
+
+Now, the explicit analysis in \cite[Sec.~IV]{Callias:1977kg} concerning the number of zero modes in the 't Hooft-Polyakov monopole says that 
+a doublet coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
+ a zero mode if $|a|>|m|$ and 
+ it has no zero mode if $|a|<|m|$.
+
+With our assumption $a_1>a_2>0$, this means that the monopole in $su(2)_1$ has a zero mode while the one in $su(2)_2$ doesn't have any.
+In our original basis, this means that the monopole with $(0,\ldots,1,-1;q_{n-1})$ does not have any zero mode and $q_{n-1}=0$,
+while the one with $(0,\ldots,1,+1;q_n)$  (which is in $su(2)_1$) has two zero modes per flavor.
+
+The one-form symmetry group is obtained by dividing $\bZ^2\times \bZ_2$ by the subgroup generated by $(1,-1;0)$ and $(1,+1;q_n)$.
+This is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $q_n$ is $0$ or $1$.
+
+Let us determine $q_n$.
+We saw two zero modes per flavor; 
+this means that there are fermionic zero modes transforming in \begin{equation}
 V_{2} \otimes R_{2n_f} 
-\end{equation} where $V_2$ is the doublet of $su(2)_2$, 
+\end{equation} where $V_2$ is the doublet of $su(2)_2$ (which is actually broken to $u(1)$ but keeping $su(2)_2$ representation is useful in organizing the answer), 
 $R_{2n_f}$ is the fundamental of $usp(2n_f)$,
@@
 It has the `vector' charge under $usp(2)$ flavor symmetry or is a doublet under $su(2)_2$.
-In either case, the $-1$ in $SO(2n_c)\times USp(2n_f)$ acts nontrivially,
+In either case, the $-1$ in $SO(2n_c)\times USp(2n_f)$ acts nontrivially, so $q_n=1$.
 and the 1-form symmetry is extended.
@@
 \end{equation}
-Again,
-it is in the `adjoint' charge under the $usp(4)$ flavor symmetry.
+The charge  is in the `adjoint' charge under the $usp(4)$ flavor symmetry,
+and therefore $q_n=0$.
 Therefore the 1-form symmetry is not extended.

### 2021-06-10 memo.tex
corrected wrong AHSS

@@
 			1  &  &&  && \cellcolor{lightyellow} &&\\
-			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2}\\
+			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
 			\hline
@@
 		\begin{array}{c|c}
-			6  & \bZ\oplus \bZ_2^{\oplus 2}\\
+			6  & \bZ\oplus \bZ_2\\
 			5  & \cellcolor{lightyellow}\\
@@
 			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
-			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
 			\hline
@@
 		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
-		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \bZ_2\cellcolor{lightyellow} & \ast\\
+		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \cellcolor{lightyellow} & \ast\\
 		\hline

### 2021-06-14 memo.tex
Bockstein square and β2 memo

@@
 \def\bZ{\mathbb{Z}}
+\def\fP{\mathfrak{P}}
 \def\diag{\mathop{\mathrm{diag}}}
@@
 This is trivial if $n_c$ is even, but is the `vector' charge if $n_c$ is odd.
+
+\newpage
 
@@
 \end{equation*}
-where $\beta_f$ is a higher Bockstein operator, whose image corresponds to $\bZ_{2^f}$ in integral cohomology.
+where $\beta_f$ is a higher Bockstein operator (reduced to $\bZ_2$ cohomology as a whole),
+whose image corresponds to $\bZ_{2^f}$ in integral cohomology.
 
@@
 
-%\subsection{Adams SS}
-%The above analysis might be complemented by Adams SS.
-%According to our naive guess,
-%the module $\widetilde H^\ast(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
-%\begin{equation}
-%	\begin{tikzpicture}[thick,baseline=(m-2-4.south)]
-%		\matrix (m) [
-%			matrix of math nodes,
-%			row sep= 1em,
-%			column sep=6em,
-%		]{
-%			& \colorB{\bullet} \\
-%			& \colorB{\bullet} & \colorC{\bullet}\\
-%		    & \colorB{\bullet} & \\
-%			\colorA{\bullet} && \colorC{\bullet}\\
-%			& \colorB{\bullet} & \\
-%			\colorA{\bullet} &&\\
-%		};
-%		\draw[colorA] (m-4-1.center) to [out=200, in=160] (m-6-1.center);
-%		%
-%		\node[colorA, right=4pt] at (m-6-1) {$a_2$};
-%		\node[colorA, right=4pt] at (m-4-1) {$(a_2)^2$};
-%		%
-%		\draw[colorB] (m-5-2.center) to [out=160, in=200] (m-3-2.center);
-%		\draw[colorB] (m-3-2.center) to (m-2-2.center);
-%		\draw[colorB] (m-3-2.center) to [out=160, in=200] (m-1-2.center);
-%		%
-%		\node[colorB, right=4pt] at (m-5-2) {$y'(1)$};
-%		\node[colorB, right=4pt] at (m-3-2) {$y'(2)$};
-%		\node[colorB, right=4pt] at (m-2-2) {$y'(1)^2$};
-%		\node[colorB, right=4pt] at (m-1-2) {$y'(3)$};
-%		%
-%		\draw[colorC] (m-2-3.center) to [out=200, in=160] (m-4-3.center);
-%		%
-%		\node[colorC, right=4pt] at (m-4-3) {$c_2$};
-%		\node[colorC, right=4pt] at (m-2-3) {$c_3$};
-%	\end{tikzpicture}
-%\end{equation}
-%This leads to the following Adams chart:
-%\begin{center}
-%	\begin{sseqdata}[
-%		name=M2,
-%		Adams grading,
-%		classes = fill,
-%		xrange = {0}{5},
-%		yrange = {0}{3},
-%		%,x label = {$t-s$}, y label = {$s$}
-%	]
-%		\tower[colorA](2,0)
-%		\tower[colorA](4,1)
-%		\class[white](4,0)
-%		\tower[colorC](4,0)
-%	\end{sseqdata}
-%	\printpage[name = M2,page = 2]
-%\end{center}
+\newpage
+
+\section{Bockstein square for non-closed cochains}
+By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2m}) \to H^{2\bullet}(-;\bZ_{4m})$ term is
+\begin{equation}
+	\label{deltaBockstein}
+	\begin{array}{ccl}
+		\delta \left(\dfrac{1}{4m}\fP(x)\right)
+		& = & \dfrac{1}{4m}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
+		& = & \dfrac{1}{4m}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
+				- \Big(\widetilde x \cup \delta \widetilde x - \delta \widetilde x \cup \widetilde x + \delta \widetilde x \cup_1 \delta \widetilde x\Big)\right]\vspace{2mm}\\
+		& = & \dfrac{1}{4m}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
+	\end{array}
+\end{equation}
+and thus if $x$ were a $\bZ_{2m}$-cocycle $\delta x = 0$ (mod $2m$)
+and its lift $\widetilde x$ were $\delta \widetilde x = 0$ or $2m$ (mod $4m$),
+then the right hand side would be zero (mod 1) and $\fP(x)$ would be a $\bZ_{4m}$-cocycle (i.e.~$0$ mod 4) as desired.
+However, when $x$ is not a cocycle but merely a cochain, this term cannot be defined in the first place.
+
+This can be saved somewhat miraculously as follows.
+A short exact sequence
+\begin{equation*}
+	0
+	\to
+	\bZ_{2^f}
+	\overset{\times 2^{f}}{\longrightarrow}
+	\bZ_{2^{2f}}
+	\overset{p}{\longrightarrow}
+	\bZ_{2^f}
+	\to
+	0
+\end{equation*}
+buys us cohomology operations called higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
+and for the element $x \in C^{\bullet}(-;\bZ_{2^f})$ one has
+\begin{equation*}
+	\delta\widetilde x
+	=
+	2^f \beta_f (x).
+\end{equation*}
+Now, let us consider the case of odd $n_c$.
+Here, the cochain $w_2(c) \in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_2)$
+can be thought of as a mod-2 reduction of $\widetilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
+Dividing the $SO\times SU$ by $\bZ_2$, these become non-closed
+\begin{equation*}
+	\delta \widetilde w_2(c) = 2 \beta v_2(c)
+\end{equation*}
+where $v_2(c)=a_2\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
+%\begin{equation*}
+%	\begin{array}{ccccccccc}
+%		&& w_2 && \widetilde w_2 & \longmapsto & v_2\\
+%		&& \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$}\\
+%		0
+%		& \longrightarrow &
+%		C^2(-;\bZ_2)
+%		& \overset{i^\ast}{\longrightarrow} &
+%		C^2(-;\bZ_4)
+%		& \overset{p^\ast}{\longrightarrow} &
+%		C^2(-;\bZ_2)
+%		& \longrightarrow &
+%		0\vspace{1mm}\\
+%		&& \downarrow\,\delta && \downarrow\,\delta && \downarrow\vspace{1mm}\\
+%		0
+%		& \longrightarrow  &
+%		C^3(-;\bZ_2)
+%		& \longrightarrow &
+%		C^3(-;\bZ_4)
+%		& \longrightarrow &
+%		C^3(-;\bZ_2)
+%		& \longrightarrow &
+%		0\\
+%		&& \rotatebox[]{90}{$\in$} && \rotatebox[]{90}{$\in$}\\
+%		&& \delta w_2 && \delta \widetilde w_2
+%	\end{array}
+%\end{equation*}
+Since this implies $\delta \widetilde w_2(c) = 0$ or $2$ mod 4
+and furthermore $\delta (2\widetilde w_2(c)) = 0$ mod 4,
+one can safely define the Pontrjagin square $\tfrac{1}{8}\fP\big(2\widetilde w_2(c)\big)$.\footnote{
+	Be careful that this factor $2$ here is not the usual map sending $\{0,1\}=\bZ_2$ to $\{0,2\}\subset \bZ_4$.
+	This time we are \textit{really} multiplying by $2$.
+}
+Note that this can naively be regarded as $\tfrac{1}{2}\fP\big(w_2(c)\big)$ at the integral cochain level.
+While the second term in the last line of \eqref{deltaBockstein} together with the overall factor takes value in
+$\tfrac{(2m)^2}{4m}\bZ = m\bZ = 2\bZ$ and dividing by two does not cause any trouble,
+the first term does as it takes value in $\tfrac{2\cdot 2m}{4m}\bZ = \bZ$.
+
+Let us take a closer look at the latter.
+The long exact sequence of cochain groups implies that $2\widetilde w_2(c) = v_2(c) = a_2$ [YL:make it more precise later].
+Then the term of interest is
+\begin{equation*}
+	\dfrac{1}{8}\cdot 2\cdot 4\beta_2(a_2) \cup a_2.
+\end{equation*}
+Therefore, the anomalous variation of the Pontrjagin square term seems to result in
+\begin{equation*}
+	\delta\left(
+		\dfrac{1}{4}\fP(w_2(c))
+	\right)
+	=
+	\dfrac{1}{2}a_2 \beta_2 a_2.
+\end{equation*}
 

### 2021-06-15 memo.tex
typos corrected

@@
 
-\section{Bockstein square for non-closed cochains}
+\section{Pontrjagin square for non-closed cochains}
 By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2m}) \to H^{2\bullet}(-;\bZ_{4m})$ term is
 \begin{equation}
-	\label{deltaBockstein}
+	\label{deltaPontrjagin}
 	\begin{array}{ccl}
@@
 then the right hand side would be zero (mod 1) and $\fP(x)$ would be a $\bZ_{4m}$-cocycle (i.e.~$0$ mod 4) as desired.
-However, when $x$ is not a cocycle but merely a cochain, this term cannot be defined in the first place.
+However, when $x$ is not a cocycle but merely a cochain,
+$\fP(x)$ is also not a cocycle and it is not clear whether this term is well-defined in the first place.
 
@@
 \begin{equation*}
-	\delta\widetilde x
+	\delta (p^\ast x)
 	=
-	2^f \beta_f (x).
+	2^f \beta_f (x) \in C^\bullet(-;\bZ_{2^{2f}}).
 \end{equation*}
@@
 Note that this can naively be regarded as $\tfrac{1}{2}\fP\big(w_2(c)\big)$ at the integral cochain level.
-While the second term in the last line of \eqref{deltaBockstein} together with the overall factor takes value in
+While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
 $\tfrac{(2m)^2}{4m}\bZ = m\bZ = 2\bZ$ and dividing by two does not cause any trouble,

### 2021-06-15 memo.tex
further refinement on Pontrjagin square part

@@
 \section{Pontrjagin square for non-closed cochains}
-By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2m}) \to H^{2\bullet}(-;\bZ_{4m})$ term is
+By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2^m}) \to H^{2\bullet}(-;\bZ_{2^{m+1}})$ term is
 \begin{equation}
@@
 	\begin{array}{ccl}
-		\delta \left(\dfrac{1}{4m}\fP(x)\right)
-		& = & \dfrac{1}{4m}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
-		& = & \dfrac{1}{4m}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
+		\delta \left(\dfrac{1}{2^{m+1}}\fP(x)\right)
+		& = & \dfrac{1}{2^{m+1}}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
+		& = & \dfrac{1}{2^{m+1}}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
 				- \Big(\widetilde x \cup \delta \widetilde x - \delta \widetilde x \cup \widetilde x + \delta \widetilde x \cup_1 \delta \widetilde x\Big)\right]\vspace{2mm}\\
-		& = & \dfrac{1}{4m}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
-	\end{array}
-\end{equation}
-and thus if $x$ were a $\bZ_{2m}$-cocycle $\delta x = 0$ (mod $2m$)
-and its lift $\widetilde x$ were $\delta \widetilde x = 0$ or $2m$ (mod $4m$),
-then the right hand side would be zero (mod 1) and $\fP(x)$ would be a $\bZ_{4m}$-cocycle (i.e.~$0$ mod 4) as desired.
+		& = & \dfrac{1}{2^{m+1}}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
+	\end{array}
+\end{equation}
+and thus if $x$ were a $\bZ_{2^m}$-cocycle, 
+its integral lift $\widetilde x \in C^\bullet(-;\bZ)$ would be a cocycle mod $2^m$ \textit{i.e.}~$\delta \widetilde x = 0$ (mod $2^m$),
+and the right hand side would be $0$ mod 1,
+which then means that $\fP(x)$ would be a $\bZ_{2^{m+1}}$-cocycle as desired.
 However, when $x$ is not a cocycle but merely a cochain,
@@
 
-This can be saved somewhat miraculously as follows.
-A short exact sequence
+This problem arises when we consider $SO(2n_c)$ QCD,
+but it turns out that this can be saved somewhat miraculously as follows.
+First, a short exact sequence
 \begin{equation*}
@@
 \end{equation*}
-buys us cohomology operations called higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
-and for the element $x \in C^{\bullet}(-;\bZ_{2^f})$ one has
-\begin{equation*}
-	\delta (p^\ast x)
+buys us cohomology operations called the higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
+and for the element $y \in C^{\bullet}(-;\bZ_{2^f})$ one has
+\begin{equation*}
+	\delta (p^\ast y)
 	=
-	2^f \beta_f (x) \in C^\bullet(-;\bZ_{2^{2f}}).
+	2^f \beta_f (y) \in C^\bullet(-;\bZ_{2^{2f}}).
 \end{equation*}
@@
 can be thought of as a mod-2 reduction of $\widetilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
-Dividing the $SO\times SU$ by $\bZ_2$, these become non-closed
+Dividing the $SO\times SU$ by $\bZ_2$, these cochains become non-closed
 \begin{equation*}
@@
 }
-Note that this can naively be regarded as $\tfrac{1}{2}\fP\big(w_2(c)\big)$ at the integral cochain level.
+Note that this can naively be regarded as $2\cdot \tfrac{1}{4}\fP\big(w_2(c)\big)$ at the integral cochain level.
 While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
-$\tfrac{(2m)^2}{4m}\bZ = m\bZ = 2\bZ$ and dividing by two does not cause any trouble,
-the first term does as it takes value in $\tfrac{2\cdot 2m}{4m}\bZ = \bZ$.
+$\tfrac{(2^m)^2}{2^{m+1}}\bZ = 2^{m-1}\bZ = 2\bZ$ and dividing by two does not cause any trouble,
+the first term does as it takes value in $\tfrac{2\cdot 2^m}{2^{m+1}}\bZ = \bZ$.
 
 Let us take a closer look at the latter.
-The long exact sequence of cochain groups implies that $2\widetilde w_2(c) = v_2(c) = a_2$ [YL:make it more precise later].
+The long exact sequence of cochain groups implies that $2\widetilde w_2(c)$ can be replaced by
+$\widetilde v_2(c) = \widetilde a_2$, which is a cocycle mod 4.
 Then the term of interest is
 \begin{equation*}
-	\dfrac{1}{8}\cdot 2\cdot 4\beta_2(a_2) \cup a_2.
+	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\widetilde a_2 \cup \widetilde a_2.
 \end{equation*}

### 2021-06-17 memo.tex
anomaly from monopole

@@
 
+\def\bR{\mathbb{R}}
 \def\bZ{\mathbb{Z}}
@@
 \section{'t Hooft-Polyakov monopole argument}
+\subsection{Basics}
 For an $SU(2)$ gauge theory Higgssed by an adjoint ($\bm{3}$, spin-$1$, isovector) scalar,
@@
 
+\subsection{Generalization}
+\subsubsection{Breaking pattern 1}
 Also, one should be able to generalize this whole argument to the case of fermions charged under
@@
 \end{equation*}
+
+\subsubsection{Breaking pattern 2}
+We can also consider $SO(2n_c) \times USp(2n_f)$ breaking to $SO(2n_c) \times U(n_f)$ 
+where the $2n_f$ dimensional irrep of $USp(2n_f)$ becomes 
+a fundamental plus an antifundamental of $U(n_f)$.
+
+The induced effective interaction is \begin{equation}
+\frac12 w_2(SO(2n_c)) c_1(U(n_f)).
+\end{equation} 
+(In the following we consider cochains valued in $\bR/\bZ$.)
+
+We now take the $\bZ_2$ quotient.
+Note that $\pi_1(U(n_f)/\bZ_2)$ is $\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
+Furthermore, when $n_f$ is even, $c_1(U(n_f)) = c_1(U(n_f)/\bZ_2)$ and $v_2(U(n_f)/\bZ_2)=v_2(USp(2n_f))$/
+When $n_f$ is odd, $c_1(U(n_f)/\bZ_2)=2 c_1(U(n_f))$ when the latter is well-defined and $v_2(U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(U(n_f)/\bZ_2)$.
+
+We now compute the anomaly cochains in the four cases separately:
+\paragraph{$(n_c,n_f)$=(even,even):}
+$w_2(SO(2n_c))$ and $c_1(U(n_f))$ can be generalized without problem,
+and therefore \begin{equation}
+\delta(\frac12 w_2(SO(2n_c)) c_1(U(n_f))) = 0.
+\end{equation}
+
+\paragraph{$(n_c,n_f)$=(odd,even):}
+$w_2(SO(2n_c))$ needs to be upgraded to a $\bZ_4$-valued cochain $a_2(SO(2n_c)/\bZ_2)$.
+The original interaction is then \begin{equation}
+\frac14 a_2(SO(2n_c)/\bZ_2) c_1(U(n_f))
+\end{equation}
+which is closed without problem.
+
+\paragraph{$(n_c,n_f)$=(even,odd):}
+Here we need to replace $c_1(U(n_f))$ by $c_1(U(n_f)/\bZ_2)/2$.
+The effective interaction is then \begin{equation}
+\frac14 w_2(SO(2n_c)/\bZ_2) c_1(U(n_f)/\bZ_2) 
+\end{equation} whose $\delta$ is \begin{align}
+\delta(\frac14 w_2(SO(2n_c)/\bZ_2) c_1(U(n_f)/\bZ_2) )
+&= \frac12 (\frac12\delta w_2(SO(2n_c)) c_1(U(n_f)/\bZ_2) ) \\
+&= \frac12 (\beta w_2(SO(2n_c)))c_1(U(n_f)/\bZ_2) 
+\end{align}
+which is the pull-back of the anomaly cochain
+\begin{equation}
+ \frac12 (\beta w_2(SO(2n_c)))v_2(USp(2n_f)/\bZ_2). 
+\end{equation}
+
+\paragraph{$(n_c,n_f)$=(odd,odd):}
+Now we make the replacement on both sides and the effective interaction is \begin{equation}
+\frac18 a_2(SO(2n_c)/\bZ_2) c_1(U(n_f)/\bZ_2) 
+\end{equation}
+whose $\delta$ is \begin{align}
+\delta(\frac18 a_2(SO(2n_c)/\bZ_2) c_1(U(n_f)/\bZ_2) )
+&= \frac12 (\frac14\delta a_2(SO(2n_c)/\bZ_2) c_1(U(n_f)/\bZ_2) ) \\
+&= \frac12 (\beta_2 a_2(SO(2n_c)/\bZ_2))c_1(U(n_f)/\bZ_2) 
+\end{align}
+which is the pull-back of \begin{equation}
+ \frac12 (\beta_2 a_2(SO(2n_c)))v_2(USp(2n_f)),
+\end{equation}
+which is more or less what we need, 
+since $a_2(SO(2n_c)=v_2(USp(2n_f)/\bZ_2)$ up to exact terms.
 

### 2021-06-21 paper.tex
paper

--- 2021-06-15 memo.tex
@@
+\pdfoutput=1
 \RequirePackage[T1]{fontenc}
@@
 %\usepackage{showkeys}
-\renewcommand{\baselinestretch}{1.08}
+\renewcommand{\baselinestretch}{1.05}
 
@@
 \urlstyle{rm}
+%\usepackage[colorlinks,citecolor=black,linkcolor=black]{hyperref}
 \usepackage{cite}
@@
 \usepackage{tikz}
-\usepackage{tikz-cd}
+%\usepackage{tikz-cd}
+\tikzset{>=stealth}
+
 \usepackage{times}
@@
 \usepackage{subfig}
-\usepackage{ascmac}
-\usepackage{spectralsequences}
-\usepackage{dashbox}
-
-\DeclareSseqGroup\tower {} {
-	\class(0,0)\foreach \i in {1,...,8} {
-		\class(0,\i)
-		\structline(0,\i-1,-1)(0,\i,-1)
-	}
-}
 
 \usepackage{xcolor}
-\usepackage{colortbl}
-\usepackage{arydshln}
-\definecolor{lightyellow}{rgb}{1.0, 0.95, 0.7}
-\definecolor{blue}{rgb}{0.0, 0.4, 1.0}
-\definecolor{Blue}{rgb}{0,0,1}
-\definecolor{darkgreen}{rgb}{0.,0.6,0.}
-\newcommand*{\red}[1]{\textcolor{red}{#1}}
-\newcommand*{\Blue}[1]{\textcolor{Blue}{#1}}
-\newcommand*{\blue}[1]{\textcolor{blue}{#1}}
-\newcommand*{\green}[1]{\textcolor{darkgreen}{#1}}
-\newcommand*{\black}[1]{\textcolor{black}{#1}}
-
-\definecolor{colorA}{rgb}{1,0,0}
-\definecolor{colorB}{rgb}{0,0.3,1}
-\definecolor{colorC}{rgb}{0.9,0.8,0.2}
-\definecolor{colorD}{rgb}{0,0.65,0}
-
-\newcommand*{\colorA}[1]{\textcolor{colorA}{#1}}
-\newcommand*{\colorB}[1]{\textcolor{colorB}{#1}}
-\newcommand*{\colorC}[1]{\textcolor{colorC}{#1}}
-\newcommand*{\colorD}[1]{\textcolor{colorD}{#1}}
-
 \usepackage{mdframed}
@@
 %% Comment
-%\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
+\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
 
 %% Yuji's macros
-%%list SeibergDual
+%%list tmf
 
+\def\Nequals#1{$\mathcal{N}{=}#1$}
 \def\bZ{\mathbb{Z}}
-\def\fP{\mathfrak{P}}
-\def\diag{\mathop{\mathrm{diag}}}
+\def\MF{\mathrm{MF}}
+\def\TMF{\mathrm{TMF}}
+\def\Tmf{\mathrm{Tmf}}
+\def\tmf{\mathrm{tmf}}
+\def\tr{\mathop{\mathrm{tr}}}
 
@@
 
-\if0
 \begin{titlepage}
@@
 \begin{flushright}
-IPMU-18-????
+% IPMU-21-XXXX
 \end{flushright}
@@
 
-{\Large \bfseries Title}
+{\Large \bfseries Higher symmetries and anomalies \\[1em]
+in $\mathfrak{so}$ QCD  and \Nequals1 duality}
 
 \vskip 1cm
-Yuji Tachikawa and friends
+Yasunori Lee$^1$, Kantaro Ohmori$^2$, and Yuji Tachikawa$^1$
 \vskip 1cm
@@
 \begin{tabular}{ll}
- & Kavli Institute for the Physics and Mathematics of the Universe, \\
-& University of Tokyo,  Kashiwa, Chiba 277-8583, Japan
+$^1$ & Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\
+& University of Tokyo,  Kashiwa, Chiba 277-8583, Japan\\
+$^2$ & Department of Physics, Faculty of Science, \\
+& University of Tokyo, Bunkyo, Tokyo 113-0033, Japan
 \end{tabular}
@@
 \noindent
-Abstract comes here.
+We study higher symmetries and anomalies of 4d  $\mathfrak{so}(2n_c)$ gauge theory with $N_f=2n_f$ flavors.
+We find that they depend on the parity of $n_c$ and $n_f$,
+on the global form of the gauge group, and the discrete theta angle.
+The contribution from the fermions plays a central role in our analysis.
+Furthermore, our conclusion applies to \Nequals1 supersymmetric cases as well, and
+we see that higher symmetries and anomalies match across the duality 
+$\mathfrak{so}(2n_c)\leftrightarrow\mathfrak{so}(2n_f-n_c+4)$ of Intriligator and Seiberg.
 
@@
 
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{3}
 \tableofcontents
 
-\newpage
+\section{Introduction and summary}
+\label{sec:introduction}
 
+\def\arxivfont{\rm}
+\bibliographystyle{ytamsalpha}
+\if0
+\baselineskip=.93\baselineskip
+\let\originalthebibliography\thebibliography
+\renewcommand\thebibliography[1]{
+  \originalthebibliography{#1}
+%  \setlength{\parskip}{0pt}
+  \setlength{\itemsep}{0pt plus 0.3ex}
+}
 \fi
-
-This file is to collect various notes on our project on the higher symmetry and Seiberg duality.
-
-\section{Duality map}
-
-The duality map among $Spin$, $SO_+$ and $SO_-$ was first found in \cite{Aharony:2013hda}
- \begin{equation}
-\begin{array}{ccc}
-	Spin(N_c) & \leftrightarrow & SO_-(N_c'),\\
-	SO_+(N_c) & \leftrightarrow & SO_+(N_c'),\\
-	SO_-(N_c) & \leftrightarrow & Spin(N_c')
-\end{array}
-\end{equation} where $N_c'=N_f-N_c+4$.
-
-Razamat-Willett \cite{Razamat:2013opa} performed a rather extensive check of this mapping by means of localization on the lens space times $S^1$.
-
-Note that there is a natural action of $SL(2,\bZ)$ on the theories with $\bZ_2$ 1-form symmetry.
-Requiring that this is compatible with the Seiberg duality, one finds that the mapping should in fact be  \begin{equation}
-\begin{array}{ccc}
-	Spin(N_c) & \leftrightarrow & T(SO_-(N_c')),\\
-	SO_+(N_c) & \leftrightarrow & T(SO_+(N_c')),\\ 
-	SO_-(N_c) & \leftrightarrow & T(Spin(N_c'))
-\end{array}
-\end{equation} 
-as discussed in \cite[Sec.~6]{Gaiotto:2014kfa} and \cite{Bhardwaj:2020ymp}.
-
-\section{References on fermionic zero modes on monopoles}
-
-Index theorem on the monopole background: 
-Callias \cite{Callias:1977kg} Bott and Seeley \cite{Bott:1978bw}\footnote{%
-These are on CMP. 
-Papers on CMP are not open access via Springer (which is reachable by doi) but is open access at Project Euclid. 
-I'd like a way to include links in the references appropriately.
-}
-
-General reviews: Harvey \cite[Lecture 4]{Harvey:1996ur}.
-
-\section{Explicit configurations detecting anomalies}
-
-Here we describe geometries detecting $\int_{M_5} B\beta E$, $\int_{M_4} B\beta w_2$, etc.
-All cohomologies in this section is $\bZ_2$-valued.
-
-This is to confirm that these expressions are not secretly trivial.
-
-\paragraph{Klein bottle:}
-
-We start from the Klein bottle $K$ as a nontrivial $S^1$ bundle over $S^1$.
-Let us denote by $a$ the Poincar\'e dual to the fiber $S^1$,
-and $t$ the Poincar\'e dual to the base $S^1$.
-
-We have $\beta a=ta$, since $\int_K \beta a = \int_K w_1 a$.
-
-\paragraph{$T^4$ bundle over $S^1$:}
-
-We now consider a $T^4$ bundle over $S^1$. 
-We denote four directions of $T^4$ as $1$, $2$, $3$ and $4$,
-and we let the directions $1$ and $3$ to flip the orientation when we go around $S^1$.
-We let $a_{1,2,3,4}\in H^1(T^4)$ be the dual basis to the $S^1$ along four directions.
-
-We now take $B=a_1a_2$ and $E=a_3 a_4$.
-Then $\beta B=tB$ and $\beta E=tE$, and $\int B\beta E=1$.
-
-\paragraph{Realizing as $SO(3)$ bundles}
-
-We now look for $SO(3)$ bundles realizing these $B$ and $E$ as $w_2$ in this $T^4$ bundle over $S^1$.
-
-We note that an $SO(3)$ bundle over $T^2$ with two commuting holonomies around two directions \[
-R_x = \diag(+1,-1,-1),\qquad
-R_y = \diag(+1,-1,-1)
-\] has a nontrivial $w_2$, since their lift to $SU(2)$ is given by $i\sigma_x$ and $i\sigma_y$ which anticommute.
-
-Luckily, these $R_x$ and $R_y$ are of order two, so we can put it over our $T^4$ bundle. Done.
-
-\section{Anomaly of trifundamental}
-
-Lee-kun's computation says that \[
-(D\Omega^\text{spin})^6 (B[SU(2)^3/\bZ_2^2]) = \bZ_2 
-\] generated by \[
-\int w_2 \beta w_2'.
-\]
-
-We would like to know if a trifundamental fermion has this anomaly.
-
-\if0
-To see this, we need to compute the eta invariant under an explicit configuration where $\int w_2 \beta w_2'=1$. 
-Such a configuration is constructed above. 
-Let us first find an explicit configuration of $SU(2)^{(1)}\times SU(2)^{(2)} \times SU(2)^{(3)}$ commuting up to $\bZ_2\times \bZ_2$, which is generated by $(-1,-1,+1)$ and $(-1,+1,-1)$.
-So we just have to choose, say, \begin{align}
-\text{holonomy around direction 1} &= (i\sigma_x, i\sigma_x, 1), \\
-\text{holonomy around direction 2} &= (i\sigma_y, i\sigma_y, 1), \\
-\text{holonomy around direction 3} &= (i\sigma_x, 1,i\sigma_x), \\
-\text{holonomy around direction 4} &= (i\sigma_y, 1,i\sigma_y).
-\end{align}
-
-Furthermore, the spinor on our $T^4$ bundle over $S^1$ is glued around $S^1$ via the action of $\Gamma_1\Gamma_3$, 
-since we flip the directions $1$ and $3$.
-
-These are enough data to construct the fermion bundle over our $T^4$ bundle over $S^1$. 
-Since the Euclidean spinor in 5d is pseudoreal, and our trifundamental is also pseudoreal,
-the tensor product is strictly real.
-The Dirac operator is therefore a real antisymmetric matrix, and the eigenvalues come in pairs $\pm \lambda$
-except the zero modes.
-Therefore in our case the eta invariant reduces to the mod-2 index,
-and we just have to count the zero modes.
-\fi
-
-\section{Via direct study of line operators}
-
-Let's determine the anomaly/extension of so SQCD by studying the line operators.
-Here I concentrate on the case of $SO(2n_c)_\pm$ with $2n_f$ flavors.
-
-Let us first consider the case of pure $SO(2n_c)_\pm$ with $n_c$ odd,
-and recall how to distinguish $\bZ_2\times \bZ_2$ or $\bZ_4$.
-
-In either case, the group of the charges of the line operators has the structure \[
-0\to \bZ_2 \to G \to \bZ_2 \to 0
-\] where the $\bZ_2$ subgroup is generated by the 't Hooft line
-and the $\bZ_2$ quotient is generated by the Wilson line in the vector representation.
-To tell whether $G$ is $\bZ_2\times \bZ_2$ or $\bZ_4$,
-we simply take two 't Hooft lines.
-When combined, it is a charge-2 't Hooft line, which can be screened by the dynamical monopole of this charge.
-In the $SO_+$ theory, this dynamical monopole is electrically neutral,
-while the $SO_-$ theory, it has the electric charge equal to the vector representation.
-Therefore, the charge-2 't Hooft line is equivalent to having no line operator in $SO_+$ theory,
-while it is equivalent to having a Wilson line in the vector representation in $SO_-$.
-We find that $G$ is $\bZ_2\times \bZ_2$ for $SO_+$ and $\bZ_4$ for $SO_-$.
-
-We learned the important lesson: 
-the 1-form symmetry group is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on 
-whether the electric charge of the dynamical monopole of an appropriate charge is 
-neutral or vector.
-
-So we would like to determine that in the $SO$ SQCD,
-but the direct analysis of dynamical monopoles in this theory is hard.
-For this purpose, we make the following deformations which do not change the symmetry structure:
-\begin{itemize}
-\item We reduce the flavor symmetry from $su(2n_f)$ to $usp(2n_f)$.
-\item We add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +cc$, where $J_{[ij]}$ is the constant matrix for the $usp(2n_f)$ part.
-\item We give a vev to $\Phi_{ab}$ to break $so(2n_c)$ to $so(2)^{n_c}$.
-\end{itemize}
-The 't Hooft line of the original $SO(2n_c)$ theory is in the `vector' class
-$(1,0,\ldots,0)$ under $so(2)^{n_c}$,
-and therefore the dynamical monopole we need to analyze has the charge in the `adjoint' class.
-
-The monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, 
-e.g.~in \cite{Weinberg:1979zt}.
-There, the following was shown.
-Let $\phi$ be the scalar vev in the real Cartan subalgebra $\mathfrak{h}\subset \mathfrak{g}$.
-This determines the simple roots $\alpha$.
-Then you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole and have a monopole solution without additional bosonic moduli.
-
-Let us say we chose the standard $\phi$ such that the simple roots are $(1,-1,\ldots,0)$,
-$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)$.
-They generate the sublattice $\Lambda$ of $\bZ^n$.
-The group of the 't Hooft line operators up to the screening by the dynamical monopoles is then \begin{equation}
-\bZ^n / \Lambda = \bZ_2.
-\end{equation}
-What we want to do is take into account the center charge $\bZ_2$ of $USp(2n_f)$. 
-For this, we consider $\bZ^n\times \bZ_2$,
-and divide it by the subgroup generated by the charges of the monopoles associated to the simple roots,
-which we denote by $(1,-1,\ldots, 0; q_1)$, $(0,1,-1,\ldots, 0; q_2)$, \ldots,
-$(0,\ldots, 1,-1; q_{n-1})$ and $(0,\ldots,1,+1; q_n)$.
-
-We do not have to determine $q_1$ to $q_{n-1}$. We simply use them to rewrite any charge vector \begin{equation}
-(m_1,\ldots, m_{n-2}, m_{n-1},m_n; q)
-\end{equation} 
-into \begin{equation}
-(0,\ldots,0, m, m' ; q')
-\end{equation}
-We then have to determine $q_{n-1}$ and $q_n$.
-
-This reduces the study to the case of $so(4)\simeq su(2)_1 \times su(2)_2$.
-The monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $su(2)$'s.
-The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume $a_1>a_2>0$.
-The fermion is in the vector representation of $so(4)$.
-Under the monopole in $su(2)_1$, it is a doublet coupled to an adjoint vev of size $a_1$ with bare mass $a_2$,
-and similarly for the monopole in $su(2)_2$.
-
-Now, the explicit analysis in \cite[Sec.~IV]{Callias:1977kg} concerning the number of zero modes in the 't Hooft-Polyakov monopole says that 
-a doublet coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
- a zero mode if $|a|>|m|$ and 
- it has no zero mode if $|a|<|m|$.
-
-With our assumption $a_1>a_2>0$, this means that the monopole in $su(2)_1$ has a zero mode while the one in $su(2)_2$ doesn't have any.
-In our original basis, this means that the monopole with $(0,\ldots,1,-1;q_{n-1})$ does not have any zero mode and $q_{n-1}=0$,
-while the one with $(0,\ldots,1,+1;q_n)$  (which is in $su(2)_1$) has two zero modes per flavor.
-
-The one-form symmetry group is obtained by dividing $\bZ^2\times \bZ_2$ by the subgroup generated by $(1,-1;0)$ and $(1,+1;q_n)$.
-This is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $q_n$ is $0$ or $1$.
-
-Let us determine $q_n$.
-We saw two zero modes per flavor; 
-this means that there are fermionic zero modes transforming in \begin{equation}
-V_{2} \otimes R_{2n_f} 
-\end{equation} where $V_2$ is the doublet of $su(2)_2$ (which is actually broken to $u(1)$ but keeping $su(2)_2$ representation is useful in organizing the answer), 
-$R_{2n_f}$ is the fundamental of $usp(2n_f)$,
-and we need to impose the reality condition using the pseudoreality of both factors,
-so that there are $4n_f$ Majorana fermion in total.
-
-I haven't analyzed the general case; let's take $n_f=1$ and $n_f=2$ as examples.
-When $n_f=1$, there are $4$ Majorana fermions.
-Quantizing them, we find the monopoles in \begin{equation}
-V_2 \otimes \mathbf{1} \oplus \mathbf{1}\otimes R_2.
-\end{equation}
-%I think we should take the spacetime scalar as indicative, (which needs to be justified)
-It has the `vector' charge under $usp(2)$ flavor symmetry or is a doublet under $su(2)_2$.
-In either case, the $-1$ in $SO(2n_c)\times USp(2n_f)$ acts nontrivially, so $q_n=1$.
-and the 1-form symmetry is extended.
-
-When $n_f=2$, there are $8$ Majorana fermions, 
-and  $su(2)_2$ and flavor $usp(4)$ are embedded into $so(8)$ via \begin{equation}
-su(2)\times usp(4) \simeq so(3)\times so(5) \subset so(8).
-\end{equation}
-Therefore, the monopoles are easily seen to be in \begin{equation}
-V_3\otimes \mathbf{1} \oplus V_2\otimes R_2 \oplus V_1\otimes R_5.
-\end{equation}
-The charge  is in the `adjoint' charge under the $usp(4)$ flavor symmetry,
-and therefore $q_n=0$.
-Therefore the 1-form symmetry is not extended.
-
-So far we considered $SO_+$ theories. 
-In $SO_-$ theories, we need to add electric charges coming from the discrete theta angle.
-This is trivial if $n_c$ is even, but is the `vector' charge if $n_c$ is odd.
-
-\newpage
-
-\appendix
-
-\section{Computation of $\Omega_5^{\mathrm{spin}}\big(
-	B\big(
-		\tfrac{SO(4)\times SU(2)}{\bZ_2}
-	\big)
-\big)$}
-
-Let us consider the simplest case of the Seiberg duality and examine the anomaly consequences.
-For $SO(4)$ gauge theory with $N_f=2$ flavors, fermions are charged under $\tfrac{SO(4)\times SU(2)}{\bZ_2}$.
-\subsection{Leray-Serre SS (preparatory)}
-For the various input of cohomology groups, see Appendix A of our WZW paper.
-For the fibration
-\begin{equation}
-	BSO(3)
-	\ \to\ 
-	B\left(SO(3)\times SO(3)\right)
-	=
-	B\left(\tfrac{SO(4)}{\bZ_2}\right)
-	\ \to\ 
-	BSO(3)
-\end{equation}
-one has
-\begin{equation}
-	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(BSO(3);H^q(BSO(3);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
-		\begin{array}{c|ccccccccccccc}
-			6 & \bZ_2 && \ast & \ast & \ast & \ast & \ast \\
-			5  & \hphantom{\bZ_2}\cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast && \ast\\
-			3  & \bZ_2 && \bZ_2\cellcolor{lightyellow} & \bZ_2 & \ast & \ast & \ast \\
-			2  & &  && \cellcolor{lightyellow} &&\\
-			1  &  &&  && \cellcolor{lightyellow} &&\\
-			0 & \bZ &  && \bZ_2 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \longrightarrow & 
-		\begin{array}{c|c}
-			6  &\bZ_2^{\oplus 3}\\
-			5  & \bZ_2\cellcolor{lightyellow}\\
-			4  & \bZ^{\oplus 2}\\
-			3  & \bZ_2^{\oplus 2}\\
-			2  & \\
-			1  & \\
-			0 & \bZ\\
-			\hline\\
-		\end{array}
-	\end{array}
-\end{equation}
-Here we expect non-trivial differentials to be absent (for the region of interest)
-from the explicit consideration of generators (since there are $W_3$ and $W'_3$, there should be $(W_3)^2$, $(W'_3)^2$, and $W_3W'_3$)
-or by requiring proper reproduction of the $\bZ_2$ cohomology (which we expect to be generated by $w_2$, $w'_2$, $w_3$, and $w'_3$).
-Then, for the fibration
-\begin{equation}
-	BSU(2)
-	\ \to\ 
-	B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right)
-	\ \to\ 
-	B\left(\tfrac{SO(4)}{\bZ_2}\right)
-\end{equation}
-we can further plug it into
-\begin{equation}
-	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(B\left(\tfrac{SO(4)}{\bZ_2}\right);H^q(BSU(2);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
-		\begin{array}{c|ccccccccccccc}
-			6  &&&&&& \\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \red{\fbox{\black{$\bZ$}}} & \cellcolor{lightyellow} && \ast & \ast & \ast & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  &&  && \cellcolor{lightyellow} &&\\
-			1  &  &&  && \cellcolor{lightyellow} &&\\
-			0 & \bZ &  && \bZ_2^{\oplus 2} & \bZ^{\oplus 2} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3}\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \longrightarrow & 
-		\begin{array}{c|c}
-			6  & \bZ_2^{\oplus 3}\\
-			5  & \cellcolor{lightyellow}\\
-			4  & \bZ^{\oplus 3}\\
-			3  & \bZ_2^{\oplus 2}\\
-			2  & \\
-			1  & \\
-			0 & \bZ\\
-			\hline\\
-		\end{array}
-	\end{array}
-\end{equation}
-Taking the normalization of instanton number into account (see Ohmori-san's e-mail on 2020-08-19),
-the differential \red{\fbox{\black{$d_2 : E_{0,4} \to E_{5,0}$}}} seems to be non-trivial.
-
-So we believe the integral cohomology structure to be
-\begin{equation}
-	\label{case1}
-	\renewcommand{\arraystretch}{1.2}
-	\begin{array}{c|cccccccccccccccc}
-		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
-		\hline
-		H^d(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ) & \bZ & 0 & 0 & \bZ_2^{\oplus 2} & \bZ^{\oplus 3} & 0 & \bZ_2^{\oplus 3} & \cdots\\
-		\hline
-		\text{generator} & 1 & - & - & W_3 & p_1 & - & (W_3)^2 & \cdots\\
-		&&&& W'_3 & p'_1 && (W'_3)^2\\
-		&&&&& 2c_2 && W_3W'_3
-	\end{array}
-\end{equation}
-where the reduction to $\bZ_2$ cohomology are
-\begin{equation}
-	\begin{array}{ccc}
-		W_3 & \to & w_3\\
-		p_1 & \to & (w_2)^2\\
-%		y_5 & \to & w_2w'_3 + w_3w'_2 \,(?)\\
-	\end{array}
-\end{equation}
-
-\subsection{Atiyah-Hirzebruch SS}
-%Turning cohomology groups into homology groups via the universal coefficient theorem,
-Having obtained (co)homology groups,
-one can fill in the $E^2$-page of the AHSS:
-\begin{equation}
-	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
-		\begin{array}{c|c:cccccccccccc}
-			6  &&&&&& \\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2} && \ast & \ast & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3} & \ast & \ast\\
-			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 3}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} & \ast\\
-			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\fbox{\black{$\bZ^{\oplus 3}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-	\end{array}
-\end{equation}
-Based on our belief, 
-\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
-\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 w_2 & = & (w_2)^2 \\
-		Sq^2 w'_2 & = & (w'_2)^2
-	\end{array}
-\end{equation}
-and also
-\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
-\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 w_3 & = & w_2w_3\\
-		Sq^2 w'_3 & = & w'_2w'_3
-	\end{array}
-\end{equation}
-and finally \green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 (w_2w'_2) & = & w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2
-	\end{array}
-\end{equation}
-then %one can proceed, and 
-the would-be-$E_3$-page is given by
-\begin{equation}
-	\label{e3page1}
-	\begin{array}{c|c:cccccccccccc}
-		6  &&&&&& \\
-		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
-		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
-		2  & \bZ_2 &  && \cellcolor{lightyellow} & \ast & \ast & \ast\\
-		1  & \bZ_2 &&  && \cellcolor{lightyellow} & \ast & \ast\\
-		0 & \bZ &  & \bZ_2^{\oplus 2} &  & \bZ^{\oplus 3} & \bZ_2\cellcolor{lightyellow} & \ast\\
-		\hline
-		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-	\end{array}
-\end{equation}
-
-\subsection{Adams SS}
-According to our naive guess, the module $\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
-\begin{equation}
-	\begin{tikzpicture}[thick,baseline=(m-2-4.south)]
-		\matrix (m) [
-			matrix of math nodes,
-			row sep= 1em,
-			column sep=6em,
-		]{
-			&&& \colorB{\bullet}\\
-			&&& \colorB{\bullet}\\
-			&&& \colorB{\bullet}\\
-			&& \colorB{\bullet} & \colorB{\bullet}\\
-			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
-		    \colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet} & \colorD{\bullet}\\
-			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
-			\colorA{\bullet} &&&& \colorC{\bullet}\\
-			\colorA{\bullet} &&&& \colorC{\bullet}\\
-		};
-		\draw[colorA] (m-7-1.center) to [out=200, in=160] (m-9-1.center);
-		\draw[colorA] (m-9-1.center) to (m-8-1.center);
-		\draw[colorA] (m-5-1.center) to [out=200, in=160] (m-7-1.center);
-		\draw[colorA] (m-6-1.center) to (m-5-1.center);
-		\draw[colorA] (m-6-1.center) to [out=340, in=20] (m-8-1.center);
-		%
-		\node[colorA, right=4pt] at (m-9-1) {$w_2$};
-		\node[colorA, right=6pt] at (m-8-1) {$w_3$};
-		\node[colorA, left=6pt] at (m-7-1) {$(w_2)^2$};
-		\node[colorA, right=6pt] at (m-6-1) {$w_2w_3$};
-		\node[colorA, left=4pt] at (m-5-1) {$(w_3)^2$};
-		%
-		\draw[colorB] (m-7-3.center) to [out=160, in=200] (m-5-3.center);
-		\draw[colorB, dotted] (m-7-3.center) to (m-6-3.center);
-		\draw[colorB, dotted] (m-6-3.center) to [out=5, in=185] (m-4-4.center);
-		\draw[colorB] (m-5-3.center) to (m-4-3.center);
-		\draw[colorB, dotted] (m-5-3.center) to [out=5, in=185] (m-3-4.center);
-		\draw[colorB, dotted] (m-4-4.center) to (m-3-4.center);
-		\draw[colorB] (m-4-3.center) to [out=5, in=185] (m-2-4.center);
-		\draw[colorB, dotted] (m-2-4.center) to (m-1-4.center);
-		\draw[colorB, dotted] (m-3-4.center) to [out=5, in=355] (m-1-4.center);
-		%
-		\node[colorB, right=4pt] at (m-7-3) {$w_2w'_2$};
-		\node[colorB, right=4pt] at (m-6-3) {$w_3w'_2 + w_2w'_3$};
-		\node[colorB, left=4pt] at (m-5-3) {$w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2$};
-		\node[colorB, left=4pt] at (m-4-3) {$(w_2)^2w'_3 + w_3(w'_2)^2$};
-		%
-		\node[colorB, right=4pt] at (m-4-4) {$\begin{array}{r}
-			w_2w_3w'_2 + w_3(w'_2)^2
-			+ (w_2)^2w'_3 + w_2w'_2w'_3
-		\end{array}$};
-		\node[colorB, right=4pt] at (m-3-4) {$\begin{array}{r}
-			(w_3)^2w'_2 + w_2w_3w'_3
-			+ w_3w'_2w'_3 + w_2(w'_3)^2
-		\end{array}$};
-		\node[colorB, left=4pt] at (m-2-4) {$\begin{array}{r}
-			(w_3)^2w'_3 + (w_2)^2w'_2w'_3
-			+ w_2w_3(w'_2)^2 + w_3(w'_3)^2
-		\end{array}$};
-		\node[colorB, right=4pt] at (m-1-4) {$\begin{array}{r}
-			(w_2)^2(w'_3)^2 + (w_3)^2(w'_2)^2
-		\end{array}$};
-		%
-		\draw[colorC] (m-7-5.center) to [out=200, in=160] (m-9-5.center);
-		\draw[colorC] (m-9-5.center) to (m-8-5.center);
-		\draw[colorC] (m-5-5.center) to [out=200, in=160] (m-7-5.center);
-		\draw[colorC] (m-6-5.center) to (m-5-5.center);
-		\draw[colorC] (m-6-5.center) to [out=340, in=20] (m-8-5.center);
-		%
-		\node[colorC, right=4pt] at (m-9-5) {$w'_2$};
-		\node[colorC, right=6pt] at (m-8-5) {$w'_3$};
-		\node[colorC, left=6pt] at (m-7-5) {$(w'_2)^2$};
-		\node[colorC, right=6pt] at (m-6-5) {$w'_2w'_3$};
-		\node[colorC, left=4pt] at (m-5-5) {$(w'_3)^2$};
-		%
-		\node[colorD, right=4pt] at (m-6-6) {(*)};
-	\end{tikzpicture}
-\end{equation}
-To be consistent with the AHSS computation,
-it seems that $w_3w_2' + w_2w'_3$ should be modded out
-(is it an obvious consequence of the transgression in LSSS...?)
-and the remaing part \colorD{(*)} turns out to be
-\begin{equation}
-	\begin{tikzpicture}[colorD, thick,baseline=(m-2-1.south)]
-		\matrix (m) [
-			matrix of math nodes,
-			row sep= 1em,
-			column sep=6em,
-		]{
-			\bullet\\
-		    \bullet\\
-			\bullet\\
-			\bullet\\
-			\bullet\\
-		};
-		\draw (m-3-1.center) to [out=200, in=160] (m-5-1.center);
-		\draw (m-5-1.center) to (m-4-1.center);
-		\draw (m-1-1.center) to [out=200, in=160] (m-3-1.center);
-		\draw (m-2-1.center) to (m-1-1.center);
-		\draw (m-2-1.center) to [out=340, in=20] (m-4-1.center);
-		%
-		\node[right=4pt] at (m-5-1) {$w_2w'_3 = w_3w'_2$};
-		\node[right=6pt] at (m-4-1) {$w_3w'_3$};
-		\node[left=6pt] at (m-3-1) {$(w_2)^2w'_3 + w_2w'_2w'_3$};
-		\node[right=6pt] at (m-2-1) {$w_2w_3w'_3 + w_3w'_2w'_3$};
-		\node[left=4pt] at (m-1-1) {$(w_3)^2w'_3 + w_3(w'_3)^2$};
-	\end{tikzpicture}
-\end{equation}
-and therefore one concludes
-\begin{equation}
-	\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
-\end{equation}
-This leads to the following Adams chart:
-\begin{center}
-	\begin{sseqdata}[
-		name=M,
-		Adams grading,
-		classes = fill,
-		xrange = {0}{5},
-		yrange = {0}{3},
-		%,x label = {$t-s$}, y label = {$s$}
-	]
-		\tower[colorB](4,0)
-		\class[white](4,0)
-		\class[white](4,0)
-		\class[colorA](2,0)
-		\class[colorC](2,0)
-		\tower[colorA](4,1)
-		\tower[colorC](4,1)
-		\class[colorD](5,0)
-	\end{sseqdata}
-	\printpage[name = M,page = 2]
-\end{center}
-and it indeed seems to be compatible with the AHSS computation.
-If the above argument (and beliefs) is correct, then the anomaly should be captured by
-\begin{equation}
-	w_2w'_3\ (= w_3w'_2).
-\end{equation}
-
-\subsection{Seiberg dual}
-The dual theory is $SO(2)$ gauge theory with $N_f = 2$ flavors, and the fermions are charged under
-\begin{equation}
-	\frac{SO(2)\times SU(2)}{\bZ_2}
-	=
-	U(2)
-\end{equation}
-Its spin bordism is known, and the relevant group turns out to be trivial:
-\begin{equation}
-	\Omega_5^{\mathrm{spin}}\big(BU(2)\big) = 0.
-\end{equation}
-This means there is no anomaly for fermions on the dual side,
-and thus the $B\beta E$ anomaly cannot be canceled by fermions.
-
-\newpage
-
-\section{Computation of $\Omega_5^{\mathrm{spin}}\big(
-	B\big(
-		\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}
-	\big)
-\big)$}
-
-\subsection{Cohomology of $BPSO(4n'_c+2)$}
-Recalling that the $\bZ_2$ cohomology read off from \cite{KonoMimura1974}
-allowed us to determine the $\bZ$ cohomology by using Bockstein SS
-(see \texttt{wzw-memo.pdf}, copy later), we had
-\begin{equation}
-	\renewcommand{\arraystretch}{1.2}
-	\begin{array}{c|cccccccccccccccc}
-		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
-		\hline
-		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ)} & \bZ & 0 & 0 & \bZ_4 & \bZ & 0 & \bZ_2 & \cdots\\
-		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ_2)} & \bZ_2 & 0 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2^{\oplus 2} & \cdots\\
-		\hline
-		\text{generator} \,(\bZ_2) & 1 & - & a_2 & y'(1) & (a_2)^2 & y'(2) & (a_2)^3 & \cdots\\
-		&&&&&&& y'(1)^2\\
-	\end{array}
-\end{equation}
-and if we assume the suspension $\bar\theta: H^\ast(PSO(4n'_c+2);\bZ_2) \to H^\ast(BPSO(4n'_c+2);\bZ_2)$
-to commute with Steenrod squares (which seems to be true according to Nishimoto-san's notes),
-then these elements are supposed to be related as
-\begin{equation*}
-	\begin{array}{ccl}
-		\beta_2 a_2 & = & y'(1)\\
-		Sq^2 y'(1) & = & y'(2)\\
-		Sq^1 y'(2) & = & y'(1)^2\\
-	\end{array}
-\end{equation*}
-where $\beta_f$ is a higher Bockstein operator (reduced to $\bZ_2$ cohomology as a whole),
-whose image corresponds to $\bZ_{2^f}$ in integral cohomology.
-
-\subsection{Leray-Serre SS (preparatory)}
-For the fibration
-\begin{equation}
-	BSU(2n_f)
-	\ \to\ 
-	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
-	\ \to\ 
-	BPSO(4n'_c+2)
-\end{equation}
-we have
-\begin{equation}
-	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
-		\begin{array}{c|ccccccccccccc}
-			6  & \bZ &&& \ast & \ast && \ast\\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast & & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  &&  && \cellcolor{lightyellow} &&\\
-			1  &  &&  && \cellcolor{lightyellow} &&\\
-			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \longrightarrow & 
-		\begin{array}{c|c}
-			6  & \bZ\oplus \bZ_2\\
-			5  & \cellcolor{lightyellow}\\
-			4  & \bZ^{\oplus 2}\\
-			3  & \bZ_4\\
-			2  & \\
-			1  & \\
-			0 & \bZ\\
-			\hline\\
-		\end{array}
-	\end{array}
-\end{equation}
-
-\subsection{Atiyah-Hirzebruch SS}
-Having obtained (co)homology groups,
-one can fill in the $E^2$-page of the AHSS:
-\begin{equation}
-	\begin{array}{c}
-		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
-		\begin{array}{c|c:cccccccccccc}
-			6  &&&&&& \\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
-			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
-			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-	\end{array}
-\end{equation}
-Based on our belief, 
-\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
-\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 a_2 & = & (a_2)^2
-	\end{array}
-\end{equation}
-and also
-\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
-\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 y'(1) & = & y'(2)\\
-	\end{array}
-\end{equation}
-and finally
-\green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
-\begin{equation}
-	\begin{array}{ccccc}
-		Sq^2 c_2 & = & c_3
-	\end{array}
-\end{equation}
-then %one can proceed, and 
-the would-be-$E_3$-page is given by
-\begin{equation}
-	\begin{array}{c|c:cccccccccccc}
-		6  &&&&&& \\
-		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
-		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
-		2  & \bZ_2 &&& \cellcolor{lightyellow} & \ast & \ast & \ast\\
-		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
-		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \cellcolor{lightyellow} & \ast\\
-		\hline
-		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-	\end{array}
-\end{equation}
-
-\newpage
-
-\section{Pontrjagin square for non-closed cochains}
-By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2m}) \to H^{2\bullet}(-;\bZ_{4m})$ term is
-\begin{equation}
-	\label{deltaPontrjagin}
-	\begin{array}{ccl}
-		\delta \left(\dfrac{1}{4m}\fP(x)\right)
-		& = & \dfrac{1}{4m}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
-		& = & \dfrac{1}{4m}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
-				- \Big(\widetilde x \cup \delta \widetilde x - \delta \widetilde x \cup \widetilde x + \delta \widetilde x \cup_1 \delta \widetilde x\Big)\right]\vspace{2mm}\\
-		& = & \dfrac{1}{4m}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
-	\end{array}
-\end{equation}
-and thus if $x$ were a $\bZ_{2m}$-cocycle $\delta x = 0$ (mod $2m$)
-and its lift $\widetilde x$ were $\delta \widetilde x = 0$ or $2m$ (mod $4m$),
-then the right hand side would be zero (mod 1) and $\fP(x)$ would be a $\bZ_{4m}$-cocycle (i.e.~$0$ mod 4) as desired.
-However, when $x$ is not a cocycle but merely a cochain,
-$\fP(x)$ is also not a cocycle and it is not clear whether this term is well-defined in the first place.
-
-This can be saved somewhat miraculously as follows.
-A short exact sequence
-\begin{equation*}
-	0
-	\to
-	\bZ_{2^f}
-	\overset{\times 2^{f}}{\longrightarrow}
-	\bZ_{2^{2f}}
-	\overset{p}{\longrightarrow}
-	\bZ_{2^f}
-	\to
-	0
-\end{equation*}
-buys us cohomology operations called higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
-and for the element $x \in C^{\bullet}(-;\bZ_{2^f})$ one has
-\begin{equation*}
-	\delta (p^\ast x)
-	=
-	2^f \beta_f (x) \in C^\bullet(-;\bZ_{2^{2f}}).
-\end{equation*}
-Now, let us consider the case of odd $n_c$.
-Here, the cochain $w_2(c) \in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_2)$
-can be thought of as a mod-2 reduction of $\widetilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
-Dividing the $SO\times SU$ by $\bZ_2$, these become non-closed
-\begin{equation*}
-	\delta \widetilde w_2(c) = 2 \beta v_2(c)
-\end{equation*}
-where $v_2(c)=a_2\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
-%\begin{equation*}
-%	\begin{array}{ccccccccc}
-%		&& w_2 && \widetilde w_2 & \longmapsto & v_2\\
-%		&& \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$}\\
-%		0
-%		& \longrightarrow &
-%		C^2(-;\bZ_2)
-%		& \overset{i^\ast}{\longrightarrow} &
-%		C^2(-;\bZ_4)
-%		& \overset{p^\ast}{\longrightarrow} &
-%		C^2(-;\bZ_2)
-%		& \longrightarrow &
-%		0\vspace{1mm}\\
-%		&& \downarrow\,\delta && \downarrow\,\delta && \downarrow\vspace{1mm}\\
-%		0
-%		& \longrightarrow  &
-%		C^3(-;\bZ_2)
-%		& \longrightarrow &
-%		C^3(-;\bZ_4)
-%		& \longrightarrow &
-%		C^3(-;\bZ_2)
-%		& \longrightarrow &
-%		0\\
-%		&& \rotatebox[]{90}{$\in$} && \rotatebox[]{90}{$\in$}\\
-%		&& \delta w_2 && \delta \widetilde w_2
-%	\end{array}
-%\end{equation*}
-Since this implies $\delta \widetilde w_2(c) = 0$ or $2$ mod 4
-and furthermore $\delta (2\widetilde w_2(c)) = 0$ mod 4,
-one can safely define the Pontrjagin square $\tfrac{1}{8}\fP\big(2\widetilde w_2(c)\big)$.\footnote{
-	Be careful that this factor $2$ here is not the usual map sending $\{0,1\}=\bZ_2$ to $\{0,2\}\subset \bZ_4$.
-	This time we are \textit{really} multiplying by $2$.
-}
-Note that this can naively be regarded as $\tfrac{1}{2}\fP\big(w_2(c)\big)$ at the integral cochain level.
-While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
-$\tfrac{(2m)^2}{4m}\bZ = m\bZ = 2\bZ$ and dividing by two does not cause any trouble,
-the first term does as it takes value in $\tfrac{2\cdot 2m}{4m}\bZ = \bZ$.
-
-Let us take a closer look at the latter.
-The long exact sequence of cochain groups implies that $2\widetilde w_2(c) = v_2(c) = a_2$ [YL:make it more precise later].
-Then the term of interest is
-\begin{equation*}
-	\dfrac{1}{8}\cdot 2\cdot 4\beta_2(a_2) \cup a_2.
-\end{equation*}
-Therefore, the anomalous variation of the Pontrjagin square term seems to result in
-\begin{equation*}
-	\delta\left(
-		\dfrac{1}{4}\fP(w_2(c))
-	\right)
-	=
-	\dfrac{1}{2}a_2 \beta_2 a_2.
-\end{equation*}
-
-\newpage
-
-\section{'t Hooft-Polyakov monopole argument}
-For an $SU(2)$ gauge theory Higgssed by an adjoint ($\bm{3}$, spin-$1$, isovector) scalar,
-the gauge group is broken down to $U(1)$, and correspondingly it accommodates topological solitons (monopoles):
-\begin{equation*}
-	\pi_2\left(
-		\dfrac{SU(2)}{U(1)}
-	\right) = \bZ.
-\end{equation*}
-In the presence of (additional) fermions, this monopole might acquire non-trivial charge under
-spacetime-Lorentz or flavor symmetries, depending on the representation of the fermions under $SU(2)$ gauge symmetry:
-\begin{equation*}
-	\begin{tabular}{c||cccc}
-		fermion gauge rep. & number of zero-modes & spin of zero-modes& spin of monopole\\
-		\hline
-		$\bm{2}$ & $1$ & $0$ & $0$\\
-		$\bm{3}$ & $2$ & $\tfrac{1}{2}$\\
-		$\bm{4}$ & $4$ & $0\oplus 1$ & $\tfrac{1}{2}$\\
-	\end{tabular}
-\end{equation*}
-The numbers of zero-modes can be computed from the Callias index theorem\cite{Callias:1977kg}.
-
-According to \cite{Wang:2018qoy},
-there is $w_2(TM_4)\beta w_2(SU(2)_{\text{gauge}})$ anomaly for a fermion in $\bm{4}$ charged under
-\begin{equation*}
-	\dfrac{Spin(4)_{\text{spacetime}} \times SU(2)_{\text{gauge}}}{\bZ_2},
-\end{equation*}
-which incarnates in the IR as an ill-definition of the effective interaction $w_2(TM) c_1(U(1)_{\text{gauge}})$,
-emerging after integrating out the fermion which obtained mass through Yukawa coupling.
-This effective interaction term should arise in order to make the monopole a fermion
-(\textit{i.e.}\,spinor representation of $Spin(4)_{\text{spacetime}}$),
-but is not well-defined without a trivialization of $w_2(TM_4)$ or equivalently a spin structure.
-
-This situation looks quite similar to our problem where the fermions are charged under
-\begin{equation*}
-	\dfrac{SO(4)_{\text{gauge}} \times SU(2)_{\text{flavor}}}{\bZ_2}.
-\end{equation*}
-Since fermions are in the fundamental representation of the flavor symmetry,
-breaking $SU(2)_{\text{flavor}}$ to $U(1)_{\text{flavor}}$ gives rise to
-a monopole in the spinor representation this time of the $SO(4)_{\text{gauge}}$\cite{Harvey:1996ur}.
-Therefore by the same logic, one can deduce that there should be
-$w_2(SO(4)_{\text{gauge}})\beta w_2(SU(2)_{\text{flavor}})$ anomaly in the first place, as desired.
-
-Also, one should be able to generalize this whole argument to the case of fermions charged under
-\begin{equation*}
-	\dfrac{SO(2n_c)_{\text{gauge}} \times SU(2n_f)_{\text{flavor}}}{\bZ_2}
-\end{equation*}
-by breaking $SU(2n_f)_{\text{flavor}}$ to $SO(2n_f)_{\text{flavor}}$,
-where we have monopoles characterized by
-\begin{equation*}
-	\pi_2\left(
-		\dfrac{SU(2n_f)}{SO(2n_f)}
-	\right)
-	=
-	\left\{
-		\begin{array}{cl}
-			\bZ_2 & (n_f \geq 2)\\
-			\bZ & (n_f = 1)
-		\end{array}
-	\right..
-\end{equation*}
-
-\newpage
-
-\section{misc}
-
-\subsection{$\bZ_4$ 1-form symmetry}
-According to \cite[Appendix C.3]{Clement2002} and \cite[Eq.\,(6.3)]{Wan:2018bns}, it seems that we have
-\begin{equation}
-	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(K(\bZ_4,2);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_4,2))\vspace{4mm}\\
-		\begin{array}{c|c:cccccccccccc}
-			6  &&&&&& \\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
-			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2$}}} & \ast\\
-			0 & \bZ &  & \bZ_4 &  & \red{\dbox{\black{$\bZ_8$}}} & \Blue{\dbox{\black{$\bZ_2$}}} \cellcolor{lightyellow} & \ast\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \quad\longrightarrow & 
-		\begin{array}{c|c}
-			6  & \ast\\
-			5  & \cellcolor{lightyellow}\\
-			4  & \bZ_4\\
-			3  & \\
-			2  & \bZ_4\\
-			1  & \\
-			0 & \\
-			\hline\\
-		\end{array}
-	\end{array}
-\end{equation}
-
-The corresponding invariant in 4d is simply \begin{equation}
-\exp(2\pi i \frac{p}{4} \int \frac12\mathfrak{P}(a) )
-\end{equation}
-where $\mathfrak{P}:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
-which is even mod 8 on a spin manifold.
-
-\subsection{$\bZ_2\times \bZ_2$ 1-form symmetry}
-Exploiting the fact that $K(\bZ_2\times \bZ_2, 2) = K(\bZ_2, 2) \times K(\bZ_2, 2)$,
-it seems that we have
-\begin{equation}
-	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(K(\bZ_2\times \bZ_2,2);\Omega_q^{\text{spin}}\big)
-		&& \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_2\times \bZ_2,2))\vspace{4mm}\\
-		\begin{array}{c|c:cccccccccccc}
-			6  &&&&&& \\
-			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
-			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
-			3  &  && \cellcolor{lightyellow} &&&\\
-			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
-			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\red{\fbox{\black{$\bZ_2^{\oplus 3}$}}}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2^{\oplus 6}$}}} & \ast\\
-			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\dbox{\black{$\bZ_4^{\oplus 2}\oplus \bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
-			\hline
-			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
-		\end{array}
-		& \quad\longrightarrow & 
-		\begin{array}{c|c}
-			6  & \ast\\
-			5  & \bZ_2\cellcolor{lightyellow}\\
-			4  & \bZ_2^{\oplus 3}\\
-			3  & \\
-			2  & \bZ_2^{\oplus 2}\\
-			1  & \\
-			0 & \\
-			\hline\\
-		\end{array}
-	\end{array}
-\end{equation}
-The $\bZ$ homology of $K(\bZ_2, 2)$ is again read off from \cite{Clement2002},
-while the $\bZ_2$ (co)homology is known \cite{Serre1953} to be
-\begin{equation*}
-	H^\ast(K(\bZ_2,2);\bZ_2)
-	=
-	\bZ_2[x_2, Sq^1 x_2, Sq^2Sq^1 x_2, \cdots].
-\end{equation*}
-
-The corresponding bordism invariants in 4d are $\mathfrak{P}(a)/2$, $ab$, $\mathfrak{P}(b)/2$, 
-and the one in 5d is $a\beta b$.
-
-\newpage
-
-\bibliographystyle{ytphys}
-\baselineskip=.95\baselineskip
 \bibliography{ref}

### 2021-06-21 paper.tex
introduction...

@@
 \usepackage{braket}
-\usepackage[svgnames]{xcolor}
+\usepackage[svgnames,psnames]{xcolor}
 \usepackage[colorlinks,citecolor=DarkGreen,linkcolor=FireBrick,urlcolor=FireBrick,linktocpage,unicode]{hyperref}
@@
 %% Yuji's macros
-%%list tmf
+%%list SeibergDual
+
+%% Color
+\usepackage{colortbl}
+\definecolor{lightyellow}{rgb}{1.0, 0.95, 0.7}
+\definecolor{lightblue}{rgb}{0.7, 0.9, 1.0}
+\definecolor{lightpink}{rgb}{1.0, 0.85, 0.95}
+\definecolor{lightgreen}{rgb}{0.7, 1.0, 0.4}
 
@@
 \def\tr{\mathop{\mathrm{tr}}}
+
+\def\SU{\mathrm{SU}}
+\def\SO{\mathrm{SO}}
+\def\so{\mathfrak{so}}
+\def\Spin{\mathrm{Spin}}
+\def\boo{0.0}
+\def\xlattice#1#2#3{
+\begin{tikzpicture}[scale=.5]
+\filldraw[color=black!5!white](-.5,-.5) rectangle (1.5,1.5);
+\draw[->] (-1,0) -- (2,0);
+\draw[->] (0,-1) -- (0,2);
+\foreach \x in {0,1} {
+	\foreach \y in {0,1}{
+		\pgfmathsetmacro\a{mod(#1 * \x - #2 * \y,2)}
+		\ifx\a\boo
+			\filldraw[color=#3] (\x,\y) circle (.5em);
+		\else
+			\filldraw[fill=white,draw=gray] (\x,\y) circle (.5em);
+		\fi
+	}
+}
+\end{tikzpicture}
+}
 
@@
 \label{sec:introduction}
+Our understanding of the concept of symmetries in quantum field theories has been greatly improved in the last several years.
+We now have the concept of $p$-form symmetries acting on $p$-dimensional objects \cite{Gaiotto:2014kfa}.
+This concept  gives a unifying point of view to both
+ordinary symmetries acting on point operators for $p=0$
+and center symmetries of gauge theories acting on Wilson line operators for $p=1$.
+In addition, the 't Hooft magnetic flux \cite{tHooft:1979rtg} can now be thought of as a background gauge field for the 1-form center symmetry.
+It is also realized more recently that 0-form symmetries and 1-form symmetries can not only coexist in a direct product but also mix in a more intricate manner.
+They can have mixed anomalies between them.
+They can also combine to form a symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.
+
+In this paper we study these issues in the case of 4d $\so(N_c)$ gauge theories with 
+$N_f$ flavors of fermion fields in vector representation.
+Let us quickly recall the 0-form and 1-form symmetries these theories have.
+
+As for the 1-form symmetry, we first need to recall that 
+such theories come in three versions, $\Spin$, $\SO_+$ and $\SO_-$,
+distinguished by the global form of the gauge group ($\Spin$ vs.~$\SO$)
+and by the choice of a discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
+This is when the theories are considered on spin manifolds.
+On more general manifolds a further distinction needs to be made \cite{Ang:2019txy}.
+For simplicity we only consider spin manifolds in this paper.
+}.
+They also differ by the nontrivial line operator they possess: 
+the $\Spin$ theory has the Wilson line $W$ in the spinor representation,
+the $\SO_+$ theory has the 't Hooft line $H$ which is mutually non-local with respect to $W$,
+and the $\SO_-$ theory has the dyonic line $D=WH$. 
+Furthermore, these line operators are charged under corresponding $\bZ_2$ 1-form symmetries,
+which we can all electric, magnetic and dyonic 1-form symmetries.
+
+As for the 0-form symmetry, 
+we focus our attention on the $\SU(N_f)$ symmetry acting on $N_f$ flavors of matter fields 
+in the vector representation.
+There can be and definitely are other discrete symmetries, but we will not consider them in this paper for brevity.
+
+Our main question is then how the $\bZ_2$ 1-form symmetry and the $\SU(N_f)$ 0-form symmetry are related.\footnote{%
+A partial answer was given in \cite{Hsin:2020nts}, but the contribution from fermions was not taken into account in that reference.
+}
+We concentrate on the case when $N_c$ and $N_f$ are both even, $N_c=2n_c$ and $N_f=2n_f$.
+
+\section{Charges of line operators in $\so$ QCD}
 

### 2021-06-21 paper.tex
introduction.

@@
 %\usepackage{tikz-cd}
+\newcommand{\tikzmark}[1]{\tikz[remember picture,overlay]\node (#1){};}
 \tikzset{>=stealth}
@@
 \def\SO{\mathrm{SO}}
+\def\su{\mathfrak{su}}
 \def\so{\mathfrak{so}}
@@
 {\Large \bfseries Higher symmetries and anomalies \\[1em]
-in $\mathfrak{so}$ QCD  and \Nequals1 duality}
+in $\so$ QCD  and \Nequals1 duality}
 
@@
 \noindent
-We study higher symmetries and anomalies of 4d  $\mathfrak{so}(2n_c)$ gauge theory with $N_f=2n_f$ flavors.
+We study higher symmetries and anomalies of 4d  $\so(2n_c)$ gauge theory with $N_f=2n_f$ flavors.
 We find that they depend on the parity of $n_c$ and $n_f$,
@@
 we see that higher symmetries and anomalies match across the duality 
-$\mathfrak{so}(2n_c)\leftrightarrow\mathfrak{so}(2n_f-n_c+4)$ of Intriligator and Seiberg.
+$\so(2n_c)\leftrightarrow\so(2n_f-n_c+4)$ of Intriligator and Seiberg.
 
@@
 As for the 0-form symmetry, 
-we focus our attention on the $\SU(N_f)$ symmetry acting on $N_f$ flavors of matter fields 
+we focus our attention on the $\su(N_f)$ symmetry acting on $N_f$ flavors of matter fields 
 in the vector representation.
@@
 
-Our main question is then how the $\bZ_2$ 1-form symmetry and the $\SU(N_f)$ 0-form symmetry are related.\footnote{%
+The main question is then how the $\bZ_2$ 1-form symmetry and the $\su(N_f)$ 0-form symmetry are related.\footnote{%
 A partial answer was given in \cite{Hsin:2020nts}, but the contribution from fermions was not taken into account in that reference.
+Our conclusion is therefore somewhat different from theirs.
 }
 We concentrate on the case when $N_c$ and $N_f$ are both even, $N_c=2n_c$ and $N_f=2n_f$.
+
+Take for example the $Spin(2n_c)$ gauge theory with $2n_f$ flavors,
+when $n_c$ is odd.
+Take two copies of  the Wilson line $W$ in the spinor representation. 
+They form a Wilson line in the vector representation.
+This can be screened by a dynamical fermion, which was why $W^2=1$ 
+as far as the 1-form symmetry charge was concerned.
+Now let us recall that this dynamical fermion transforms nontrivially under $-1\in \SU(2n_f)$.
+Therefore, when we take the flavor symmetry into account, $W^2$ is still nontrivial.
+As we will recall below,  formally this means that the $\bZ_2$ 1-form symmetry extends the $\SU(2n_f)/\bZ_2$ 0-form symmetry in a nontrivial manner, forming a nontrivial 2-group  $H$\begin{equation}
+0\to \bZ_2[1] \to H\to \SU(2n_f)/\bZ_2\to 0,\label{2-group}
+\end{equation}
+whose Postnikov class is specified by \begin{equation}
+\beta v_2 \in H^3(\SU(2n_f)/\bZ_2,\bZ_2),\label{postnikov}
+\end{equation}
+where $a_2$ is the generator of $H^2(\SU(2n_f)/\bZ_2,\bZ_2)=\bZ_2$ and $\beta$ is the Bockstein.
+
+The $\SO_+$ gauge theory is then obtained by gauging the $\bZ_2$ 1-form symmetry \cite{Kapustin:2014gua}.
+The presence of the fermions significantly complicates the analysis.
+For the moment let us suppose that we have $N_f$ scalars instead of fermions in the vector representation.
+Then, the argument of \cite{Tachikawa:2017gyf} immediately applies, and 
+we see that the $\bZ_2$ 1-form symmetry of the $\SO(2n_f)$ theory and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry remains a direct product but with a mixed anomaly given by \begin{equation}
+2\pi i \frac12 \int B\beta v_2.\label{mixed}
+\end{equation}
+
+In the rest of the paper, we will carefully analyze how the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form symmetry are combined.
+The derivation will be detailed in the following, and here we simply summarize the result  in Table~\ref{table:main}.
+There, `none' specifies that they remain a direct product without mixed anomaly;
+`anomaly' implies that they remain a direct product but with mixed anomaly of the form \eqref{mixed};
+and `extension' means that they combine into a 2-group given by \eqref{2-group} with the Postnikov class \eqref{postnikov}.
+
+\begin{table}
+\centering
+\begin{tabular}{r@{\vphantom{$\Bigm|$}\,}l|ccc}
+$(n_c,$&$n_f)$ & $\Spin$ & $\SO_+$ & $\SO_-$\\
+\hline
+(even,&even) & no\tikzmark{A}ne & no\tikzmark{B}ne & no\tikzmark{C}ne \\
+(odd,&even) & exte\tikzmark{P}nsion & ano\tikzmark{Q}maly & exte\tikzmark{R}nsion \\
+(even,&odd) & ano\tikzmark{S}maly & exte\tikzmark{T}nsion & exte\tikzmark{U}nsion \\
+(odd,&odd) & exte\tikzmark{L}nsion & exte\tikzmark{M}nsion & ano\tikzmark{N}maly 
+\end{tabular}
+\caption{How the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form symmetry are combined
+in $\so(2n_c)$ QCD.
+`none' implies that they remain a direct product without mixed anomaly;
+`anomaly' means that they remain a direct product but with mixed anomaly;
+and `extension' is when they combine into a nontrivial 2-group. 
+The orange lines show how the duality of Intriligator and Seiberg acts on this set of theories.
+\label{table:main}}
+\end{table}
+\tikz[overlay,remember picture]{%
+\draw[<->,bend left,color=Orange,line width=1.5] (A.north) to (C.north);
+\draw[<->,color=Orange,line width=1.5] (B.north west) .. controls +(80:0.5) ..  (B.north east);
+\draw[<->,bend left,color=Orange,line width=1.5] (P.north) to (R.north);
+\draw[<->,color=Orange,line width=1.5] (Q.north west) .. controls +(80:0.5) ..  (Q.north east);
+\draw[<->,color=Orange,line width=1.5] (S.south) to (N.north);
+\draw[<->,color=Orange,line width=1.5] (T.south) to (M.north);
+\draw[<->,color=Orange,line width=1.5] (U.south) to (L.north);
+}
+
+Our result is equally applicable in the case of \Nequals1 supersymmetric QCD, for which
+Intriligator and Seiberg found in \cite{Intriligator:1995id} a duality exchanging $\so(N_c)$ and $\so(N_f-N_c+4)$,
+which in our notation sends $n_c$ to $n_c'=n_f-n_c+2$.
+In \cite{Aharony:2013hda}, this duality was refined to account for the global form of the gauge group and the discrete theta angle, and it was concluded that $\Spin$ is exchanged with $\SO_-$ while $\SO_+$ maps to itself.
+This mapping was checked using supersymmetric localization on $S^3/\bZ_n \times S^1$ in \cite{Razamat:2013opa}.
+Our analysis allows us to check this duality by comparing how the 1-form symmetry and the 0-form symmetry are combined in the dual pairs.
+We superimposed the action of the duality on our main Table~\ref{table:main}.
+It is satisfying to see that the duality action correctly preserves the labels `none', `anomaly' and `extension'.
+
+The rest of the paper is organized as follows ...
 

### 2021-06-21 paper.tex
lines in spin theory

@@
 
-\section{Charges of line operators in $\so$ QCD}
+\section{2-group structure}
+Let us first study whether the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ flavor symmetry form a nontrivial 2-group or not. 
+This can be found rather physically by studying the line operators.
+
+\subsection{$\Spin$}
+We start by discussing the $\Spin(2n_c)$ gauge theories. 
+We first recall that the center of $\Spin(2n_c)$ is $\bZ_2\times \bZ_2$ when $n_c$ is even and $\bZ_4$ when $n_c$ is odd.
+This corresponds to the fact that the tensor square of a spinor representation contains the identity representation when $n_c$ is even while it contains the vector representation when $n_c$ is odd.
+
+We now consider the Wilson line $W$ in the spinor representation in the $\Spin(2n_c)$ gauge theory with $2n_f$ fermions in the vector representation.
+When $n_c$ is even, $W^2$ contains the identity representation, and therefore we simply have a $\bZ_2$ 1-form symmetry independent of the $\su$ flavor symmetry, and there is nothing to see here.
+
+When $n_c$ is odd, $W^2$ contains the vector representation.
+This can be screened by the dynamical fermion, which however carries the fundamental representation of $\su(2n_f)$ flavor symmetry, 
+and in particular transforms nontrivially under $-1\in \SU(2n_f)$.
+In other words, the flavor Wilson line in the vector representation of $\SU(2n_f)$ can now be considered as the square  of the gauge Wilson line in the spinor representation of $\Spin(2n_c)$.
+This means that we have the following extension of groups \begin{equation}
+0\to \underbrace{\bZ_2}_{\substack{\text{subgroup of}\\
+\text{rep.~of center of $\SU(2n_f)$}}}
+\to \bZ_4 
+\to \underbrace{\bZ_2}_{\substack{\text{group of gauge Wilson lines }\\
+\text{up to screening}}} \to 0.
+\end{equation}
+
+As the groups of charges of $\su(2n_f)$ 0-form symmetry and $\bZ_2$ 1-form symmetry are combined nontrivially, 
+the 0-form symmetry group and the 1-form symmetry group are also combined nontrivially.
+This can be seen most clearly by considering background fields for the symmetry groups.
+
+The fermion fields are in the vector of $\SO(2n_c)$ and in the fundamental of $\SU(2n_f)$, and therefore is a representation of $G=[\SO(2n_c)\times \SU(2n_f)]/\bZ_2$.
+Given a $G$-bundle on a manifold $X$,
+there is an $\SO(2n_c)/\bZ_2$ bundle and an $\SU(2n_f)/\bZ_2$ bundle associated to it.
+Let us denote by $a_2,v_2\in H^2(X,\bZ_2)$ the obstruction classes controlling whether they lift to $\SO(2n_c)$ and $\SU(2n_f)$ respectively. 
+Then we have $a_2=v_2$ for a $G$-bundle.
+The flavor Wilson line in the fundamental representation is charged under $-1\in \SU(2n_f)$ in the center,
+and $v_2$ can be considered as the background field for this $\bZ_2$ 1-form center symmetry.
+
+Now, without the flavor background,  the background $E\in H^2(X,\bZ_2)$ for the electric $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2\in H^2(X,\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2$, which controls whether it lifts to a $\Spin(2n_c)$ bundle.
+When the flavor background $v_2$ is nontrivial,
+the obstruction class $a_2$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$ is nontrivial.
+In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta a_2$, where $\beta$ is the Bockstein operation.
+As $E=w_2$ and $a_2=v_2$, we conclude that the background fields satisfy \begin{equation}
+\delta E=\beta v_2.
+\end{equation}
+This means that the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry form the 2-group $H$ fitting in the sequence \begin{equation}
+0\to \bZ_2[1]\to H \to \SU(2n_f)/\bZ_2 \to 0
+\end{equation} whose Postnikov class is $\beta v_2 \in H^3(B\SU(2n_f)/\bZ_2,\bZ_2)$.
 

### 2021-06-21 paper.tex
minor improv

@@
 \text{up to screening}}} \to 0.
+\label{charge-extension}
 \end{equation}
@@
 the obstruction class $a_2$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$ is nontrivial.
-In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta a_2$, where $\beta$ is the Bockstein operation.
+In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta a_2$, where $\beta$ is the Bockstein operation,
+since together they specify the obstruction class $x_2\in H^2(X,\bZ_4)$ 
+controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
 As $E=w_2$ and $a_2=v_2$, we conclude that the background fields satisfy \begin{equation}
 \delta E=\beta v_2.
+\label{ba}
 \end{equation}
@@
 0\to \bZ_2[1]\to H \to \SU(2n_f)/\bZ_2 \to 0
+\label{group-extension}
 \end{equation} whose Postnikov class is $\beta v_2 \in H^3(B\SU(2n_f)/\bZ_2,\bZ_2)$.
+
+Before proceeding, we note that having the extension of groups of charges of line operators as in \eqref{charge-extension}
+is equivalent to having a nontrivial 2-group extension \eqref{group-extension} 
+whose background fields satisfy \eqref{ba}.
+Therefore, to find a nontrivial 2-group extension, we can simply study the group of charges of line operators,
+which we will carry out for $\SO_\pm$ gauge theories next.
 

### 2021-06-21 paper.tex
rest of sec.2

@@
 
+\def\U{\mathrm{U}}
 \def\SU{\mathrm{SU}}
 \def\SO{\mathrm{SO}}
+\def\USp{\mathrm{USp}}
+\def\u{\mathfrak{u}}
 \def\su{\mathfrak{su}}
 \def\so{\mathfrak{so}}
+\def\usp{\mathfrak{usp}}
 \def\Spin{\mathrm{Spin}}
@@
 
+\subsection{$\SO_\pm$}
+
+We would like to study how the magnetic $\bZ_2$ 1-form symmetry of the $\SO(2n_c)_+$ theory is combined with the $\su(n_f)$ flavor symmetry.
+According to the discussions in the previous subsection, 
+we consider what happens if we take two copies of the 't Hooft line operator $H$ and fuse them.
+At the very naive level, $H^2$ can be screened by a dynamical monopole,
+but dynamical monopoles can receive flavor and gauge center charges from the fermion zero modes.
+To study these issues, it is useful to deform the theories to make them simpler.
+
+For this purpose, we perform the following steps:
+\begin{itemize}
+\item We reduce the flavor symmetry from $\su(2n_f)$ to $\usp(2n_f)$. 
+The fundamental representation still transforms nontrivially under $-1\in \USp(2n_f)$, which is enough for our purposes.
+\item We add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +cc$, where $J_{[ij]}$ is the constant matrix for the $\usp(2n_f)$ part.
+\item We give a vev to $\Phi_{ab}$ to break $\SO(2n_c)$ to $\SO(2)^{n_c}$.
+\end{itemize}
+
+The 't Hooft lines in the resulting $\SO(2)^{n_c}$ theory can be labeled by their magnetic charges $(m_1,\ldots,m_{n_c})\in \bZ^{n_c})$.
+The dynamical monopoles have the charges in the `adjoint class', which are
+in the root lattice $\Lambda$ of $\SO(2n_c)$.
+
+The group of the magnetic charges of 't Hooft lines up to screening by the dynamical monopoles is then \begin{equation}
+\bZ^{n_c}/\Lambda = \bZ_2,
+\end{equation}
+which agrees with the 1-form symmetry before the deformation.
+We now would like to study how this $\bZ_2$ is combined with the flavor/gauge center charge $\bZ_2$.
+
+For this purpose we need to know slightly more details of the dynamical monopoles.
+The dynamical monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, 
+e.g.~in \cite{Weinberg:1979zt}.
+There, the following was shown.
+Let $\phi$ be the scalar vev in the real Cartan subalgebra, $\phi\in \mathfrak{h}\subset \mathfrak{g}$.
+This determines the simple roots $\alpha$.
+Then you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole and have a monopole solution without additional bosonic moduli.
+
+Let us say we chose the standard $\phi$ such that the simple roots are $(1,-1,\ldots,0)$,
+$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)$,
+which we call simple dynamical monopoles.
+
+We now consider the group $\bZ^{n_c}\times \bZ_2$ which combine the magnetic charges $\bZ^{n_c}$ and the flavor/gauge center charge $\bZ_2$.
+What we are after is the quotient of $\bZ^{n_c}\times \bZ_2$ 
+by the subgroup generated by the charges of simple dynamical monopoles,
+which we denote by
+$(1,-1,\ldots, 0; q_1)$, $(0,1,-1,\ldots, 0; q_2)$, \ldots,
+$(0,\ldots, 1,-1; q_{n_c-1})$ and $(0,\ldots,1,+1; q_{n_c})$, respectively.
+
+Let us determine this quotient.
+We do not have to determine $q_1$ to $q_{n_c-1}$. 
+We simply use them to rewrite any charge vector $
+(m_1,\ldots, m_{n_c-2}, m_{n_c-1},m_{n_c}; q)
+$
+into the form $
+(0,\ldots,0, m, m' ; q').
+$
+We then have to determine $q_{n-1}$ and $q_{n_c}$.
+
+This reduces the study to the case of $\so(4)\simeq \su(2)_1 \times \su(2)_2$.
+The monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $\su(2)$'s.
+The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume $a_1>a_2>0$.
+The fermion is in the vector representation of $so(4)$.
+Under the monopole in $\su(2)_1$, it is a doublet coupled to an adjoint vev of size $a_1$ with bare mass $a_2$,
+and similarly for the monopole in $\su(2)_2$.
+
+Now, the explicit analysis in \cite[Sec.~IV]{Callias:1977kg} concerning the number of zero modes in the 't Hooft-Polyakov monopole says that 
+a doublet coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
+ a zero mode if $|a|>|m|$ and 
+ it has no zero mode if $|a|<|m|$.
+
+With our assumption $a_1>a_2>0$, this means that the monopole in $\su(2)_1$ has a zero mode while the one in $\su(2)_2$ does not have any.
+In our original basis, this means that the monopole with $(0,\ldots,1,-1;q_{n_c-1})$ does not have any zero modes and $q_{n_c-1}=0$,
+while the one with $(0,\ldots,1,+1;q_{n_c})$  (which is in $\su(2)_1$) has two zero modes per flavor.
+
+The one-form symmetry group is obtained by dividing $\bZ^2\times \bZ_2$ by the subgroup generated by $(1,-1;0)$ and $(1,+1;q_{n_c})$.
+This is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $q_{n_c}$ is $0$ or $1$.
+
+Let us determine $q_{n_c}$.
+We saw two zero modes per flavor; 
+this means that there are fermionic zero modes transforming in \begin{equation}
+V_{2} \otimes R_{2n_f} 
+\end{equation} where $V_2$ is the doublet of $\su(2)_2$ (which is actually broken to $\u(1)$ but keeping $\su(2)_2$ representation is useful in organizing the answer), 
+$R_{2n_f}$ is the fundamental of $\usp(2n_f)$,
+and we need to impose the reality condition using the pseudoreality of both factors,
+so that there are $4n_f$ Majorana fermion in total.
+
+To determine the flavor/gauge center charge of the monopole,
+it suffices to consider the case $n_f=1$;
+the general case is given by simply multiplying it by $n_f$.
+When $n_f=1$, there are $4$ Majorana fermions.
+Quantizing them, we find the monopoles in \begin{equation}
+V_2 \otimes \mathbf{1} \oplus \mathbf{1}\otimes R_2.
+\end{equation}
+It has the `vector' charge under $\usp(2)$ flavor symmetry or is a doublet under $\su(2)_2$,
+which corresponds to the `vector' charge under $\so(4)$ gauge symmetry.
+In either case, they have the flavor/gauge center charge $1 \in \{0,1\}=\bZ_2$.
+Therefore we conclude the flavor/gauge center charge $q_{n_c}$ is simply given by $n_f$ mod 2.
+
+Combining the intermediate steps above, we conclude the following: 
+for the $\SO(2n_c)_+$ theory,
+the group $\bZ_2$ of magnetic charges of 't Hooft lines is extended by the flavor/gauge center symmetry $\bZ_2$ to become $\bZ_4$ when $n_f$ is odd,
+while they remain separate when $n_f$ is even.
+
+The analysis of the $\SO(2n_c)_-$ theory is largely the same;
+the only difference is that the discrete theta angle gives an additional gauge center charge to the simple dynamical monopole with the magnetic charge $(0,0,\ldots,1,1)$, so that $q_{n_c}=n_f+n_c$ mod 2.
+Therefore, we conclude the following:
+for the $\SO(2n_c)_-$ theory,
+the group $\bZ_2$ of magnetic charges of 't Hooft lines is extended by the flavor/gauge center symmetry $\bZ_2$ to become $\bZ_4$ when $n_f+n_c$ is odd,
+while they remain separate when $n_f+n_c$ is even.
+
+The result of the analysis is summarized in Table~\ref{table:2group}.
+There, `product' means that the $\bZ_2$ 1-form symmetry and $\SU(2n_f)/\bZ_2$ flavor symmetry are kept separate and form a direct product,
+while `extended' means that they form a nontrivial 2-group.
+We remark that the nontrivial 2-group is always given by the extension \eqref{group-extension}  whose background fields satisfy \eqref{ba}.
+
+\begin{table}
+\centering
+\begin{tabular}{r@{\vphantom{$\Bigm|$}\,}l|ccc}
+$(n_c,$&$n_f)$ & $\Spin$ & $\SO_+$ & $\SO_-$\\
+\hline
+(even,&even) & product & product & product \\
+(odd,&even) & extended & product & extended \\
+(even,&odd) & product & extended & extended \\
+(odd,&odd) & extended & extended & product
+\end{tabular}
+\caption{How the $\bZ_2$ 1-form symmetry and the flavor symmetry $\SU(N_f)/\bZ_2$ are combined
+in $\so(2n_c)$ QCD.
+`product' means that they form a direct product,
+and `extended' means that they form a nontrivial 2-group.
+\label{table:2group}}
+\end{table}
+
 \def\arxivfont{\rm}
 \bibliographystyle{ytamsalpha}
-\if0
-\baselineskip=.93\baselineskip
+
+\baselineskip=.98\baselineskip
 \let\originalthebibliography\thebibliography
@@
 }
-\fi
+
 \bibliography{ref}

### 2021-06-21 paper.tex
sl(2,z)

@@
 
+\usepackage{ascmac}
+\usepackage{spectralsequences}
+\usepackage{dashbox}
+
+\DeclareSseqGroup\tower {} {
+	\class(0,0)\foreach \i in {1,...,8} {
+		\class(0,\i)
+		\structline(0,\i-1,-1)(0,\i,-1)
+	}
+}
+
+\usepackage{xcolor}
+\usepackage{colortbl}
+\usepackage{arydshln}
+\definecolor{lightyellow}{rgb}{1.0, 0.95, 0.7}
+\definecolor{blue}{rgb}{0.0, 0.4, 1.0}
+\definecolor{Blue}{rgb}{0,0,1}
+\definecolor{darkgreen}{rgb}{0.,0.6,0.}
+\newcommand*{\red}[1]{\textcolor{red}{#1}}
+\newcommand*{\Blue}[1]{\textcolor{Blue}{#1}}
+\newcommand*{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand*{\green}[1]{\textcolor{darkgreen}{#1}}
+\newcommand*{\black}[1]{\textcolor{black}{#1}}
+
+\definecolor{colorA}{rgb}{1,0,0}
+\definecolor{colorB}{rgb}{0,0.3,1}
+\definecolor{colorC}{rgb}{0.9,0.8,0.2}
+\definecolor{colorD}{rgb}{0,0.65,0}
+
+\newcommand*{\colorA}[1]{\textcolor{colorA}{#1}}
+\newcommand*{\colorB}[1]{\textcolor{colorB}{#1}}
+\newcommand*{\colorC}[1]{\textcolor{colorC}{#1}}
+\newcommand*{\colorD}[1]{\textcolor{colorD}{#1}}
+
 %% Yuji's macros
@@
 \def\Spin{\mathrm{Spin}}
+\def\SL{\mathrm{SL}}
 \def\boo{0.0}
@@
 \label{table:main}}
-\end{table}
+
 \tikz[overlay,remember picture]{%
@@
 }
+\end{table}
 
@@
 
+\section{$\SL(2,\bZ_2)$ action and the anomalies}
+
+In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
+In a quantum field theory, any symmetry comes with its (possibly trivial) 't Hooft anomaly.
+Here we determine the anomalies of these theories using the $\SL(2,\bZ_2)$ action on the set of quantum field theories (QFTs) with $\bZ_2$ 1-form symmetry.
+
+\subsection{$\SL(2,\bZ_2)$ action}
+Let us say that  a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry is given.
+We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
+where we suppress the dependence on $X$ in the notation and $E\in H^2(X,\bZ_2)$ is the background field for the 1-form symmetry.
+We then define $SQ$ and $TQ$ to be given by the formula \begin{equation}
+Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q{B},\qquad
+Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \mathfrak{P}(E)} Z_Q[E].
+\end{equation}
+We can show that $S^2=T^2=1$ and $(ST)^3=1$, meaning that they generate $\SL(2,\bZ_2)$.
+This operation was considered in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.
+
+\subsection{$\SL(2,\bZ_2)$ action and $\so$ gauge theories}
+
+Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
+More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T\SO(2n_c)_\pm$, respectively.
+Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
+Then we have the following chain of actions: \begin{equation}
+T\Spin \stackrel{T}{\longleftrightarrow} 
+\Spin \stackrel{S}{\longleftrightarrow} 
+\SO_+ \stackrel{T}{\longleftrightarrow} 
+T\SO_+ \stackrel{S}{\longleftrightarrow} 
+T\SO_- \stackrel{T}{\longleftrightarrow} 
+\SO_- \stackrel{S}{\longleftrightarrow} .
+\end{equation}
+
+Let us now study what happens if we perform this $\SL(2,\bZ_2)$ action when the $\bZ_2$ 1-form symmetry in question is part of a larger symmetry group.
+So far we have been considering the effect of $\SU(2n_f)/\bZ_2$ flavor symmetry,
+but the discussions in the last section shows that at a formal level only the background field $v_2 \in H^2(X,\bZ_2)$ matters, which controls the lift from $\SU(2n_f)/\bZ_2$ to $\SU(2n_f)$.
+Let us regard $v_2$ as the background field for a flavor $\bZ_2$ 1-form symmetry.
+
+The combined 1-form symmetry is either $\bZ_2\times \bZ_2$ or $\bZ_4$,
+and we perform the $\SL(2,\bZ_2)$ action  by picking a $\bZ_2$ subgroup.
+The symmetry and the anomaly of the resulting theory can be determined by a formal argument once the symmetry and the anomaly of the original theory 
+and the action of the anomaly-free subgroup to be gauged is given \cite{Tachikawa:2017gyf}.
+
+As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly of $\bZ_2\times \bZ_2$ 1-form symmetry of 4d spin QFTs is \begin{equation}
+2\pi i \tfrac12 \int_Y B\beta E  \label{anom}
+\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y,\bZ_2)$ are the background fields,
+there is no anomaly for $\bZ_4$ 1-form symmetry.
+
+\subsection{$\SL(2,\bZ_2)$ actions with extra background }
+
+Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
+The case $\bZ_2\times \bZ_2$ with no anomaly is very easy.
+The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
+\text{none} \stackrel{T}{\longleftrightarrow} 
+\text{none} \stackrel{S}{\longleftrightarrow} 
+\text{none} \stackrel{T}{\longleftrightarrow} 
+\text{none} \stackrel{S}{\longleftrightarrow} 
+\text{none} \stackrel{T}{\longleftrightarrow} 
+\text{none} \stackrel{S}{\longleftrightarrow} 
+\label{trivial-chain}
+\end{equation} where `none' stands for $\bZ_2\times \bZ_2$ with no anomaly.
+
+Let us now consider $\bZ_4$ 1-form symmetry and gauge its $\bZ_2$ subgroup,
+without the background term $\frac12\mathfrak{P}(E)$.
+As described in \cite{Tachikawa:2017gyf},
+the resulting theory has $\bZ_2\times \bZ_2$ 1-form symmetry with the anomaly \eqref{anom}.
+
+When we gauge the $\bZ_2$ subgroup  of $\bZ_4$ 1-form symmetry 
+with the background term $\frac12\mathfrak{P}(E)$,
+the resulting theory instead have $\bZ_4$ symmetry
+with the background term $\frac12\mathfrak{P}(E)$.
+This can be seen as follows:
+the gauging process involves the term
+ \begin{equation}
+\exp\left(2\pi i\int_X ( \frac14 \mathfrak{P}(E) +\frac12 B E)\right)
+\label{boo}
+\end{equation}
+where $E$ is the variable to be gauged and $B$ is the newly introduced background field.
+When $\bZ_2$ to be gauged is the $\bZ_2$ subgroup of a $\bZ_4$ symmetry,
+$E$ is not necessarily closed, but satisfies rather the relation \begin{equation}
+\delta E = \beta v_2
+\end{equation}
+where $v_2$ is the background field for the quotient $\bZ_4/\bZ_2$ 1-form symmetry.
+Then the second term in \eqref{boo} is not closed, 
+and to even talk about the first term in \eqref{boo}, one first needs to extend the definition of the Pontryagin square $\mathfrak{P}$ to non-closed cochains.
+
+To make  the coupling \eqref{boo}  well-defined, we consider adding a background term to \eqref{boo} so that we have \begin{equation}
+\exp\left(2\pi i\int_X ( \frac14 \mathfrak{P}(E) +\frac12 B E + \frac14 \mathfrak{P}(B) )\right)
+= 
+\exp \left(2\pi i \frac14 \int_X \mathfrak{P}(E+B)\right) .
+\end{equation}
+This is perfectly well-defined if the newly-introduced background field $B$  also satisfies \begin{equation}
+\delta B=\beta v_2.
+\end{equation}
+This means that the 1-form symmetry after the gauging is still extended, with a background coupling.
+
+Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
+\text{extended} \stackrel{S}{\longleftrightarrow} 
+\text{anomaly} \stackrel{T}{\longleftrightarrow} 
+\text{anomaly} \stackrel{S}{\longleftrightarrow} 
+\text{extended} \stackrel{T}{\longleftrightarrow} 
+\begin{array}{c}
+\text{extended}\\
+\text{and with $\mathfrak{P}$} 
+\end{array} 
+\stackrel{S}{\longleftrightarrow} 
+\begin{array}{c}
+\text{extended }\\
+\text{and with $\mathfrak{P}$} 
+\end{array} 
+\stackrel{T}{\longleftrightarrow} 
+\label{nontrivial-chain}
+\end{equation}
+where `extended' stands for $\bZ_4$ without the background term $\frac12\mathfrak{P}(E)$,
+`extended with $\mathfrak{P}$' is for $\bZ_4$ with the background term,
+and `anomaly' is $\bZ_2\times \bZ_2$ with the anomaly \eqref{anom}.
+
+\subsection{Anomalies from $\SL(2,\bZ_2)$ action} 
+Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
+and Table~\ref{table:2group},
+we see that the anomaly is automatically determined and 
+we obtain the result already presented in Table~\ref{table:main}.
+There is a small puzzle to be resolved, but it's already 1pm. I am going to sleep...
+
+\appendix
+\section{Bordism group computations}
+\label{sec:bordism}
+\subsection{$\bZ_4$ 1-form symmetry}
+According to \cite[Appendix C.3]{Clement2002} and \cite[Eq.\,(6.3)]{Wan:2018bns}, it seems that we have
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(K(\bZ_4,2);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_4,2))\vspace{4mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2$}}} & \ast\\
+			0 & \bZ &  & \bZ_4 &  & \red{\dbox{\black{$\bZ_8$}}} & \Blue{\dbox{\black{$\bZ_2$}}} \cellcolor{lightyellow} & \ast\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \quad\longrightarrow & 
+		\begin{array}{c|c}
+			6  & \ast\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ_4\\
+			3  & \\
+			2  & \bZ_4\\
+			1  & \\
+			0 & \\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+
+The corresponding invariant in 4d is simply \begin{equation}
+\exp(2\pi i \frac{p}{4} \int \frac12\mathfrak{P}(a) )
+\end{equation}
+where $\mathfrak{P}:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
+which is even mod 8 on a spin manifold.
+
+\subsection{$\bZ_2\times \bZ_2$ 1-form symmetry}
+Exploiting the fact that $K(\bZ_2\times \bZ_2, 2) = K(\bZ_2, 2) \times K(\bZ_2, 2)$,
+it seems that we have
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(K(\bZ_2\times \bZ_2,2);\Omega_q^{\text{spin}}\big)
+		&& \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_2\times \bZ_2,2))\vspace{4mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\red{\fbox{\black{$\bZ_2^{\oplus 3}$}}}}}\cellcolor{lightyellow} & \Blue{\fbox{\black{$\bZ_2^{\oplus 6}$}}} & \ast\\
+			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\dbox{\black{$\bZ_4^{\oplus 2}\oplus \bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \quad\longrightarrow & 
+		\begin{array}{c|c}
+			6  & \ast\\
+			5  & \bZ_2\cellcolor{lightyellow}\\
+			4  & \bZ_2^{\oplus 3}\\
+			3  & \\
+			2  & \bZ_2^{\oplus 2}\\
+			1  & \\
+			0 & \\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+The $\bZ$ homology of $K(\bZ_2, 2)$ is again read off from \cite{Clement2002},
+while the $\bZ_2$ (co)homology is known \cite{Serre1953} to be
+\begin{equation*}
+	H^\ast(K(\bZ_2,2);\bZ_2)
+	=
+	\bZ_2[x_2, Sq^1 x_2, Sq^2Sq^1 x_2, \cdots].
+\end{equation*}
+
+The corresponding bordism invariants in 4d are $\mathfrak{P}(a)/2$, $ab$, $\mathfrak{P}(b)/2$, 
+and the one in 5d is $a\beta b$.
+
 \def\arxivfont{\rm}

### 2021-06-21 paper.tex
couldn't resist; should sleep

@@
 
+\def\ewith{
+\begin{array}{c}
+\text{extended}\\
+\text{with $\mathfrak{P}$} 
+\end{array} 
+}
+\def\ewithout{
+\begin{array}{c}
+\text{extended}\\
+\text{without $\mathfrak{P}$} 
+\end{array} 
+}
 Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
-\text{extended} \stackrel{S}{\longleftrightarrow} 
+\ewith \stackrel{T}{\longleftrightarrow} 
+\ewithout \stackrel{S}{\longleftrightarrow} 
 \text{anomaly} \stackrel{T}{\longleftrightarrow} 
 \text{anomaly} \stackrel{S}{\longleftrightarrow} 
-\text{extended} \stackrel{T}{\longleftrightarrow} 
-\begin{array}{c}
-\text{extended}\\
-\text{and with $\mathfrak{P}$} 
-\end{array} 
-\stackrel{S}{\longleftrightarrow} 
-\begin{array}{c}
-\text{extended }\\
-\text{and with $\mathfrak{P}$} 
-\end{array} 
-\stackrel{T}{\longleftrightarrow} 
+\ewithout \stackrel{T}{\longleftrightarrow} 
+\ewith \stackrel{S}{\longleftrightarrow} 
 \label{nontrivial-chain}
@@
 we obtain the result already presented in Table~\ref{table:main}.
-There is a small puzzle to be resolved, but it's already 1pm. I am going to sleep...
+
+More precisely, when `extended' or `anomaly' is involved, 
+we should better distinguish $\Spin(2n_c)$ and $T\Spin$, etc.
+We find the following:{\small \begin{equation}
+\begin{array}{r@{\,}l|cccccc}
+(n_c,&n_f)  & T\Spin & \Spin & \SO_+ & T\SO_+& T\SO_- & \SO_- \\
+\hline
+(\text{odd},&\text{even}) & \text{e.with} &\text{e.without} & \text{anom} & \text{anom} & \text{e.without } & \text{e.with} \\
+(\text{even},&\text{odd}) & \text{anom} & \text{anom} & \text{e.without } & \text{e.with}  & \text{e.with} & \text{e.without} \\
+(\text{odd},&\text{odd}) & \text{e.without } & \text{e.with} & \text{e.with} & \text{e.without}
+ &  \text{anom} & \text{anom}   \end{array} 
+\end{equation}}
 

### 2021-06-22 paper.tex
more on sl(2,z)

--- 2021-06-21 paper.tex
@@
 \def\tr{\mathop{\mathrm{tr}}}
+
+\def\fP{\mathfrak{P}}
 
@@
 \section{2-group structure}
+\label{sec:2-group}
 Let us first study whether the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ flavor symmetry form a nontrivial 2-group or not. 
@@
 Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q{B},\qquad
-Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \mathfrak{P}(E)} Z_Q[E].
+Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \fP(E)} Z_Q[E].
 \end{equation}
@@
 
+\subsection{$\SL(2,\bZ_2)$ actions with extra background}
+
 Let us now study what happens if we perform this $\SL(2,\bZ_2)$ action when the $\bZ_2$ 1-form symmetry in question is part of a larger symmetry group.
@@
 
-As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly of $\bZ_2\times \bZ_2$ 1-form symmetry of 4d spin QFTs is \begin{equation}
-2\pi i \tfrac12 \int_Y B\beta E  \label{anom}
-\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y,\bZ_2)$ are the background fields,
-there is no anomaly for $\bZ_4$ 1-form symmetry.
+Let us work at the level of anomalies described at the level of cohomology, since we do not need to deal with anomalies more general than that.
+We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G,\U(1))$. 
+We pick a subgroup $H\subset G$ such that $\alpha$ trivializes in it, so that one can find $\mu \in C^d(H,\U(1))$ such that $\delta \mu = \alpha|_H$. 
+We then gauge $H$, using $\mu$ as the action.
+What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$
+Clearly, given $\beta\in C^d(G,\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\beta,\alpha-\delta\beta)$ should give the same result, since we merely added the countertem $\beta$ as the action.
+This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
+by using $\beta$ to be an arbitrary extension of $\mu$ from $H$ to $G$.
+This is convenient in discussing the $\SL(2,\bZ_2)$ action,
+since our $S$ operation is defined in the convention that $\mu=0$.
 
-\subsection{$\SL(2,\bZ_2)$ actions with extra background }
+Now, what are the possible choices of $(\mu,\alpha)$ or $(0,\alpha')$ we need to discuss?
+Let us first consider $\bZ_2\times \bZ_2$ 1-form symmetry.
+As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly for 4d spin QFTs with this symmetry is \begin{equation}
+\alpha=2\pi i \tfrac12  B\beta E  \label{anom}
+\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y,\bZ_2)$ are the background fields.
+Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivially zero,
+and then the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
+\mu = 2\pi i \tfrac12  \tfrac12\fP(E).\label{P}
+\end{equation}
+This $\mu$ can be extended from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ subgroup as a closed cochain.
+Therefore, we only have to consider pairs $(0,0)$ and $(0,\alpha)$.
+
+Next, we consider $\bZ_4$ 1-form symmetry.
+Again in the Appendix~\ref{sec:bordism}, we show that there is no anomaly for $\bZ_4$ 1-form symmetry.
+Therefore we can pick $\alpha=0$. Then the possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
+One difference here is that the discrete theta angle \eqref{P} cannot be extended as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
+As discussed in the Appendix~\ref{sec:nonclosedP}, with $\delta E=\beta a_2$,
+where $a_2\in H^2(X,\bZ_4/\bZ_2)$,
+one finds \begin{equation}
+\alpha':=\delta \mu = 2\pi i \tfrac12 a_2 \beta_2 a_2.
+\end{equation}
+Therefore, the pairs we need to consider are $(0,0)$ and $(\mu,0)\sim (0,\alpha')$.
+
+\def\Textended{extended$_T$}
+Summarizing,  we need to consider the following four choices, namely:
+\begin{itemize}
+\item For $\bZ_2\times \bZ_2$, the pairs $(0,0)$ and $(0,\alpha)$, which we call `none' and `anomaly'
+\item For $\bZ_4$, the pairs $(0,0)$ and $(\mu,0)\sim (0,\alpha')$, which we call `extended' and `\Textended'.
+\end{itemize}
 
 Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
-The case $\bZ_2\times \bZ_2$ with no anomaly is very easy.
+The case `none' is very easy.
 The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
@@
 \text{none} \stackrel{S}{\longleftrightarrow} 
-\label{trivial-chain}
-\end{equation} where `none' stands for $\bZ_2\times \bZ_2$ with no anomaly.
+\label{trivial-chain}.
+\end{equation}
 
-Let us now consider $\bZ_4$ 1-form symmetry and gauge its $\bZ_2$ subgroup,
-without the background term $\frac12\mathfrak{P}(E)$.
-As described in \cite{Tachikawa:2017gyf},
-the resulting theory has $\bZ_2\times \bZ_2$ 1-form symmetry with the anomaly \eqref{anom}.
+Let us now consider $\bZ_4$ 1-form symmetry and gauge its $\bZ_2$ subgroup.
+The case  `extended' was analyzed in \cite{Tachikawa:2017gyf},
+the resulting theory has $\bZ_2\times \bZ_2$ 1-form symmetry with the anomaly \eqref{anom}, 
+which we decided to call `anomaly'.
 
-When we gauge the $\bZ_2$ subgroup  of $\bZ_4$ 1-form symmetry 
-with the background term $\frac12\mathfrak{P}(E)$,
-the resulting theory instead have $\bZ_4$ symmetry
-with the background term $\frac12\mathfrak{P}(E)$.
-This can be seen as follows:
-the gauging process involves the term
+The case `\Textended' was analyzed in \cite{Hsin:2020nts},
+where it was shown that the gauged theory has again `\Textended'.
+Let us quickly recall why this is the case. 
+The gauging process involves the term
  \begin{equation}
-\exp\left(2\pi i\int_X ( \frac14 \mathfrak{P}(E) +\frac12 B E)\right)
+\exp\left(2\pi i\int_X ( \frac14 \fP(E) +\frac12 B E)\right)
 \label{boo}
@@
 Then the second term in \eqref{boo} is not closed, 
-and to even talk about the first term in \eqref{boo}, one first needs to extend the definition of the Pontryagin square $\mathfrak{P}$ to non-closed cochains.
+and to even talk about the first term in \eqref{boo}, one first needs to extend the definition of the Pontryagin square $\fP$ to non-closed cochains.
 
 To make  the coupling \eqref{boo}  well-defined, we consider adding a background term to \eqref{boo} so that we have \begin{equation}
-\exp\left(2\pi i\int_X ( \frac14 \mathfrak{P}(E) +\frac12 B E + \frac14 \mathfrak{P}(B) )\right)
+\exp\left(2\pi i\int_X ( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) )\right)
 = 
-\exp \left(2\pi i \frac14 \int_X \mathfrak{P}(E+B)\right) .
+\exp \left(2\pi i \frac14 \int_X \fP(E+B)\right) .
 \end{equation}
@@
 \end{equation}
-This means that the 1-form symmetry after the gauging is still extended, with a background coupling.
+This means that, starting from `\Textended', performing $S$ and then $T$, we find a theory with the data `extended'.
+Therefore, simply performing $S$ for the theory of the type `\Textended',  one  finds `\Textended'.
 
 Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
+\text{\Textended} \stackrel{T}{\longleftrightarrow} 
 \text{extended} \stackrel{S}{\longleftrightarrow} 
@@
 \text{anomaly} \stackrel{S}{\longleftrightarrow} 
-\text{extended} \stackrel{T}{\longleftrightarrow} 
-\begin{array}{c}
-\text{extended}\\
-\text{and with $\mathfrak{P}$} 
-\end{array} 
-\stackrel{S}{\longleftrightarrow} 
-\begin{array}{c}
-\text{extended }\\
-\text{and with $\mathfrak{P}$} 
-\end{array} 
-\stackrel{T}{\longleftrightarrow} 
+\text{extended}\stackrel{T}{\longleftrightarrow} 
+\text{\Textended}\stackrel{S}{\longleftrightarrow}.
 \label{nontrivial-chain}
 \end{equation}
-where `extended' stands for $\bZ_4$ without the background term $\frac12\mathfrak{P}(E)$,
-`extended with $\mathfrak{P}$' is for $\bZ_4$ with the background term,
-and `anomaly' is $\bZ_2\times \bZ_2$ with the anomaly \eqref{anom}.
 
 \subsection{Anomalies from $\SL(2,\bZ_2)$ action}
+
+\begin{table}
+\centering
+\[
+\begin{array}{r@{\,}l|cccccc}
+(n_c,&n_f)  & T\Spin & \Spin & \SO_+ & T\SO_+& T\SO_- & \SO_- \\
+\hline
+(\text{even},&\text{even}) & \text{none}& \color{Purple}\text{none}& \text{none}& \text{none}& \text{none}& \text{none}\\
+(\text{odd},&\text{even}) & \text{\Textended} &\color{Purple}\text{extended} & \text{anomaly} & \text{anomaly} & \text{extended } & \text{\Textended} \\
+(\text{even},&\text{odd}) & \text{anomaly} & \color{Purple}\text{anomaly} & \text{extended } & \text{\Textended}  & \text{\Textended} & \text{extended} \\
+(\text{odd},&\text{odd}) & \text{extended } & \color{Purple}\text{\Textended} & \text{\Textended} & \text{extended}
+ &  \text{anomaly} & \text{anomaly}   \end{array} 
+\]
+\caption{The symmetry structure of $\so(2n_c)$ QCD with $2n_f$ flavors,
+as deduced from the 2-group structures found in Sec.~\ref{sec:2-group}
+and from the $\SL(2,\bZ_2)$ action discussed in this section.
+The symmetry structure of the $\Spin$ case will be checked independently in the next section.
+\label{table:refined}}
+\end{table}
+
 Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
@@
 we obtain the result already presented in Table~\ref{table:main}.
-There is a small puzzle to be resolved, but it's already 1pm. I am going to sleep...
+More precisely, we should better distinguish $\Spin(2n_c)$ and $T\Spin$, etc.,
+and we find the assignment given in Table~\ref{table:refined}.
+As the way we determined the symmetry structures were somewhat indirect,
+we confirm the symmetry structures of the $\Spin$ case in the next section
+in a different means.
+
+\section{Fermion contribution to anomalies}
 
@@
 The corresponding invariant in 4d is simply \begin{equation}
-\exp(2\pi i \frac{p}{4} \int \frac12\mathfrak{P}(a) )
+\exp(2\pi i \frac{p}{4} \int \frac12\fP(a) )
 \end{equation}
-where $\mathfrak{P}:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
+where $\fP:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
 which is even mod 8 on a spin manifold.
@@
 
-The corresponding bordism invariants in 4d are $\mathfrak{P}(a)/2$, $ab$, $\mathfrak{P}(b)/2$, 
+The corresponding bordism invariants in 4d are $\fP(a)/2$, $ab$, $\fP(b)/2$, 
 and the one in 5d is $a\beta b$.
+
+\section{Pontrjagin square for non-closed cochains}
+\label{sec:nonclosedP}
+By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2^m}) \to H^{2\bullet}(-;\bZ_{2^{m+1}})$ term is
+\begin{equation}
+	\label{deltaPontrjagin}
+	\begin{array}{ccl}
+		\delta \left(\dfrac{1}{2^{m+1}}\fP(x)\right)
+		& = & \dfrac{1}{2^{m+1}}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
+		& = & \dfrac{1}{2^{m+1}}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
+				- \Big(\widetilde x \cup \delta \widetilde x - \delta \widetilde x \cup \widetilde x + \delta \widetilde x \cup_1 \delta \widetilde x\Big)\right]\vspace{2mm}\\
+		& = & \dfrac{1}{2^{m+1}}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
+	\end{array}
+\end{equation}
+and thus if $x$ were a $\bZ_{2^m}$-cocycle, 
+its integral lift $\widetilde x \in C^\bullet(-;\bZ)$ would be a cocycle mod $2^m$ \textit{i.e.}~$\delta \widetilde x = 0$ (mod $2^m$),
+and the right hand side would be $0$ mod 1,
+which then means that $\fP(x)$ would be a $\bZ_{2^{m+1}}$-cocycle as desired.
+However, when $x$ is not a cocycle but merely a cochain,
+$\fP(x)$ is also not a cocycle and it is not clear whether this term is well-defined in the first place.
+
+This problem arises when we consider $SO(2n_c)$ QCD,
+but it turns out that this can be saved somewhat miraculously as follows.
+First, a short exact sequence
+\begin{equation*}
+	0
+	\to
+	\bZ_{2^f}
+	\overset{\times 2^{f}}{\longrightarrow}
+	\bZ_{2^{2f}}
+	\overset{p}{\longrightarrow}
+	\bZ_{2^f}
+	\to
+	0
+\end{equation*}
+buys us cohomology operations called the higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
+and for the element $y \in C^{\bullet}(-;\bZ_{2^f})$ one has
+\begin{equation*}
+	\delta (p^\ast y)
+	=
+	2^f \beta_f (y) \in C^\bullet(-;\bZ_{2^{2f}}).
+\end{equation*}
+Now, let us consider the case of odd $n_c$.
+Here, the cochain $w_2(c) \in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_2)$
+can be thought of as a mod-2 reduction of $\widetilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
+Dividing the $SO\times SU$ by $\bZ_2$, these cochains become non-closed
+\begin{equation*}
+	\delta \widetilde w_2(c) = 2 \beta v_2(c)
+\end{equation*}
+where $v_2(c)=a_2\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
+%\begin{equation*}
+%	\begin{array}{ccccccccc}
+%		&& w_2 && \widetilde w_2 & \longmapsto & v_2\\
+%		&& \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$}\\
+%		0
+%		& \longrightarrow &
+%		C^2(-;\bZ_2)
+%		& \overset{i^\ast}{\longrightarrow} &
+%		C^2(-;\bZ_4)
+%		& \overset{p^\ast}{\longrightarrow} &
+%		C^2(-;\bZ_2)
+%		& \longrightarrow &
+%		0\vspace{1mm}\\
+%		&& \downarrow\,\delta && \downarrow\,\delta && \downarrow\vspace{1mm}\\
+%		0
+%		& \longrightarrow  &
+%		C^3(-;\bZ_2)
+%		& \longrightarrow &
+%		C^3(-;\bZ_4)
+%		& \longrightarrow &
+%		C^3(-;\bZ_2)
+%		& \longrightarrow &
+%		0\\
+%		&& \rotatebox[]{90}{$\in$} && \rotatebox[]{90}{$\in$}\\
+%		&& \delta w_2 && \delta \widetilde w_2
+%	\end{array}
+%\end{equation*}
+Since this implies $\delta \widetilde w_2(c) = 0$ or $2$ mod 4
+and furthermore $\delta (2\widetilde w_2(c)) = 0$ mod 4,
+one can safely define the Pontrjagin square $\tfrac{1}{8}\fP\big(2\widetilde w_2(c)\big)$.\footnote{
+	Be careful that this factor $2$ here is not the usual map sending $\{0,1\}=\bZ_2$ to $\{0,2\}\subset \bZ_4$.
+	This time we are \textit{really} multiplying by $2$.
+}
+Note that this can naively be regarded as $2\cdot \tfrac{1}{4}\fP\big(w_2(c)\big)$ at the integral cochain level.
+While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
+$\tfrac{(2^m)^2}{2^{m+1}}\bZ = 2^{m-1}\bZ = 2\bZ$ and dividing by two does not cause any trouble,
+the first term does as it takes value in $\tfrac{2\cdot 2^m}{2^{m+1}}\bZ = \bZ$.
+
+Let us take a closer look at the latter.
+The long exact sequence of cochain groups implies that $2\widetilde w_2(c)$ can be replaced by
+$\widetilde v_2(c) = \widetilde a_2$, which is a cocycle mod 4.
+Then the term of interest is
+\begin{equation*}
+	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\widetilde a_2 \cup \widetilde a_2.
+\end{equation*}
+Therefore, the anomalous variation of the Pontrjagin square term seems to result in
+\begin{equation*}
+	\delta\left(
+		\dfrac{1}{4}\fP(w_2(c))
+	\right)
+	=
+	\dfrac{1}{2}a_2 \beta_2 a_2.
+\end{equation*}
 

### 2021-06-22 paper.tex
anomaly via effective interaction

@@
 \usepackage{tikz}
-%\usepackage{tikz-cd}
+\usepackage{tikz-cd}
 \newcommand{\tikzmark}[1]{\tikz[remember picture,overlay]\node (#1){};}
@@
 
-\setcounter{tocdepth}{3}
+\setcounter{tocdepth}{2}
 \tableofcontents
@@
 \section{$\SL(2,\bZ_2)$ action and the anomalies}
-
+\label{sec:sl2z}
 In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
@@
 
-\subsection{$\SL(2,\bZ_2)$ action}
+\subsection{$\SL(2,\bZ_2)$ action and $\so$ gauge theories}
+
 Let us say that  a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry is given.
@@
 This operation was considered in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.
-
-\subsection{$\SL(2,\bZ_2)$ action and $\so$ gauge theories}
 
@@
 one finds \begin{equation}
-\alpha':=\delta \mu = 2\pi i \tfrac12 a_2 \beta_2 a_2.
+\alpha':=\delta \mu = 2\pi i \tfrac12 a_2 \beta_2 a_2.\label{anom'}
 \end{equation}
@@
 \section{Fermion contribution to anomalies}
+So far, we first determined the 2-group structure in Sec.~\ref{sec:2-group} by studying the charges of line operators,
+and then determined the anomalies in Sec.~\ref{sec:sl2z} by matching it to the action of $\SL(2,\bZ_2)$.
+Going over  the entries on the column $\Spin$ of Table~\ref{table:refined},
+we find that the anomaly is trivial when $(n_c,n_f)$ is (even,even) or (odd,even),
+while it is $\alpha$ when $(n_c,n_f)$ is (odd,even) and $\alpha'$ when (odd,odd).
+Since the 1-form symmetry background in the $\Spin$ theory is simply the class $w_2$ of the $\SO(2n_c)$ gauge bundle, 
+these anomalies should simply come from the anomalies of fermions under $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
+Here we use $\USp(2n_f)$ instead of $\SU(2n_f)$, because under the latter we also have perturbative anomalies, which could potentially complicate the analysis.
+
+More explicitly, for $n_c$ even, the anomaly should be given by  \begin{equation}
+\alpha= 2\pi i \frac12 w_2 \beta v_2
+\end{equation} when $n_c$ is even,
+where $w_2,v_2$ are the classes in $H^2(X,\bZ_2)$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
+and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively,
+and for $n_c$ odd, the anomaly cochain should be given by 
+ \begin{equation}
+\alpha'=2\pi i \frac12 a_2 \beta_2 a_2
+\end{equation} where $a_2$ is the class in $H^2(X,\bZ_2)$ which is the mod-2 reduction of
+the class in $H^2(X,\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\bZ_4$.
+We note that $\alpha'$ is exact, but as explained in the previous section, this still affects the gauging process.
+
+The aim of this last section is to give a check of these anomalies from a different point of view.
+We will proceed as follows. 
+We add scalar fields, adjoint under $\USp(2n_f)$ in the system, and break it a subgroup.
+We then determine the effective interaction induced by the fermion zero modes.
+The next step is to see what happens when the symmetry group is further changed from $\SO(2n_c)\times \USp(2n_f)$ to its $\bZ_2$ quotient.
+We will see that the effective interaction will have the required anomalies.
+
+Before proceeding, we have two remarks.
+First, this method was first used in \cite[Sec.~4]{Witten:1995gf} under the name of `a curious minus sign', and recognized as determining an anomaly in \cite[Sec.~2.4.3]{Cordova:2018acb}.
+It was also used in \cite[Sec.~3.1 and Sec.~5.1.2]{Wang:2018qoy}.
+Second, in this section we can only say that the effective interaction we find is compatible with the anomalies
+as found in Sec.~\ref{sec:sl2z},
+and will not be able to determine it completely.
+This is mostly due to the fact that the computation of the spin bordism group $\Omega^\text{spin}_d([\SO(2n_c)\times \USp(2n_f)]/\bZ_2)$ which governs the anomaly is quite hard, 
+because even the integral cohomology of the group in question is hard to obtain.
+In only a couple of cases we can say more, as we comment along the way.
+
+\subsection{Effective interaction}
+We break $\USp(2n_f)$ down to $\U(n_f)$, using a scalar field,
+such that the fundamental representation of $\USp(2n_f)$ splits to the fundamental plus the antifundamental of $\U(n_f)$.
+The monopole charge is given by the first Chern class $c_1$ of the low-energy $\U(n_f)$.
+
+Take a standard 't Hooft-Polyakov monopole associated to $\U(1)\subset \USp(2)$
+and embed it into  $\U(n_f)\subset \USp(2n_f)$.
+The fermion zero modes form a vector representation of $\SO(2n_c)$,
+whose quantization leads to the spinor representation.
+This means that there is an effective interaction \begin{equation}
+2\pi i \frac12 \int_X w_2 c_1
+\end{equation} where $w_2$ is the Stiefel-Whitney class of the $\SO(2n_c)$ bundle
+and $c_1$ is the first Chern class of $\U(n_f)$.
+
+\subsection{Anomalies}
+We now take the $\bZ_2$ quotient, changing the symmetry group from 
+$\SO(2n_c)\times \USp(2n_f)$ to $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
+Note that $\pi_1(U(n_f)/\bZ_2)$ is $\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
+
+Furthermore, when $n_f$ is even, $c_1(\U(n_f)) = c_1(\U(n_f)/\bZ_2)$ and $v_2(\U(n_f)/\bZ_2)=v_2(\USp(2n_f))$.
+When $n_f$ is odd, $c_1(\U(n_f)/\bZ_2)=2 c_1(\U(n_f))$ when the latter is well-defined and $v_2(\U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(\U(n_f)/\bZ_2)$.
+We now compute the anomaly cochains in the four cases separately:
+\paragraph{$(n_c,n_f)$=(even,even):}
+$w_2(\SO(2n_c))$ and $c_1(\U(n_f))$ can be generalized without problem,
+and therefore \begin{equation}
+\delta(\frac12 w_2(\SO(2n_c)) c_1(\U(n_f))) = 0.
+\end{equation}
+
+\paragraph{$(n_c,n_f)$=(odd,even):}
+$w_2(\SO(2n_c))$ needs to be upgraded to a $\bZ_4$-valued cochain $a_2(\SO(2n_c)/\bZ_2)$.
+The original interaction is then \begin{equation}
+\frac14 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f))
+\end{equation}
+which is closed without problem,
+and therefore its $\delta$ is zero.
+
+\paragraph{$(n_c,n_f)$=(even,odd):}
+Here we need to replace $c_1(\U(n_f))$ by $c_1(\U(n_f)/\bZ_2)/2$.
+The effective interaction is then \begin{equation}
+\frac14 w_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 
+\end{equation} whose $\delta$ is \begin{align}
+\delta(\frac14 w_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) )
+&= \frac12 (\frac12\delta w_2(\SO(2n_c)) c_1(\U(n_f)/\bZ_2) ) \\
+&= \frac12 (\beta w_2(\SO(2n_c)))c_1(\U(n_f)/\bZ_2) 
+\end{align}
+which is the pull-back of the anomaly cochain
+\begin{equation}
+ \frac12 (\beta w_2(\SO(2n_c)))v_2(\USp(2n_f)/\bZ_2). 
+\end{equation}
+When $n_c=2$ and $n_f=1$, we can confirm this is indeed the entire anomaly,
+since we can compute $\mathrm{Hom}(\Omega^\text{spin}_5([\SO(4)\times \USp(2)]/\bZ_2),\U(1))$
+and show that this is the only nontrivial element there.
+For details, see Appendix~\ref{sec:so4su2}.
+
+\paragraph{$(n_c,n_f)$=(odd,odd):}
+Now we make the replacement on both sides and the effective interaction is \begin{equation}
+\frac18 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 
+\end{equation}
+whose $\delta$ is \begin{align}
+\delta(\frac18 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) )
+&= \frac12 (\frac14\delta a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) ) \\
+&= \frac12 (\beta_2 a_2(\SO(2n_c)/\bZ_2))c_1(\U(n_f)/\bZ_2) 
+\end{align}
+which is the pull-back of \begin{equation}
+ \frac12 (\beta_2 a_2(\SO(2n_c)))v_2(\USp(2n_f)).
+\end{equation}
+We now recall that the symmetry we are considering now is $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$,
+and therefore there is a single degree-2 obstruction cochain which equals both $a_2$ and $v_2$,
+and therefore the anomaly cochain is \begin{equation}
+ \frac12 (\beta_2 a_2(\SO(2n_c)))a_2(\USp(2n_f)).
+\end{equation}
+This is what we wanted to show.
+Recall that this anomaly cochain is exact as we repeatedly mentioned.
+This is consistent with our computation of the bordism group in Appendix~\ref{sec:so(2odd)},
+where we show that $\Omega^\text{spin}_5([\SO(2n_c)\times \USp(2n_f)]/\bZ_2=0$ when $n_c$ is odd.
+
+\section*{Acknowledgments}
+The authors thank discussions with 
+Lakshya Bhardwaj,
+Clay C\'ordova,
+Po-shen Hsin,
+Ho Tat Lam,
+Sakura Sch\"afer-Nameki,
+Nati Seiberg,
+and Yunqin Zheng.
+
+Y.L.~is partially supported by the Programs for Leading Graduate Schools, MEXT, Japan, via the Leading Graduate Course for Frontiers of Mathematical Sciences and Physics
+and also by JSPS Research Fellowship for Young Scientists.
+Y.T.~is partially supported  by JSPS KAKENHI Grant-in-Aid (Wakate-A), No.17H04837 
+and also by WPI Initiative, MEXT, Japan at IPMU, the University of Tokyo.
 
@@
 and the one in 5d is $a\beta b$.
+
+\subsection{$[\SO(4)\times \SU(2)]/\bZ_2$}
+\label{sec:so4su2}
+
+\subsubsection{Leray-Serre SS (preparatory)}
+For the various input of cohomology groups, see Appendix A of our WZW paper.
+For the fibration
+\begin{equation}
+	BSO(3)
+	\ \to\ 
+	B\left(SO(3)\times SO(3)\right)
+	=
+	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+	\ \to\ 
+	BSO(3)
+\end{equation}
+one has
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(BSO(3);H^q(BSO(3);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6 & \bZ_2 && \ast & \ast & \ast & \ast & \ast \\
+			5  & \hphantom{\bZ_2}\cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast && \ast\\
+			3  & \bZ_2 && \bZ_2\cellcolor{lightyellow} & \bZ_2 & \ast & \ast & \ast \\
+			2  & &  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_2 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  &\bZ_2^{\oplus 3}\\
+			5  & \bZ_2\cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 2}\\
+			3  & \bZ_2^{\oplus 2}\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+Here we expect non-trivial differentials to be absent (for the region of interest)
+from the explicit consideration of generators (since there are $W_3$ and $W'_3$, there should be $(W_3)^2$, $(W'_3)^2$, and $W_3W'_3$)
+or by requiring proper reproduction of the $\bZ_2$ cohomology (which we expect to be generated by $w_2$, $w'_2$, $w_3$, and $w'_3$).
+Then, for the fibration
+\begin{equation}
+	BSU(2)
+	\ \to\ 
+	B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right)
+	\ \to\ 
+	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+\end{equation}
+we can further plug it into
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(B\left(\tfrac{SO(4)}{\bZ_2}\right);H^q(BSU(2);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \red{\fbox{\black{$\bZ$}}} & \cellcolor{lightyellow} && \ast & \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  &&  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_2^{\oplus 2} & \bZ^{\oplus 2} & \red{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & \bZ_2^{\oplus 3}\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 3}\\
+			3  & \bZ_2^{\oplus 2}\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+Taking the normalization of instanton number into account (see Ohmori-san's e-mail on 2020-08-19),
+the differential \red{\fbox{\black{$d_2 : E_{0,4} \to E_{5,0}$}}} seems to be non-trivial.
+
+So we believe the integral cohomology structure to be
+\begin{equation}
+	\label{case1}
+	\renewcommand{\arraystretch}{1.2}
+	\begin{array}{c|cccccccccccccccc}
+		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
+		\hline
+		H^d(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ) & \bZ & 0 & 0 & \bZ_2^{\oplus 2} & \bZ^{\oplus 3} & 0 & \bZ_2^{\oplus 3} & \cdots\\
+		\hline
+		\text{generator} & 1 & - & - & W_3 & p_1 & - & (W_3)^2 & \cdots\\
+		&&&& W'_3 & p'_1 && (W'_3)^2\\
+		&&&&& 2c_2 && W_3W'_3
+	\end{array}
+\end{equation}
+where the reduction to $\bZ_2$ cohomology are
+\begin{equation}
+	\begin{array}{ccc}
+		W_3 & \to & w_3\\
+		p_1 & \to & (w_2)^2\\
+%		y_5 & \to & w_2w'_3 + w_3w'_2 \,(?)\\
+	\end{array}
+\end{equation}
+
+\subsubsection{Atiyah-Hirzebruch SS}
+%Turning cohomology groups into homology groups via the universal coefficient theorem,
+Having obtained (co)homology groups,
+one can fill in the $E^2$-page of the AHSS:
+\begin{equation}
+	\begin{array}{ccc}
+		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2} && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\dbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \bZ_2^{\oplus 3} & \ast & \ast\\
+			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 3}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\bZ_2^{\oplus 3}$}}} & \ast\\
+			0 & \bZ &  & \bZ_2^{\oplus 2} &  & \red{\fbox{\black{$\bZ^{\oplus 3}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 3}$}}} \cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+	\end{array}
+\end{equation}
+Based on our belief, 
+\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
+\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 w_2 & = & (w_2)^2 \\
+		Sq^2 w'_2 & = & (w'_2)^2
+	\end{array}
+\end{equation}
+and also
+\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
+\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 w_3 & = & w_2w_3\\
+		Sq^2 w'_3 & = & w'_2w'_3
+	\end{array}
+\end{equation}
+and finally \green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 (w_2w'_2) & = & w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2
+	\end{array}
+\end{equation}
+then %one can proceed, and 
+the would-be-$E_3$-page is given by
+\begin{equation}
+	\label{e3page1}
+	\begin{array}{c|c:cccccccccccc}
+		6  &&&&&& \\
+		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
+		2  & \bZ_2 &  && \cellcolor{lightyellow} & \ast & \ast & \ast\\
+		1  & \bZ_2 &&  && \cellcolor{lightyellow} & \ast & \ast\\
+		0 & \bZ &  & \bZ_2^{\oplus 2} &  & \bZ^{\oplus 3} & \bZ_2\cellcolor{lightyellow} & \ast\\
+		\hline
+		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+	\end{array}
+\end{equation}
+
+\subsubsection{Adams SS}
+According to our naive guess, the module $\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
+\begin{equation}
+	\begin{tikzpicture}[thick,baseline=(m-2-4.south)]
+		\matrix (m) [
+			matrix of math nodes,
+			row sep= 1em,
+			column sep=6em,
+		]{
+			&&& \colorB{\bullet}\\
+			&&& \colorB{\bullet}\\
+			&&& \colorB{\bullet}\\
+			&& \colorB{\bullet} & \colorB{\bullet}\\
+			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
+		    \colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet} & \colorD{\bullet}\\
+			\colorA{\bullet} && \colorB{\bullet} && \colorC{\bullet}\\
+			\colorA{\bullet} &&&& \colorC{\bullet}\\
+			\colorA{\bullet} &&&& \colorC{\bullet}\\
+		};
+		\draw[colorA] (m-7-1.center) to [out=200, in=160] (m-9-1.center);
+		\draw[colorA] (m-9-1.center) to (m-8-1.center);
+		\draw[colorA] (m-5-1.center) to [out=200, in=160] (m-7-1.center);
+		\draw[colorA] (m-6-1.center) to (m-5-1.center);
+		\draw[colorA] (m-6-1.center) to [out=340, in=20] (m-8-1.center);
+		%
+		\node[colorA, right=4pt] at (m-9-1) {$w_2$};
+		\node[colorA, right=6pt] at (m-8-1) {$w_3$};
+		\node[colorA, left=6pt] at (m-7-1) {$(w_2)^2$};
+		\node[colorA, right=6pt] at (m-6-1) {$w_2w_3$};
+		\node[colorA, left=4pt] at (m-5-1) {$(w_3)^2$};
+		%
+		\draw[colorB] (m-7-3.center) to [out=160, in=200] (m-5-3.center);
+		\draw[colorB, dotted] (m-7-3.center) to (m-6-3.center);
+		\draw[colorB, dotted] (m-6-3.center) to [out=5, in=185] (m-4-4.center);
+		\draw[colorB] (m-5-3.center) to (m-4-3.center);
+		\draw[colorB, dotted] (m-5-3.center) to [out=5, in=185] (m-3-4.center);
+		\draw[colorB, dotted] (m-4-4.center) to (m-3-4.center);
+		\draw[colorB] (m-4-3.center) to [out=5, in=185] (m-2-4.center);
+		\draw[colorB, dotted] (m-2-4.center) to (m-1-4.center);
+		\draw[colorB, dotted] (m-3-4.center) to [out=5, in=355] (m-1-4.center);
+		%
+		\node[colorB, right=4pt] at (m-7-3) {$w_2w'_2$};
+		\node[colorB, right=4pt] at (m-6-3) {$w_3w'_2 + w_2w'_3$};
+		\node[colorB, left=4pt] at (m-5-3) {$w_3w'_3 + (w_2)^2w'_2 + w_2(w'_2)^2$};
+		\node[colorB, left=4pt] at (m-4-3) {$(w_2)^2w'_3 + w_3(w'_2)^2$};
+		%
+		\node[colorB, right=4pt] at (m-4-4) {$\begin{array}{r}
+			w_2w_3w'_2 + w_3(w'_2)^2
+			+ (w_2)^2w'_3 + w_2w'_2w'_3
+		\end{array}$};
+		\node[colorB, right=4pt] at (m-3-4) {$\begin{array}{r}
+			(w_3)^2w'_2 + w_2w_3w'_3
+			+ w_3w'_2w'_3 + w_2(w'_3)^2
+		\end{array}$};
+		\node[colorB, left=4pt] at (m-2-4) {$\begin{array}{r}
+			(w_3)^2w'_3 + (w_2)^2w'_2w'_3
+			+ w_2w_3(w'_2)^2 + w_3(w'_3)^2
+		\end{array}$};
+		\node[colorB, right=4pt] at (m-1-4) {$\begin{array}{r}
+			(w_2)^2(w'_3)^2 + (w_3)^2(w'_2)^2
+		\end{array}$};
+		%
+		\draw[colorC] (m-7-5.center) to [out=200, in=160] (m-9-5.center);
+		\draw[colorC] (m-9-5.center) to (m-8-5.center);
+		\draw[colorC] (m-5-5.center) to [out=200, in=160] (m-7-5.center);
+		\draw[colorC] (m-6-5.center) to (m-5-5.center);
+		\draw[colorC] (m-6-5.center) to [out=340, in=20] (m-8-5.center);
+		%
+		\node[colorC, right=4pt] at (m-9-5) {$w'_2$};
+		\node[colorC, right=6pt] at (m-8-5) {$w'_3$};
+		\node[colorC, left=6pt] at (m-7-5) {$(w'_2)^2$};
+		\node[colorC, right=6pt] at (m-6-5) {$w'_2w'_3$};
+		\node[colorC, left=4pt] at (m-5-5) {$(w'_3)^2$};
+		%
+		\node[colorD, right=4pt] at (m-6-6) {(*)};
+	\end{tikzpicture}
+\end{equation}
+To be consistent with the AHSS computation,
+it seems that $w_3w_2' + w_2w'_3$ should be modded out
+(is it an obvious consequence of the transgression in LSSS...?)
+and the remaing part \colorD{(*)} turns out to be
+\begin{equation}
+	\begin{tikzpicture}[colorD, thick,baseline=(m-2-1.south)]
+		\matrix (m) [
+			matrix of math nodes,
+			row sep= 1em,
+			column sep=6em,
+		]{
+			\bullet\\
+		    \bullet\\
+			\bullet\\
+			\bullet\\
+			\bullet\\
+		};
+		\draw (m-3-1.center) to [out=200, in=160] (m-5-1.center);
+		\draw (m-5-1.center) to (m-4-1.center);
+		\draw (m-1-1.center) to [out=200, in=160] (m-3-1.center);
+		\draw (m-2-1.center) to (m-1-1.center);
+		\draw (m-2-1.center) to [out=340, in=20] (m-4-1.center);
+		%
+		\node[right=4pt] at (m-5-1) {$w_2w'_3 = w_3w'_2$};
+		\node[right=6pt] at (m-4-1) {$w_3w'_3$};
+		\node[left=6pt] at (m-3-1) {$(w_2)^2w'_3 + w_2w'_2w'_3$};
+		\node[right=6pt] at (m-2-1) {$w_2w_3w'_3 + w_3w'_2w'_3$};
+		\node[left=4pt] at (m-1-1) {$(w_3)^2w'_3 + w_3(w'_3)^2$};
+	\end{tikzpicture}
+\end{equation}
+and therefore one concludes
+\begin{equation}
+	\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
+\end{equation}
+This leads to the following Adams chart:
+\begin{center}
+	\begin{sseqdata}[
+		name=M,
+		Adams grading,
+		classes = fill,
+		xrange = {0}{5},
+		yrange = {0}{3},
+		%,x label = {$t-s$}, y label = {$s$}
+	]
+		\tower[colorB](4,0)
+		\class[white](4,0)
+		\class[white](4,0)
+		\class[colorA](2,0)
+		\class[colorC](2,0)
+		\tower[colorA](4,1)
+		\tower[colorC](4,1)
+		\class[colorD](5,0)
+	\end{sseqdata}
+	\printpage[name = M,page = 2]
+\end{center}
+and it indeed seems to be compatible with the AHSS computation.
+If the above argument (and beliefs) is correct, then the anomaly should be captured by
+\begin{equation}
+	w_2w'_3\ (= w_3w'_2).
+\end{equation}
+
+\subsection{$[SO(4n'_c+2)\times SU(2n_f)]/\bZ_2$}
+\label{sec:so(2odd)}
+
+\subsubsection{Cohomology of $BPSO(4n'_c+2)$}
+Recalling that the $\bZ_2$ cohomology read off from \cite{KonoMimura1974}
+allowed us to determine the $\bZ$ cohomology by using Bockstein SS
+(see \texttt{wzw-memo.pdf}, copy later), we had
+\begin{equation}
+	\renewcommand{\arraystretch}{1.2}
+	\begin{array}{c|cccccccccccccccc}
+		d & 0 & 1 & 2 & 3 & 4 & 5 & 6 & \cdots \\
+		\hline
+		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ)} & \bZ & 0 & 0 & \bZ_4 & \bZ & 0 & \bZ_2 & \cdots\\
+		\multicolumn{1}{l|}{H^d(BPSO(4n'_c+2);\bZ_2)} & \bZ_2 & 0 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2 & \bZ_2^{\oplus 2} & \cdots\\
+		\hline
+		\text{generator} \,(\bZ_2) & 1 & - & a_2 & y'(1) & (a_2)^2 & y'(2) & (a_2)^3 & \cdots\\
+		&&&&&&& y'(1)^2\\
+	\end{array}
+\end{equation}
+and if we assume the suspension $\bar\theta: H^\ast(PSO(4n'_c+2);\bZ_2) \to H^\ast(BPSO(4n'_c+2);\bZ_2)$
+to commute with Steenrod squares (which seems to be true according to Nishimoto-san's notes),
+then these elements are supposed to be related as
+\begin{equation*}
+	\begin{array}{ccl}
+		\beta_2 a_2 & = & y'(1)\\
+		Sq^2 y'(1) & = & y'(2)\\
+		Sq^1 y'(2) & = & y'(1)^2\\
+	\end{array}
+\end{equation*}
+where $\beta_f$ is a higher Bockstein operator (reduced to $\bZ_2$ cohomology as a whole),
+whose image corresponds to $\bZ_{2^f}$ in integral cohomology.
+
+\subsubsection{Leray-Serre SS (preparatory)}
+For the fibration
+\begin{equation}
+	BSU(2n_f)
+	\ \to\ 
+	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
+	\ \to\ 
+	BPSO(4n'_c+2)
+\end{equation}
+we have
+\begin{equation}
+	\begin{array}{ccc}
+		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		\begin{array}{c|ccccccccccccc}
+			6  & \bZ &&& \ast & \ast && \ast\\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast & & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  &&  && \cellcolor{lightyellow} &&\\
+			1  &  &&  && \cellcolor{lightyellow} &&\\
+			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+		& \longrightarrow & 
+		\begin{array}{c|c}
+			6  & \bZ\oplus \bZ_2\\
+			5  & \cellcolor{lightyellow}\\
+			4  & \bZ^{\oplus 2}\\
+			3  & \bZ_4\\
+			2  & \\
+			1  & \\
+			0 & \bZ\\
+			\hline\\
+		\end{array}
+	\end{array}
+\end{equation}
+
+\subsubsection{Atiyah-Hirzebruch SS}
+Having obtained (co)homology groups,
+one can fill in the $E^2$-page of the AHSS:
+\begin{equation}
+	\begin{array}{c}
+		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
+		\begin{array}{c|c:cccccccccccc}
+			6  &&&&&& \\
+			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+			3  &  && \cellcolor{lightyellow} &&&\\
+			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
+			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
+			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
+			\hline
+			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+		\end{array}
+	\end{array}
+\end{equation}
+Based on our belief, 
+\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
+\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 a_2 & = & (a_2)^2
+	\end{array}
+\end{equation}
+and also
+\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
+\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 y'(1) & = & y'(2)\\
+	\end{array}
+\end{equation}
+and finally
+\green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
+\begin{equation}
+	\begin{array}{ccccc}
+		Sq^2 c_2 & = & c_3
+	\end{array}
+\end{equation}
+then %one can proceed, and 
+the would-be-$E_3$-page is given by
+\begin{equation}
+	\begin{array}{c|c:cccccccccccc}
+		6  &&&&&& \\
+		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
+		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
+		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
+		2  & \bZ_2 &&& \cellcolor{lightyellow} & \ast & \ast & \ast\\
+		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
+		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \cellcolor{lightyellow} & \ast\\
+		\hline
+		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
+	\end{array}
+\end{equation}
 

### 2021-06-22 paper.tex
title; more duality action

@@
 
-{\Large \bfseries Higher symmetries and anomalies \\[1em]
-in $\so$ QCD  and \Nequals1 duality}
+{\Large \bfseries Matching higher symmetries \\[1em]
+across Intiligator-Seiberg duality}
 
@@
 \hline
-(\text{even},&\text{even}) & \text{none}& \color{Purple}\text{none}& \text{none}& \text{none}& \text{none}& \text{none}\\
-(\text{odd},&\text{even}) & \text{\Textended} &\color{Purple}\text{extended} & \text{anomaly} & \text{anomaly} & \text{extended } & \text{\Textended} \\
-(\text{even},&\text{odd}) & \text{anomaly} & \color{Purple}\text{anomaly} & \text{extended } & \text{\Textended}  & \text{\Textended} & \text{extended} \\
-(\text{odd},&\text{odd}) & \text{extended } & \color{Purple}\text{\Textended} & \text{\Textended} & \text{extended}
- &  \text{anomaly} & \text{anomaly}   \end{array} 
+\vphantom{\Bigm|}(\text{even},&\text{even}) & \text{none}\tikzmark{a1}& \color{Purple}\text{none}\tikzmark{a2}& \text{none}\tikzmark{a3}& \tikzmark{a4}\text{none}& \tikzmark{a5}\text{none}& \tikzmark{a6}\text{none}\\
+\vphantom{\Bigm|}(\text{odd},&\text{even}) & \text{\Textended}\tikzmark{b1} &\color{Purple}\text{extended}\tikzmark{b2} & \text{anomaly}\tikzmark{b3} & \tikzmark{b4}\text{anomaly} & \tikzmark{b5}\text{extended } & \tikzmark{b6}\text{\Textended} \\
+\vphantom{\Bigm|}(\text{even},&\text{odd}) & \text{anomaly}\tikzmark{c1} & \color{Purple}\text{anomaly}\tikzmark{c2} & \text{extended}\tikzmark{c3} & \tikzmark{c4}\text{\Textended}  & \tikzmark{c5}\text{\Textended} & \tikzmark{c6}\text{extended} \\
+\vphantom{\Bigm|}(\text{odd},&\text{odd}) & \text{extended}\tikzmark{d1} & \color{Purple}\text{\Textended}\tikzmark{d2} & \text{\Textended}\tikzmark{d3} & \tikzmark{d4}\text{extended}
+ &  \tikzmark{d5}\text{anomaly} & \tikzmark{d6}\text{anomaly}   \end{array} 
 \]
+\tikz[overlay,remember picture]{%
+\draw[<->,bend left,color=Orange,line width=1.5] (a1.north) to (a6.north);
+\draw[<->,bend left,color=Orange,line width=1.5] (a2.north) to (a5.north);
+\draw[<->,color=Orange,line width=1.5] (a3) to (a4);
+\draw[<->,bend right,color=Orange,line width=1.5] (b1.south) to (b6.south);
+\draw[<->,bend right,color=Orange,line width=1.5] (b2.south) to (b5.south);
+\draw[<->,color=Orange,line width=1.5] (b3.south) to (b4.south);
+\draw[<->,color=Orange,line width=1.5] (c1.south) to (d6.north);
+\draw[<->,color=Orange,line width=1.5] (c2.south) to (d5.north);
+\draw[<->,color=Orange,line width=1.5] (c3.south) to (d4.north);
+\draw[<->,color=Orange,line width=1.5] (c4.south) to (d3.north);
+\draw[<->,color=Orange,line width=1.5] (c5.south) to (d2.north);
+\draw[<->,color=Orange,line width=1.5] (c6.south) to (d1.north);
+}
 \caption{The symmetry structure of $\so(2n_c)$ QCD with $2n_f$ flavors,
@@
 in a different means.
+
+We can also use this Table~\ref{table:refined}
+to give a further check of the Intriligator-Seiberg duality,
+which is known to act as follows:
+\begin{equation}
+\begin{array}{ccc}
+	\Spin(2n_c) & \leftrightarrow & T(\SO_-(2n_f-2n_c+4)),\\
+	\SO_+(2n_c) & \leftrightarrow & T(\SO_+(2n_f-2n_c+4)),\\ 
+	\SO_-(2n_c) & \leftrightarrow & T(\Spin(2n_f-2n_c+4)).
+\end{array}
+\end{equation} 
+We see that the symmetry structure is indeed preserved across the duality.
+This duality action  taking  the finer distinction of $Q$ and $TQ$ into account was
+first discussed in \cite[Sec.~6]{Gaiotto:2014kfa} and further discussed in \cite{Bhardwaj:2020ymp}.
 

### 2021-06-23 paper.tex
Update on Overleaf.
minor typos fixed

@@
 
-{\Large \bfseries Matching higher symmetries \\[1em]
-across Intiligator-Seiberg duality}
+{\Large \bfseries Matching higher symmetries\\[.8em]
+across Intriligator-Seiberg duality}
 
@@
 We find that they depend on the parity of $n_c$ and $n_f$,
-on the global form of the gauge group, and the discrete theta angle.
+the global form of the gauge group, and the discrete theta angle.
 The contribution from the fermions plays a central role in our analysis.
 Furthermore, our conclusion applies to \Nequals1 supersymmetric cases as well, and
-we see that higher symmetries and anomalies match across the duality 
-$\so(2n_c)\leftrightarrow\so(2n_f-n_c+4)$ of Intriligator and Seiberg.
+we see that higher symmetries and anomalies match across the duality between
+$\so(2n_c)\leftrightarrow\so(2n_f-2n_c+4)$ of Intriligator and Seiberg.
 
@@
 \label{sec:introduction}
-Our understanding of the concept of symmetries in quantum field theories has been greatly improved in the last several years.
+Our understanding of the concept of symmetries in quantum field theories (QFT) has been greatly improved in the last several years.
 We now have the concept of $p$-form symmetries acting on $p$-dimensional objects \cite{Gaiotto:2014kfa}.
@@
 It is also realized more recently that 0-form symmetries and 1-form symmetries can not only coexist in a direct product but also mix in a more intricate manner.
-They can have mixed anomalies between them.
-They can also combine to form a symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.
+They can have mixed anomalies between them,
+or they can also combine to form a symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.
 
@@
 distinguished by the global form of the gauge group ($\Spin$ vs.~$\SO$)
-and by the choice of a discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
+and further by the choice of a discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
 This is when the theories are considered on spin manifolds.
-On more general manifolds a further distinction needs to be made \cite{Ang:2019txy}.
-For simplicity we only consider spin manifolds in this paper.
+On more general manifolds, a further distinction needs to be made \cite{Ang:2019txy}.
+For simplicity, we only consider spin manifolds in this paper.
 }.
@@
 Furthermore, these line operators are charged under corresponding $\bZ_2$ 1-form symmetries,
-which we can all electric, magnetic and dyonic 1-form symmetries.
+which we respectively call electric, magnetic and dyonic 1-form symmetries.
 
@@
 }
-We concentrate on the case when $N_c$ and $N_f$ are both even, $N_c=2n_c$ and $N_f=2n_f$.
+We concentrate on the case when $N_c$ and $N_f$ are both even: $N_c=2n_c$ and $N_f=2n_f$.
 
@@
 whose Postnikov class is specified by \begin{equation}
-\beta v_2 \in H^3(\SU(2n_f)/\bZ_2,\bZ_2),\label{postnikov}
-\end{equation}
-where $a_2$ is the generator of $H^2(\SU(2n_f)/\bZ_2,\bZ_2)=\bZ_2$ and $\beta$ is the Bockstein.
+\beta v_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2),\label{postnikov}
+\end{equation}
+where $v_2$ is the generator of $H^2(\SU(2n_f)/\bZ_2;\bZ_2)=\bZ_2$ and $\beta$ is the Bockstein.
 
@@
 we see that the $\bZ_2$ 1-form symmetry of the $\SO(2n_f)$ theory and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry remains a direct product but with a mixed anomaly given by \begin{equation}
-2\pi i \frac12 \int B\beta v_2.\label{mixed}
+2\pi i \cdot \frac12 \int B\beta v_2.\label{mixed}
 \end{equation}
@@
 there is an $\SO(2n_c)/\bZ_2$ bundle and an $\SU(2n_f)/\bZ_2$ bundle associated to it.
-Let us denote by $a_2,v_2\in H^2(X,\bZ_2)$ the obstruction classes controlling whether they lift to $\SO(2n_c)$ and $\SU(2n_f)$ respectively. 
+Let us denote by $a_2,v_2\in H^2(X;\bZ_2)$ the obstruction classes controlling whether they lift to $\SO(2n_c)$ and $\SU(2n_f)$ respectively. 
 Then we have $a_2=v_2$ for a $G$-bundle.
@@
 
-Now, without the flavor background,  the background $E\in H^2(X,\bZ_2)$ for the electric $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2\in H^2(X,\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2$, which controls whether it lifts to a $\Spin(2n_c)$ bundle.
+Now, without the flavor background,  the background $E\in H^2(X;\bZ_2)$ for the electric $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2\in H^2(X;\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2$, which controls whether it lifts to a $\Spin(2n_c)$ bundle.
 When the flavor background $v_2$ is nontrivial,
@@
 In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta a_2$, where $\beta$ is the Bockstein operation,
-since together they specify the obstruction class $x_2\in H^2(X,\bZ_4)$ 
+since together they specify the obstruction class $x_2\in H^2(X;\bZ_4)$ 
 controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
@@
 \label{group-extension}
-\end{equation} whose Postnikov class is $\beta v_2 \in H^3(B\SU(2n_f)/\bZ_2,\bZ_2)$.
+\end{equation} whose Postnikov class is $\beta v_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2)$.
 
@@
 
-The 't Hooft lines in the resulting $\SO(2)^{n_c}$ theory can be labeled by their magnetic charges $(m_1,\ldots,m_{n_c})\in \bZ^{n_c})$.
+The 't Hooft lines in the resulting $\SO(2)^{n_c}$ theory can be labeled by their magnetic charges $(m_1,\ldots,m_{n_c})\in \bZ^{n_c}$.
 The dynamical monopoles have the charges in the `adjoint class', which are
@@
 which agrees with the 1-form symmetry before the deformation.
-We now would like to study how this $\bZ_2$ is combined with the flavor/gauge center charge $\bZ_2$.
+We now would like to study how this $\bZ_2$ is combined with the flavor/gauge center $\bZ_2$ charge.
 
@@
 $
-We then have to determine $q_{n-1}$ and $q_{n_c}$.
+We then have to determine $q_{n_c-1}$ and $q_{n_c}$.
 
@@
 The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume $a_1>a_2>0$.
-The fermion is in the vector representation of $so(4)$.
+The fermion is in the vector representation of $SO(4)$.
 Under the monopole in $\su(2)_1$, it is a doublet coupled to an adjoint vev of size $a_1$ with bare mass $a_2$,
@@
 a doublet coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
- a zero mode if $|a|>|m|$ and 
- it has no zero mode if $|a|<|m|$.
+ a zero mode if $|a|>|\mu|$ and 
+ it has no zero mode if $|a|<|\mu|$.
 
@@
 In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
-In a quantum field theory, any symmetry comes with its (possibly trivial) 't Hooft anomaly.
-Here we determine the anomalies of these theories using the $\SL(2,\bZ_2)$ action on the set of quantum field theories (QFTs) with $\bZ_2$ 1-form symmetry.
+In a QFT, any symmetry comes with its (possibly trivial) 't Hooft anomaly.
+Here we determine the anomalies of these theories using the $\SL(2,\bZ_2)$ action on the set of QFTs with $\bZ_2$ 1-form symmetry.
 
@@
 We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
-where we suppress the dependence on $X$ in the notation and $E\in H^2(X,\bZ_2)$ is the background field for the 1-form symmetry.
-We then define $SQ$ and $TQ$ to be given by the formula \begin{equation}
+where we suppress the dependence on $X$ in the notation and $E\in H^2(X;\bZ_2)$ is the background field for the 1-form symmetry.
+We then define $SQ$ and $TQ$ to be QFTs with partition functions given by the formula \begin{equation}
 Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q{B},\qquad
@@
 Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
-More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T\SO(2n_c)_\pm$, respectively.
+More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
 Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
 Then we have the following chain of actions: \begin{equation}
+{\scriptstyle S} \ \rotatebox[]{-90}{$\circlearrowleft$}\hspace{2mm}
 T\Spin \stackrel{T}{\longleftrightarrow} 
@@
 T\SO_- \stackrel{T}{\longleftrightarrow} 
-\SO_- \stackrel{S}{\longleftrightarrow} .
+\SO_- \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
 \end{equation}
@@
 So far we have been considering the effect of $\SU(2n_f)/\bZ_2$ flavor symmetry,
-but the discussions in the last section shows that at a formal level only the background field $v_2 \in H^2(X,\bZ_2)$ matters, which controls the lift from $\SU(2n_f)/\bZ_2$ to $\SU(2n_f)$.
+but the discussions in the last section shows that at a formal level only the background field $v_2 \in H^2(X;\bZ_2)$ matters, which controls the lift from $\SU(2n_f)/\bZ_2$ to $\SU(2n_f)$.
 Let us regard $v_2$ as the background field for a flavor $\bZ_2$ 1-form symmetry.
@@
 and we perform the $\SL(2,\bZ_2)$ action  by picking a $\bZ_2$ subgroup.
-The symmetry and the anomaly of the resulting theory can be determined by a formal argument once the symmetry and the anomaly of the original theory 
-and the action of the anomaly-free subgroup to be gauged is given \cite{Tachikawa:2017gyf}.
+The symmetry and the anomaly of the resulting theory can be determined by a formal argument once those of the original theory 
+and the action of the anomaly-free subgroup to be gauged are given \cite{Tachikawa:2017gyf}.
 
 Let us work at the level of anomalies described at the level of cohomology, since we do not need to deal with anomalies more general than that.
-We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G,\U(1))$. 
-We pick a subgroup $H\subset G$ such that $\alpha$ trivializes in it, so that one can find $\mu \in C^d(H,\U(1))$ such that $\delta \mu = \alpha|_H$. 
+We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G;\U(1))$. 
+We pick a subgroup $H\subset G$ such that $\alpha$ trivializes in it, so that one can find $\mu \in C^d(H;\U(1))$ such that $\delta \mu = \alpha|_H$. 
 We then gauge $H$, using $\mu$ as the action.
-What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$
-Clearly, given $\beta\in C^d(G,\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\beta,\alpha-\delta\beta)$ should give the same result, since we merely added the countertem $\beta$ as the action.
+What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$.
+Clearly, given $\nu\in C^d(G;\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\nu,\alpha-\delta\nu)$ should give the same result, since we merely added the countertem $\nu$ as the action.
 This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
-by using $\beta$ to be an arbitrary extension of $\mu$ from $H$ to $G$.
+by using $\nu$ to be an arbitrary extension of $\mu$ from $H$ to $G$.
 This is convenient in discussing the $\SL(2,\bZ_2)$ action,
@@
 As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly for 4d spin QFTs with this symmetry is \begin{equation}
-\alpha=2\pi i \tfrac12  B\beta E  \label{anom}
-\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y,\bZ_2)$ are the background fields.
+\alpha=2\pi i \cdot \frac12  B\beta E  \label{anom}
+\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y;\bZ_2)$ are the background fields.
 Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivially zero,
 and then the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
-\mu = 2\pi i \tfrac12  \tfrac12\fP(E).\label{P}
+\mu = 2\pi i \cdot \frac14 \fP(E).\label{P}
 \end{equation}
@@
 As discussed in the Appendix~\ref{sec:nonclosedP}, with $\delta E=\beta a_2$,
-where $a_2\in H^2(X,\bZ_4/\bZ_2)$,
+where $a_2\in H^2(X;\bZ_4/\bZ_2)$,
 one finds \begin{equation}
-\alpha':=\delta \mu = 2\pi i \tfrac12 a_2 \beta_2 a_2.\label{anom'}
+\alpha':=\delta \mu = 2\pi i \cdot \frac12 a_2 \beta_2 a_2.\label{anom'}
 \end{equation}
@@
 \text{none} \stackrel{T}{\longleftrightarrow} 
-\text{none} \stackrel{S}{\longleftrightarrow} 
+\text{none} \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}
 \label{trivial-chain}.
@@
 \text{extended}\stackrel{T}{\longleftrightarrow} 
-\text{\Textended}\stackrel{S}{\longleftrightarrow}.
+\text{\Textended}\hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
 \label{nontrivial-chain}
@@
 \end{equation} when $n_c$ is even,
-where $w_2,v_2$ are the classes in $H^2(X,\bZ_2)$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
+where $w_2,v_2$ are the classes in $H^2(X;\bZ_2)$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
 and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively,
@@
 \alpha'=2\pi i \frac12 a_2 \beta_2 a_2
-\end{equation} where $a_2$ is the class in $H^2(X,\bZ_2)$ which is the mod-2 reduction of
-the class in $H^2(X,\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\bZ_4$.
+\end{equation} where $a_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
+the class in $H^2(X;\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\bZ_4$.
 We note that $\alpha'$ is exact, but as explained in the previous section, this still affects the gauging process.
@@
 \end{equation}
-where $\fP:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
+where $\fP:H^2(-;\bZ_4)\to H^4(-;\bZ_8)$ is the Pontryagin square,
 which is even mod 8 on a spin manifold.

### 2021-06-27 paper.tex
changed v2 <-> a2 (+ other minor changes) + organization added

@@
 They can have mixed anomalies between them,
-or they can also combine to form a symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.
-
-In this paper we study these issues in the case of 4d $\so(N_c)$ gauge theories with 
-$N_f$ flavors of fermion fields in vector representation.
+or they can also combine to form a \textit{higher} symmetry structure called 2-groups \cite{Cordova:2018cvg,Benini:2018reh}.
+
+In this paper, we study these issues in the case of 4d $\so(N_c)$ gauge theories with 
+$N_f$ flavors of fermion fields in the vector representation.
 Let us quickly recall the 0-form and 1-form symmetries these theories have.
@@
 such theories come in three versions, $\Spin$, $\SO_+$ and $\SO_-$,
-distinguished by the global form of the gauge group ($\Spin$ vs.~$\SO$)
+distinguished firstly by the global form of the gauge group ($\Spin$ vs.~$\SO$)
 and further by the choice of a discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
@@
 
-Take for example the $Spin(2n_c)$ gauge theory with $2n_f$ flavors,
-when $n_c$ is odd.
-Take two copies of  the Wilson line $W$ in the spinor representation. 
-They form a Wilson line in the vector representation.
-This can be screened by a dynamical fermion, which was why $W^2=1$ 
+Take for example the $\Spin(2n_c)$ gauge theory with $2n_f$ flavors.
+When $n_c$ is odd,
+two copies of the Wilson line $W$ in the spinor representation
+form a Wilson line in the vector representation.
+This can be screened by a dynamical fermion, and that was why $W^2=1$ 
 as far as the 1-form symmetry charge was concerned.
 Now let us recall that this dynamical fermion transforms nontrivially under $-1\in \SU(2n_f)$.
-Therefore, when we take the flavor symmetry into account, $W^2$ is still nontrivial.
-As we will recall below,  formally this means that the $\bZ_2$ 1-form symmetry extends the $\SU(2n_f)/\bZ_2$ 0-form symmetry in a nontrivial manner, forming a nontrivial 2-group  $H$\begin{equation}
+Therefore, when we further take the flavor symmetry into account, $W^2$ is still nontrivial.
+As we will recall below,  formally this means that the $\bZ_2$ 1-form symmetry extends the $\SU(2n_f)/\bZ_2$ 0-form symmetry in a nontrivial manner, forming a 2-group $H$\begin{equation}
 0\to \bZ_2[1] \to H\to \SU(2n_f)/\bZ_2\to 0,\label{2-group}
@@
 whose Postnikov class is specified by \begin{equation}
-\beta v_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2),\label{postnikov}
-\end{equation}
-where $v_2$ is the generator of $H^2(\SU(2n_f)/\bZ_2;\bZ_2)=\bZ_2$ and $\beta$ is the Bockstein.
+\beta a_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2),\label{postnikov}
+\end{equation}
+where $a_2$ is the generator of $H^2(B(\SU(2n_f)/\bZ_2);\bZ_2)=\bZ_2$~\cite{KonoMimura1974}
+and $\beta$ is the Bockstein homomorphism.
 
@@
 we see that the $\bZ_2$ 1-form symmetry of the $\SO(2n_f)$ theory and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry remains a direct product but with a mixed anomaly given by \begin{equation}
-2\pi i \cdot \frac12 \int B\beta v_2.\label{mixed}
+2\pi i \cdot \frac12 \int B\beta a_2.\label{mixed}
 \end{equation}
@@
 
-The rest of the paper is organized as follows ...
+The rest of the paper is organized as follows.
+In Sec.~\ref{sec:2-group},
+we determine exactly when the electric/magnetic/dyonic $\bZ_2$ 1-form symmetries
+and the $\SU(2n_f)/\bZ_2$ flavor 0-form symmetry are mixed nontrivially,
+by examining the charges of line operators in each theory.
+In Sec.~\ref{sec:sl2z},
+we exploit the $\SL(2,\bZ_2)$ actions on $\so(2n_f)$ QCDs to determine the 't Hooft anomalies they possess.
+Combining the results with those obtained in Sec.~\ref{sec:2-group},
+one can completely determine the structures of symmetries and anomalies of $\so(2n_f)$ QCDs,
+and can further confirm that they are indeed compatible with the Intriligator-Seiberg duality.
+Although the result itself is satisfactory, the analysis leading to it is somewhat ad-hoc, 
+so we partially complement it with the more direct computation of fermion anomalies in Sec.~\ref{sec:fermion}.
+Finally, the two appendices provide technical details of the mathematical facts used in the main part;
+in Appendix~\ref{sec:bordism}, we compute relevant bordism groups capturing the fermion anomalies associated to various symmetries;
+and in Appendix~\ref{sec:nonclosedP}, we describe some subtleties concerning the Pontrjagin square.
 
@@
 \label{sec:2-group}
-Let us first study whether the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ flavor symmetry form a nontrivial 2-group or not. 
+Let us first study whether the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry form a nontrivial 2-group or not. 
 This can be found rather physically by studying the line operators.
@@
 We start by discussing the $\Spin(2n_c)$ gauge theories. 
-We first recall that the center of $\Spin(2n_c)$ is $\bZ_2\times \bZ_2$ when $n_c$ is even and $\bZ_4$ when $n_c$ is odd.
+First, recall that the center of $\Spin(2n_c)$ is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $n_c$ is even or odd.
 This corresponds to the fact that the tensor square of a spinor representation contains the identity representation when $n_c$ is even while it contains the vector representation when $n_c$ is odd.
@@
 We now consider the Wilson line $W$ in the spinor representation in the $\Spin(2n_c)$ gauge theory with $2n_f$ fermions in the vector representation.
-When $n_c$ is even, $W^2$ contains the identity representation, and therefore we simply have a $\bZ_2$ 1-form symmetry independent of the $\su$ flavor symmetry, and there is nothing to see here.
+When $n_c$ is even, $W^2$ contains the identity representation, and therefore we simply have a $\bZ_2$ 1-form symmetry independent of the flavor symmetry, and there is nothing to see here.
 
@@
 0\to \underbrace{\bZ_2}_{\substack{\text{subgroup of}\\
-\text{rep.~of center of $\SU(2n_f)$}}}
+\text{rep.~of center of}\\
+\text{flavor $\SU(2n_f)$}}}
 \to \bZ_4 
-\to \underbrace{\bZ_2}_{\substack{\text{group of gauge Wilson lines }\\
+\to \underbrace{\bZ_2}_{\substack{\text{group of}\\\text{gauge Wilson lines }\\
 \text{up to screening}}} \to 0.
@@
 \end{equation}
-
 As the groups of charges of $\su(2n_f)$ 0-form symmetry and $\bZ_2$ 1-form symmetry are combined nontrivially, 
-the 0-form symmetry group and the 1-form symmetry group are also combined nontrivially.
-This can be seen most clearly by considering background fields for the symmetry groups.
-
-The fermion fields are in the vector of $\SO(2n_c)$ and in the fundamental of $\SU(2n_f)$, and therefore is a representation of $G=[\SO(2n_c)\times \SU(2n_f)]/\bZ_2$.
+the symmetry groups themselves are also combined nontrivially.
+This can be seen most clearly by considering their background fields.
+
+The fermion fields are simultaneously in the vector representation of $\SO(2n_c)$ and the fundamental representation of $\SU(2n_f)$,
+and therefore are in a representation of $G=[\SO(2n_c)\times \SU(2n_f)]/\bZ_2$.
 Given a $G$-bundle on a manifold $X$,
 there is an $\SO(2n_c)/\bZ_2$ bundle and an $\SU(2n_f)/\bZ_2$ bundle associated to it.
-Let us denote by $a_2,v_2\in H^2(X;\bZ_2)$ the obstruction classes controlling whether they lift to $\SO(2n_c)$ and $\SU(2n_f)$ respectively. 
-Then we have $a_2=v_2$ for a $G$-bundle.
+Let us denote by $v_2,a_2\in H^2(X;\bZ_2)$ the obstruction classes controlling whether they lift to $\SO(2n_c)$ and $\SU(2n_f)$ respectively. 
+Then we have $v_2=a_2$ for a $G$-bundle.
 The flavor Wilson line in the fundamental representation is charged under $-1\in \SU(2n_f)$ in the center,
-and $v_2$ can be considered as the background field for this $\bZ_2$ 1-form center symmetry.
-
-Now, without the flavor background,  the background $E\in H^2(X;\bZ_2)$ for the electric $\bZ_2$ one-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2\in H^2(X;\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2$, which controls whether it lifts to a $\Spin(2n_c)$ bundle.
-When the flavor background $v_2$ is nontrivial,
-the obstruction class $a_2$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$ is nontrivial.
-In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta a_2$, where $\beta$ is the Bockstein operation,
+and $a_2$ can be considered as the background field for this $\bZ_2$ 1-form center symmetry.
+
+Now, without the flavor background,  the background $E\in H^2(X;\bZ_2)$ for the electric $\bZ_2$ 1-form symmetry of the $\Spin(2n_c)$ theory sets the Stiefel-Whitney class $w_2\in H^2(X;\bZ_2)$ of the $\SO(2n_c)$ gauge bundle to be $E=w_2$, which controls whether it lifts to a $\Spin(2n_c)$ bundle.
+When the flavor background $a_2$ is nontrivial,
+the obstruction class $v_2$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$ is nontrivial.
+In this situation when $n_c$ is odd, $w_2$ can no longer be defined as a closed cochain; rather it satisfies $\delta w_2 = \beta v_2$, where $\beta$ is the Bockstein operation,
 since together they specify the obstruction class $x_2\in H^2(X;\bZ_4)$ 
 controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
-As $E=w_2$ and $a_2=v_2$, we conclude that the background fields satisfy \begin{equation}
-\delta E=\beta v_2.
+As $E=w_2$ and $v_2=a_2$, we conclude that the background field satisfies \begin{equation}
+\delta E=\beta a_2.
 \label{ba}
@@
 \label{group-extension}
-\end{equation} whose Postnikov class is $\beta v_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2)$.
+\end{equation} with the Postnikov class being $\beta a_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2)$.
 
@@
 is equivalent to having a nontrivial 2-group extension \eqref{group-extension} 
-whose background fields satisfy \eqref{ba}.
+whose background field satisfies \eqref{ba}.
 Therefore, to find a nontrivial 2-group extension, we can simply study the group of charges of line operators,
@@
 
-We would like to study how the magnetic $\bZ_2$ 1-form symmetry of the $\SO(2n_c)_+$ theory is combined with the $\su(n_f)$ flavor symmetry.
-According to the discussions in the previous subsection, 
-we consider what happens if we take two copies of the 't Hooft line operator $H$ and fuse them.
-At the very naive level, $H^2$ can be screened by a dynamical monopole,
-but dynamical monopoles can receive flavor and gauge center charges from the fermion zero modes.
-To study these issues, it is useful to deform the theories to make them simpler.
-
-For this purpose, we perform the following steps:
+We would like to study how the magnetic $\bZ_2$ 1-form symmetry of the $\SO(2n_c)_+$ theory is combined with the $\su(2n_f)$ flavor symmetry.
+In accord with the discussions in the previous subsection, 
+we consider what happens when we take two copies of the 't Hooft line operator $H$ and fuse them.
+At the very naive level, $H^2$ can be screened by dynamical monopoles,
+but dynamical monopoles can receive flavor/gauge center charges from the fermion zero modes.
+To study these issues, it is useful to deform the theory and make it simpler
+by performing the following steps:
 \begin{itemize}
-\item We reduce the flavor symmetry from $\su(2n_f)$ to $\usp(2n_f)$. 
+\item Reduce the flavor symmetry from $\su(2n_f)$ to $\usp(2n_f)$. 
 The fundamental representation still transforms nontrivially under $-1\in \USp(2n_f)$, which is enough for our purposes.
-\item We add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +cc$, where $J_{[ij]}$ is the constant matrix for the $\usp(2n_f)$ part.
-\item We give a vev to $\Phi_{ab}$ to break $\SO(2n_c)$ to $\SO(2)^{n_c}$.
+\item Add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +c.c.$, where $J_{[ij]}$ is the constant matrix for the $\usp(2n_f)$ part.
+\item Give a vacuum expectation value (vev) to $\Phi_{ab}$ to break $\SO(2n_c)$ to $\SO(2)^{n_c}$.
 \end{itemize}
@@
 in the root lattice $\Lambda$ of $\SO(2n_c)$. 
-
-The group of the magnetic charges of 't Hooft lines up to screening by the dynamical monopoles is then \begin{equation}
+Then, the group of the magnetic charges of 't Hooft lines up to screening by the dynamical monopoles is \begin{equation}
 \bZ^{n_c}/\Lambda = \bZ_2,
@@
 Let us say we chose the standard $\phi$ such that the simple roots are $(1,-1,\ldots,0)$,
-$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)$,
+$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)\in \bZ^{n_c}$,
 which we call simple dynamical monopoles.
-
-We now consider the group $\bZ^{n_c}\times \bZ_2$ which combine the magnetic charges $\bZ^{n_c}$ and the flavor/gauge center charge $\bZ_2$.
+Now, consider the group $\bZ^{n_c}\times \bZ_2$ which combines the magnetic charges in $\bZ^{n_c}$ and the flavor/gauge center charge $q \in \bZ_2$.
 What we are after is the quotient of $\bZ^{n_c}\times \bZ_2$ 
@@
 
-Let us determine this quotient.
-We do not have to determine $q_1$ to $q_{n_c-1}$. 
-We simply use them to rewrite any charge vector $
+To determine this quotient,
+we do not have to determine the all $q_i$'s; 
+we simply use $q_{i=1,\ldots, n_c-2}$ to rewrite any charge vector $
 (m_1,\ldots, m_{n_c-2}, m_{n_c-1},m_{n_c}; q)
@@
 $
-We then have to determine $q_{n_c-1}$ and $q_{n_c}$.
-
-This reduces the study to the case of $\so(4)\simeq \su(2)_1 \times \su(2)_2$.
-The monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $\su(2)$'s.
-The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume $a_1>a_2>0$.
-The fermion is in the vector representation of $SO(4)$.
+Then, only $q_{n_c-1}$ and $q_{n_c}$ need to be determined.
+This reduces the study to the case of $n_c=2$ and $\so(4)\simeq \su(2)_1 \times \su(2)_2$,
+where the monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $\su(2)$'s.
+The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume to be $a_1>a_2>0$.
+Here, the fermion is in the vector representation of $\so(4)$.
 Under the monopole in $\su(2)_1$, it is a doublet coupled to an adjoint vev of size $a_1$ with bare mass $a_2$,
@@
 a zero mode if $|a|>|\mu|$ and 
- it has no zero mode if $|a|<|\mu|$.
-
-With our assumption $a_1>a_2>0$, this means that the monopole in $\su(2)_1$ has a zero mode while the one in $\su(2)_2$ does not have any.
-In our original basis, this means that the monopole with $(0,\ldots,1,-1;q_{n_c-1})$ does not have any zero modes and $q_{n_c-1}=0$,
-while the one with $(0,\ldots,1,+1;q_{n_c})$  (which is in $\su(2)_1$) has two zero modes per flavor.
-
-The one-form symmetry group is obtained by dividing $\bZ^2\times \bZ_2$ by the subgroup generated by $(1,-1;0)$ and $(1,+1;q_{n_c})$.
+has no zero modes if $|a|<|\mu|$.
+With our assumption $a_1>a_2>0$, this means that the monopole in $\su(2)_1$ has a zero mode, while the monopole in $\su(2)_2$ does not.
+In our original basis, this means that the monopole with $(0,\ldots,1,-1;q_{n_c-1})$ does not produce any zero modes and $q_{n_c-1}=0$,
+while the monopole with $(0,\ldots,1,+1;q_{n_c})$  has two zero modes per flavor.
+The 1-form symmetry group is obtained by dividing $\bZ^2\times \bZ_2$ by the subgroup generated by $(1,-1;0)$ and $(1,+1;q_{n_c})$.
 This is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $q_{n_c}$ is $0$ or $1$.
@@
 Let us determine $q_{n_c}$.
-We saw two zero modes per flavor; 
+We saw that there are two zero modes per flavor; 
 this means that there are fermionic zero modes transforming in \begin{equation}
 V_{2} \otimes R_{2n_f} 
-\end{equation} where $V_2$ is the doublet of $\su(2)_2$ (which is actually broken to $\u(1)$ but keeping $\su(2)_2$ representation is useful in organizing the answer), 
+\end{equation} where $V_2$ is the doublet of $\su(2)_2$\footnote{
+	It is actually broken to $\u(1)$, but keeping $\su(2)_2$ representation is useful in organizing the answer.
+}, and
 $R_{2n_f}$ is the fundamental of $\usp(2n_f)$,
-and we need to impose the reality condition using the pseudoreality of both factors,
+and we need to impose the reality condition using the pseudo-reality of both factors,
 so that there are $4n_f$ Majorana fermion in total.
 
-To determine the flavor/gauge center charge of the monopole,
+To determine the flavor/gauge center charge $q_{n_c}$ of the monopole,
 it suffices to consider the case $n_f=1$;
@@
 Quantizing them, we find the monopoles in \begin{equation}
-V_2 \otimes \mathbf{1} \oplus \mathbf{1}\otimes R_2.
-\end{equation}
-It has the `vector' charge under $\usp(2)$ flavor symmetry or is a doublet under $\su(2)_2$,
+(V_2 \otimes \mathbf{1}) \oplus (\mathbf{1}\otimes R_2).
+\end{equation}
+It has the `vector' charge under $\usp(2)\simeq\su(2)$ flavor symmetry or is a doublet under $\su(2)_2$,
 which corresponds to the `vector' charge under $\so(4)$ gauge symmetry.
@@
 The analysis of the $\SO(2n_c)_-$ theory is largely the same;
-the only difference is that the discrete theta angle gives an additional gauge center charge to the simple dynamical monopole with the magnetic charge $(0,0,\ldots,1,1)$, so that $q_{n_c}=n_f+n_c$ mod 2.
+the only difference is that the discrete theta angle gives an additional gauge center charge to the simple dynamical monopole with the magnetic charge $(0,0,\ldots,1,+1)$, so that $q_{n_c}=n_f+n_c$ mod 2.
 Therefore, we conclude the following:
@@
 \centering
-\begin{tabular}{r@{\vphantom{$\Bigm|$}\,}l|ccc}
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{rl|ccc}
 $(n_c,$&$n_f)$ & $\Spin$ & $\SO_+$ & $\SO_-$\\
@@
 We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
-where we suppress the dependence on $X$ in the notation and $E\in H^2(X;\bZ_2)$ is the background field for the 1-form symmetry.
+where we suppress the dependence on $X$ in the notation and $E\in H^2(X;\bZ_2)$ is the background field for the $\bZ_2$ 1-form symmetry.
 We then define $SQ$ and $TQ$ to be QFTs with partition functions given by the formula \begin{equation}
-Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q{B},\qquad
+Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q[E],\qquad
 Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \fP(E)} Z_Q[E].
@@
 {\scriptstyle S} \ \rotatebox[]{-90}{$\circlearrowleft$}\hspace{2mm}
-T\Spin \stackrel{T}{\longleftrightarrow} 
+T(\Spin) \stackrel{T}{\longleftrightarrow} 
 \Spin \stackrel{S}{\longleftrightarrow} 
 \SO_+ \stackrel{T}{\longleftrightarrow} 
-T\SO_+ \stackrel{S}{\longleftrightarrow} 
-T\SO_- \stackrel{T}{\longleftrightarrow} 
+T(\SO_+) \stackrel{S}{\longleftrightarrow} 
+T(\SO_-) \stackrel{T}{\longleftrightarrow} 
 \SO_- \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
@@
 So far we have been considering the effect of $\SU(2n_f)/\bZ_2$ flavor symmetry,
-but the discussions in the last section shows that at a formal level only the background field $v_2 \in H^2(X;\bZ_2)$ matters, which controls the lift from $\SU(2n_f)/\bZ_2$ to $\SU(2n_f)$.
-Let us regard $v_2$ as the background field for a flavor $\bZ_2$ 1-form symmetry.
+but the discussions in the last section shows that, at a formal level, only the background field $a_2 \in H^2(X;\bZ_2)$ matters, which controls the lift from $\SU(2n_f)/\bZ_2$ to $\SU(2n_f)$.
+Let us regard $a_2$ as the background field for a flavor $\bZ_2$ 1-form symmetry.
 
@@
 What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$.
-Clearly, given $\nu\in C^d(G;\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\nu,\alpha-\delta\nu)$ should give the same result, since we merely added the countertem $\nu$ as the action.
+Clearly, given $\nu\in C^d(G;\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\nu|_H,\alpha-\delta\nu)$ should give the same result, since we merely added the counterterm $\nu|_H$ as the action.
 This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
-by using $\nu$ to be an arbitrary extension of $\mu$ from $H$ to $G$.
+by taking $\nu$ to be an arbitrary lift of $\mu$ from $H$ to $G$.
 This is convenient in discussing the $\SL(2,\bZ_2)$ action,
@@
 
-Now, what are the possible choices of $(\mu,\alpha)$ or $(0,\alpha')$ we need to discuss?
+Now, what are the possible choices of $(\mu,\alpha)\sim(0,\alpha')$ we need to discuss?
 Let us first consider $\bZ_2\times \bZ_2$ 1-form symmetry.
@@
 \alpha=2\pi i \cdot \frac12  B\beta E  \label{anom}
-\end{equation} where $Y$ is the 5d spin manifold and $B,E\in H^2(Y;\bZ_2)$ are the background fields.
-Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivially zero,
-and then the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
+\end{equation} where $B,E\in H^2(Y;\bZ_2)$ are the background fields on the bulk 5d spin manifold $Y$.
+Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivial i.e. $\alpha|_{H=\bZ_2} = 0$,
+and thus the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
 \mu = 2\pi i \cdot \frac14 \fP(E).\label{P}
 \end{equation}
-This $\mu$ can be extended from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ subgroup as a closed cochain.
+This $\mu$ can be lifted from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ group as a closed cochain.
 Therefore, we only have to consider pairs $(0,0)$ and $(0,\alpha)$.
@@
 Next, we consider $\bZ_4$ 1-form symmetry.
-Again in the Appendix~\ref{sec:bordism}, we show that there is no anomaly for $\bZ_4$ 1-form symmetry.
+Again in the Appendix~\ref{sec:bordism}, we show that this time there is no anomaly for $\bZ_4$ 1-form symmetry.
 Therefore we can pick $\alpha=0$. Then the possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
-One difference here is that the discrete theta angle \eqref{P} cannot be extended as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
+One difference here is that the discrete theta angle \eqref{P} cannot be lifted as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
 As discussed in the Appendix~\ref{sec:nonclosedP}, with $\delta E=\beta a_2$,
@@
 The case  `extended' was analyzed in \cite{Tachikawa:2017gyf},
-the resulting theory has $\bZ_2\times \bZ_2$ 1-form symmetry with the anomaly \eqref{anom}, 
+and the resulting theory has $\bZ_2\times \bZ_2$ 1-form symmetry with the anomaly \eqref{anom}, 
 which we decided to call `anomaly'.
@@
  \begin{equation}
-\exp\left(2\pi i\int_X ( \frac14 \fP(E) +\frac12 B E)\right)
+\exp\left[2\pi i\int_X \left( \frac14 \fP(E) +\frac12 B E\right)\right]
 \label{boo}
@@
 When $\bZ_2$ to be gauged is the $\bZ_2$ subgroup of a $\bZ_4$ symmetry,
-$E$ is not necessarily closed, but satisfies rather the relation \begin{equation}
-\delta E = \beta v_2
-\end{equation}
-where $v_2$ is the background field for the quotient $\bZ_4/\bZ_2$ 1-form symmetry.
+$E$ is not necessarily closed, but rather satisfies the relation \begin{equation}
+\delta E = \beta a_2
+\end{equation}
+where $a_2$ is the background field for the quotient $\bZ_4/\bZ_2$ 1-form symmetry.
 Then the second term in \eqref{boo} is not closed, 
@@
 To make  the coupling \eqref{boo}  well-defined, we consider adding a background term to \eqref{boo} so that we have \begin{equation}
-\exp\left(2\pi i\int_X ( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) )\right)
+\exp\left[2\pi i\int_X \left( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) \right)\right]
 = 
-\exp \left(2\pi i \frac14 \int_X \fP(E+B)\right) .
-\end{equation}
-This is perfectly well-defined if the newly-introduced background field $B$  also satisfies \begin{equation}
-\delta B=\beta v_2.
+\exp \left[2\pi i \int_X \frac14 \fP(E+B)\right] .
+\end{equation}
+This is perfectly well-defined and has no problem at all with the lifting,
+if the newly-introduced background field $B$  also satisfies \begin{equation}
+\delta B=\beta a_2.
 \end{equation}
@@
 
-Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
+Combined, the preceding arguments allow us to see the chain of actions \begin{equation}
 \text{\Textended} \stackrel{T}{\longleftrightarrow} 
@@
 \begin{array}{r@{\,}l|cccccc}
-(n_c,&n_f)  & T\Spin & \Spin & \SO_+ & T\SO_+& T\SO_- & \SO_- \\
+(n_c,&n_f)  & T(\Spin) & \Spin & \SO_+ & T(\SO_+) & T(\SO_-) & \SO_- \\
 \hline
@@
 we see that the anomaly is automatically determined and 
-we obtain the result already presented in Table~\ref{table:main}.
-More precisely, we should better distinguish $\Spin(2n_c)$ and $T\Spin$, etc.,
+we obtain the result which was already presented in Table~\ref{table:main}.
+More precisely, we should better distinguish $\Spin$ and $T(\Spin)$ etc.,
 and we find the assignment given in Table~\ref{table:refined}.
@@
 \begin{equation}
+\renewcommand{\arraystretch}{1.1}
 \begin{array}{ccc}
@@
 \section{Fermion contribution to anomalies}
+\label{sec:fermion}
 So far, we first determined the 2-group structure in Sec.~\ref{sec:2-group} by studying the charges of line operators,
@@
 while it is $\alpha$ when $(n_c,n_f)$ is (odd,even) and $\alpha'$ when (odd,odd).
-Since the 1-form symmetry background in the $\Spin$ theory is simply the class $w_2$ of the $\SO(2n_c)$ gauge bundle, 
-these anomalies should simply come from the anomalies of fermions under $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
-Here we use $\USp(2n_f)$ instead of $\SU(2n_f)$, because under the latter we also have perturbative anomalies, which could potentially complicate the analysis.
-
-More explicitly, for $n_c$ even, the anomaly should be given by  \begin{equation}
-\alpha= 2\pi i \frac12 w_2 \beta v_2
-\end{equation} when $n_c$ is even,
-where $w_2,v_2$ are the classes in $H^2(X;\bZ_2)$ controlling the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
-and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively,
-and for $n_c$ odd, the anomaly cochain should be given by 
- \begin{equation}
-\alpha'=2\pi i \frac12 a_2 \beta_2 a_2
-\end{equation} where $a_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
-the class in $H^2(X;\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\bZ_4$.
+Since the 1-form symmetry background in the $\Spin$ theory is simply the Stiefel-Whitney class $w_2$ of the $\SO(2n_c)$ gauge bundle, 
+these anomalies should simply come from the anomalies of fermions charged under $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
+Here we use $\USp(2n_f)$ instead of $\SU(2n_f)$, because under the latter we also have perturbative anomalies, which might complicate the analysis.
+
+For even $n_c$, the anomaly should be given by  \begin{equation}
+\alpha= 2\pi i \cdot \frac12 w_2 \beta a_2
+\end{equation}
+where $w_2,a_2\in H^2(X;\bZ_2)$ controls the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
+and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively.
+For odd $n_c$, the anomaly cochain should be given by 
+ \begin{equation}
+\alpha'=2\pi i \cdot \frac12 v_2 \beta_2 v_2
+\end{equation} where $v_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
+the class $x_2 \in H^2(X;\bZ_4)$ controlling the lift from $\SO(2n_c)/\bZ_2=\Spin(2n_c)/\bZ_4$ to $\Spin(2n_c)$.
 We note that $\alpha'$ is exact, but as explained in the previous section, this still affects the gauging process.
@@
 We will proceed as follows. 
-We add scalar fields, adjoint under $\USp(2n_f)$ in the system, and break it a subgroup.
+Starting from the theory where the fermions are charged under $\SO(2n_c)\times \USp(2n_f)$,
+we add scalar fields which are adjoint under $\USp(2n_f)$ in the system, and break it down to a subgroup.
 We then determine the effective interaction induced by the fermion zero modes.
-The next step is to see what happens when the symmetry group is further changed from $\SO(2n_c)\times \USp(2n_f)$ to its $\bZ_2$ quotient.
-We will see that the effective interaction will have the required anomalies.
+The next step is to see what happens when the symmetry group is changed from $\SO(2n_c)\times \USp(2n_f)$ to its $\bZ_2$ quotient;
+we will see that the effective interaction will have the required anomalies.
 
@@
 because even the integral cohomology of the group in question is hard to obtain.
-In only a couple of cases we can say more, as we comment along the way.
+Only in a couple of cases we can say more, as we comment along the way.
 
 \subsection{Effective interaction}
-We break $\USp(2n_f)$ down to $\U(n_f)$, using a scalar field,
-such that the fundamental representation of $\USp(2n_f)$ splits to the fundamental plus the antifundamental of $\U(n_f)$.
-The monopole charge is given by the first Chern class $c_1$ of the low-energy $\U(n_f)$.
+We break $\USp(2n_f)$ down to $\U(n_f)$ using a scalar field,
+such that the fundamental representation of $\USp(2n_f)$ splits to the fundamental plus the anti-fundamental representation of $\U(n_f)$.
+The monopole charge is given by the first Chern class $c_1$ of the low-energy $\U(n_f)$ flavor symmetry.
 
@@
 This means that there is an effective interaction \begin{equation}
-2\pi i \frac12 \int_X w_2 c_1
-\end{equation} where $w_2$ is the Stiefel-Whitney class of the $\SO(2n_c)$ bundle
-and $c_1$ is the first Chern class of $\U(n_f)$.
+2\pi i \cdot \frac12 \int_X w_2 c_1.
+\end{equation} %where $w_2$ is the Stiefel-Whitney class of the $\SO(2n_c)$ bundle
+%and $c_1$ is the first Chern class of $\U(n_f)$.
 
@@
 $\SO(2n_c)\times \USp(2n_f)$ to $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
-Note that $\pi_1(U(n_f)/\bZ_2)$ is $\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
-
-Furthermore, when $n_f$ is even, $c_1(\U(n_f)) = c_1(\U(n_f)/\bZ_2)$ and $v_2(\U(n_f)/\bZ_2)=v_2(\USp(2n_f))$.
-When $n_f$ is odd, $c_1(\U(n_f)/\bZ_2)=2 c_1(\U(n_f))$ when the latter is well-defined and $v_2(\U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(\U(n_f)/\bZ_2)$.
+Note that $\pi_1(U(n_f)/\bZ_2)=\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
+
+Furthermore, when $n_f$ is even, $c_1(\U(n_f)) = c_1(\U(n_f)/\bZ_2)$ and $a_2(\U(n_f)/\bZ_2)=a_2(\USp(2n_f))$.
+When $n_f$ is odd, $c_1(\U(n_f)/\bZ_2)=2 c_1(\U(n_f))$ when the latter is well-defined and $a_2(\U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(\U(n_f)/\bZ_2)$.
 We now compute the anomaly cochains in the four cases separately:
 \paragraph{$(n_c,n_f)$=(even,even):}
-$w_2(\SO(2n_c))$ and $c_1(\U(n_f))$ can be generalized without problem,
+$w_2(\SO(2n_c))$ and $c_1(\U(n_f))$ can be generalized without any problem,
 and therefore \begin{equation}
-\delta(\frac12 w_2(\SO(2n_c)) c_1(\U(n_f))) = 0.
+\delta\left(\frac12 w_2(\SO(2n_c)) c_1(\U(n_f))\right) = 0.
 \end{equation}
@@
 \paragraph{$(n_c,n_f)$=(odd,even):}
-$w_2(\SO(2n_c))$ needs to be upgraded to a $\bZ_4$-valued cochain $a_2(\SO(2n_c)/\bZ_2)$.
+$w_2(\SO(2n_c))$ needs to be upgraded to a $\bZ_4$-valued cochain $x_2(\SO(2n_c)/\bZ_2)$.
 The original interaction is then \begin{equation}
-\frac14 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f))
+\frac14 x_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f))
 \end{equation}
 which is closed without problem,
-and therefore its $\delta$ is zero.
+and therefore taking $\delta$ results in zero.
 
@@
 \frac14 w_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 
-\end{equation} whose $\delta$ is \begin{align}
-\delta(\frac14 w_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) )
-&= \frac12 (\frac12\delta w_2(\SO(2n_c)) c_1(\U(n_f)/\bZ_2) ) \\
-&= \frac12 (\beta w_2(\SO(2n_c)))c_1(\U(n_f)/\bZ_2) 
+\end{equation} and \begin{align}
+\delta\left(\frac14 w_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) \right)
+&= \frac12 \left(\frac12\delta w_2(\SO(2n_c)) c_1(\U(n_f)/\bZ_2) \right) \\
+&= \frac12 \Big(\beta w_2(\SO(2n_c))\Big)c_1(\U(n_f)/\bZ_2) 
 \end{align}
-which is the pull-back of the anomaly cochain
-\begin{equation}
- \frac12 (\beta w_2(\SO(2n_c)))v_2(\USp(2n_f)/\bZ_2). 
+which is a pull-back of the anomaly cochain
+\begin{equation}
+ \frac12 \Big(\beta w_2(\SO(2n_c))\Big)a_2(\USp(2n_f)/\bZ_2). 
 \end{equation}
@@
 Now we make the replacement on both sides and the effective interaction is \begin{equation}
-\frac18 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 
-\end{equation}
-whose $\delta$ is \begin{align}
-\delta(\frac18 a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) )
-&= \frac12 (\frac14\delta a_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) ) \\
-&= \frac12 (\beta_2 a_2(\SO(2n_c)/\bZ_2))c_1(\U(n_f)/\bZ_2) 
+\frac18 x_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 
+\end{equation}
+and \begin{align}
+\delta\left(\frac18 x_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) \right)
+&= \frac12 \left(\frac14\delta v_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) \right) \\
+&= \frac12 \Big(\beta_2 v_2(\SO(2n_c)/\bZ_2)\Big)c_1(\U(n_f)/\bZ_2) 
 \end{align}
 which is the pull-back of \begin{equation}
- \frac12 (\beta_2 a_2(\SO(2n_c)))v_2(\USp(2n_f)).
+ \frac12 \Big(\beta_2 v_2(\SO(2n_c))\Big)a_2(\USp(2n_f)).
 \end{equation}
 We now recall that the symmetry we are considering now is $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$,
-and therefore there is a single degree-2 obstruction cochain which equals both $a_2$ and $v_2$,
+and therefore there is a single degree-2 obstruction cochain which equals both $v_2$ and $a_2$,
 and therefore the anomaly cochain is \begin{equation}
- \frac12 (\beta_2 a_2(\SO(2n_c)))a_2(\USp(2n_f)).
+ \frac12 v_2\beta_2 v_2.
 \end{equation}
 This is what we wanted to show.
-Recall that this anomaly cochain is exact as we repeatedly mentioned.
+Recall that this anomaly cochain is exact as we have repeatedly mentioned.
 This is consistent with our computation of the bordism group in Appendix~\ref{sec:so(2odd)},
@@
 		\hline
-		\text{generator} \,(\bZ_2) & 1 & - & a_2 & y'(1) & (a_2)^2 & y'(2) & (a_2)^3 & \cdots\\
+		\text{generator} \,(\bZ_2) & 1 & - & v_2 & y'(1) & (v_2)^2 & y'(2) & (v_2)^3 & \cdots\\
 		&&&&&&& y'(1)^2\\
@@
 	\begin{array}{ccl}
-		\beta_2 a_2 & = & y'(1)\\
+		\beta_2 v_2 & = & y'(1)\\
 		Sq^2 y'(1) & = & y'(2)\\
@@
 	\begin{array}{ccccc}
-		Sq^2 a_2 & = & (a_2)^2
+		Sq^2 v_2 & = & (v_2)^2
 	\end{array}
@@
 \end{equation*}
-where $v_2(c)=a_2\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
+where $v_2(c)\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
 %\begin{equation*}
@@
 The long exact sequence of cochain groups implies that $2\widetilde w_2(c)$ can be replaced by
-$\widetilde v_2(c) = \widetilde a_2$, which is a cocycle mod 4.
+$\widetilde v_2(c)$, which is a cocycle mod 4.
 Then the term of interest is
 \begin{equation*}
-	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\widetilde a_2 \cup \widetilde a_2.
+	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\widetilde v_2 \cup \widetilde v_2.
 \end{equation*}
@@
 	=
-	\dfrac{1}{2}a_2 \beta_2 a_2.
+	\dfrac{1}{2}v_2 \beta_2 v_2.
 \end{equation*}

### 2021-07-01 paper.tex
duality chains modified
Yunqin's corrections

@@
 Then we have the following chain of actions: \begin{equation}
-{\scriptstyle S} \ \rotatebox[]{-90}{$\circlearrowleft$}\hspace{2mm}
+\begin{tikzpicture}
+	\node at (0,0) {$
 		T(\Spin) \stackrel{T}{\longleftrightarrow} 
@@
 		T(\SO_-) \stackrel{T}{\longleftrightarrow} 
-\SO_- \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
+		\SO_-.
+	$};
+	\draw[->] (-5,-1) -- (-5,-0.5);
+	\draw[->] (5.4,-1) -- (5.4,-0.5);
+	\draw (-5,-1) -- node[above] {\scriptsize $S$} (5.4,-1);
+\end{tikzpicture}
 \end{equation}
@@
 The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
+\begin{tikzpicture}
+	\node at (0,0) {$
 		\text{none} \stackrel{T}{\longleftrightarrow} 
@@
 		\text{none} \stackrel{T}{\longleftrightarrow} 
-\text{none} \hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}
-\label{trivial-chain}.
+		\text{none}.
+	$};
+	\draw[->] (-4.6,-1) -- (-4.6,-0.5);
+	\draw[->] (4.5,-1) -- (4.5,-0.5);
+	\draw (-4.6,-1) -- node[above] {\scriptsize $S$} (4.5,-1);
+\end{tikzpicture}
+\label{trivial-chain}
 \end{equation}
@@
 Combined, the preceding arguments allow us to see the chain of actions \begin{equation}
+\begin{tikzpicture}
+	\node at (0,0) {$
 		\text{\Textended} \stackrel{T}{\longleftrightarrow} 
@@
 		\text{extended}\stackrel{T}{\longleftrightarrow} 
-\text{\Textended}\hspace{1mm}\rotatebox[]{90}{$\circlearrowleft$} \ {\scriptstyle S}.
+		\text{\Textended}.
+	$};
+	\draw[->] (-6.5,-1) -- (-6.5,-0.5);
+	\draw[->] (6.3,-1) -- (6.3,-0.5);
+	\draw (-6.5,-1) -- node[above] {\scriptsize $S$} (6.3,-1);
+\end{tikzpicture}
 \label{nontrivial-chain}
@@
 \end{equation}
-where $w_2,a_2\in H^2(X;\bZ_2)$ controls the lift from $\SO(2n_c)/\bZ_2$ to $\SO(2n_c)$
+where $w_2,a_2\in H^2(X;\bZ_2)$ controls the lift from $\SO(2n_c)$ to $\Spin(2n_c)$
 and from $\USp(2n_f)/\bZ_2$ to $\USp(2n_f)$, respectively.

### 2021-07-01 paper.tex
edits on Sec.1

@@
 we see that higher symmetries and anomalies match across the duality between
-$\so(2n_c)\leftrightarrow\so(2n_f-2n_c+4)$ of Intriligator and Seiberg.
+$\so(2n_c)\leftrightarrow\so(2n_f-2n_c+4)$, originally found by Intriligator and Seiberg.
 
@@
 We now have the concept of $p$-form symmetries acting on $p$-dimensional objects \cite{Gaiotto:2014kfa}.
-This concept  gives a unifying point of view to both
+This concept  gives a point of view which unifies both
 ordinary symmetries acting on point operators for $p=0$
@@
 distinguished firstly by the global form of the gauge group ($\Spin$ vs.~$\SO$)
-and further by the choice of a discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
+and further by the choice of the discrete theta angle ($\SO_+$ vs.~$\SO_-$) \cite{Aharony:2013hda}\footnote{%
 This is when the theories are considered on spin manifolds.
-On more general manifolds, a further distinction needs to be made \cite{Ang:2019txy}.
+For non-spin manifolds, a further distinction needs to be made \cite{Ang:2019txy}.
 For simplicity, we only consider spin manifolds in this paper.
@@
 We concentrate on the case when $N_c$ and $N_f$ are both even: $N_c=2n_c$ and $N_f=2n_f$.
-
+We introduce three possible behaviors, which we call `extension', `anomaly' and `none'.
+
+\paragraph{The `extension':} 
 Take for example the $\Spin(2n_c)$ gauge theory with $2n_f$ flavors.
@@
 form a Wilson line in the vector representation.
-This can be screened by a dynamical fermion, and that was why $W^2=1$ 
+This can be screened by a dynamical fermion, which was why $W^2=1$ 
 as far as the 1-form symmetry charge was concerned.
@@
 Therefore, when we further take the flavor symmetry into account, $W^2$ is still nontrivial.
-As we will recall below,  formally this means that the $\bZ_2$ 1-form symmetry extends the $\SU(2n_f)/\bZ_2$ 0-form symmetry in a nontrivial manner, forming a 2-group $H$\begin{equation}
+As we will detail in this paper,  this means that the $\bZ_2$ 1-form symmetry extends the $\SU(2n_f)/\bZ_2$ 0-form symmetry in a nontrivial manner, forming a 2-group $H$\begin{equation}
 0\to \bZ_2[1] \to H\to \SU(2n_f)/\bZ_2\to 0,\label{2-group}
 \end{equation}
-whose Postnikov class is specified by \begin{equation}
+whose extension class is specified by \begin{equation}
 \beta a_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2),\label{postnikov}
@@
 
-The $\SO_+$ gauge theory is then obtained by gauging the $\bZ_2$ 1-form symmetry \cite{Kapustin:2014gua}.
+\paragraph{The `anomaly':} 
+The $\SO_+$ gauge theory is obtained by gauging the $\bZ_2$ 1-form symmetry of the $\Spin$ gauge theory \cite{Kapustin:2014gua}.
 The presence of the fermions significantly complicates the analysis.
@@
 `anomaly' implies that they remain a direct product but with mixed anomaly of the form \eqref{mixed};
-and `extension' means that they combine into a 2-group given by \eqref{2-group} with the Postnikov class \eqref{postnikov}.
+and `extension' means that they combine into a 2-group given by \eqref{2-group} with the extension class \eqref{postnikov}.
 
@@
 \centering
-\begin{tabular}{r@{\vphantom{$\Bigm|$}\,}l|ccc}
+\begin{tabular}{r@{\,}l|ccc}
 $(n_c,$&$n_f)$ & $\Spin$ & $\SO_+$ & $\SO_-$\\
 \hline
+\vphantom{$\Bigm($}
 (even,&even) & no\tikzmark{A}ne & no\tikzmark{B}ne & no\tikzmark{C}ne \\
+\vphantom{$\Bigm($}
 (odd,&even) & exte\tikzmark{P}nsion & ano\tikzmark{Q}maly & exte\tikzmark{R}nsion \\
+\vphantom{$\Bigm($}
 (even,&odd) & ano\tikzmark{S}maly & exte\tikzmark{T}nsion & exte\tikzmark{U}nsion \\
+\vphantom{$\Bigm($}
 (odd,&odd) & exte\tikzmark{L}nsion & exte\tikzmark{M}nsion & ano\tikzmark{N}maly 
@@
 \draw[<->,bend left,color=Orange,line width=1.5] (A.north) to (C.north);
-\draw[<->,color=Orange,line width=1.5] (B.north west) .. controls +(80:0.5) ..  (B.north east);
+\draw[<->,color=Orange,line width=1.5] (B.north west) .. controls +(75:0.5) ..  (B.north east);
 \draw[<->,bend left,color=Orange,line width=1.5] (P.north) to (R.north);
-\draw[<->,color=Orange,line width=1.5] (Q.north west) .. controls +(80:0.5) ..  (Q.north east);
-\draw[<->,color=Orange,line width=1.5] (S.south) to (N.north);
-\draw[<->,color=Orange,line width=1.5] (T.south) to (M.north);
-\draw[<->,color=Orange,line width=1.5] (U.south) to (L.north);
+\draw[<->,color=Orange,line width=1.5] (Q.north west) .. controls +(75:0.5) ..  (Q.north east);
+\draw[<->,color=Orange,line width=1.5] (S.south) to ([yshift=.2em]N.north);
+\draw[<->,color=Orange,line width=1.5] ([yshift=+.2em]T.south) to ([yshift=0em]M.north);
+\draw[<->,color=Orange,line width=1.5] (U.south) to ([yshift=.2em]L.north);
 }
@@
 
-Our result is equally applicable in the case of \Nequals1 supersymmetric QCD, for which
-Intriligator and Seiberg found in \cite{Intriligator:1995id} a duality exchanging $\so(N_c)$ and $\so(N_f-N_c+4)$,
+Our result is equally applicable in the case of \Nequals1 supersymmetric QCD, 
+since they are connected to the non-supersymmetric QCD by a continuous deformation 
+preserving all the symmetries we care about.
+Now, let us recall that Intriligator and Seiberg found in \cite{Intriligator:1995id} a duality exchanging $\so(N_c)$ and $\so(N_f-N_c+4)$,
 which in our notation sends $n_c$ to $n_c'=n_f-n_c+2$.
 In \cite{Aharony:2013hda}, this duality was refined to account for the global form of the gauge group and the discrete theta angle, and it was concluded that $\Spin$ is exchanged with $\SO_-$ while $\SO_+$ maps to itself.
-This mapping was checked using supersymmetric localization on $S^3/\bZ_n \times S^1$ in \cite{Razamat:2013opa}.
+This mapping was given a further check e.g.~by using supersymmetric localization on $S^3/\bZ_n \times S^1$ in \cite{Razamat:2013opa}.
 Our analysis allows us to check this duality by comparing how the 1-form symmetry and the 0-form symmetry are combined in the dual pairs.
 We superimposed the action of the duality on our main Table~\ref{table:main}.
-It is satisfying to see that the duality action correctly preserves the labels `none', `anomaly' and `extension'.
+It is satisfying to see that the duality action correctly preserves the behaviors `none', `anomaly' and `extension'.
 
@@
 we determine exactly when the electric/magnetic/dyonic $\bZ_2$ 1-form symmetries
-and the $\SU(2n_f)/\bZ_2$ flavor 0-form symmetry are mixed nontrivially,
+and the $\SU(2n_f)/\bZ_2$ flavor 0-form symmetry form a nontrivial 2-group,
 by examining the charges of line operators in each theory.
 In Sec.~\ref{sec:sl2z},
-we exploit the $\SL(2,\bZ_2)$ actions on $\so(2n_f)$ QCDs to determine the 't Hooft anomalies they possess.
+we exploit the $\SL(2,\bZ_2)$ actions on theories with $\bZ_2$ 1-form symmetries, including our $\so(2n_f)$ QCDs.
+This will allow us to determine the 't Hooft anomalies they possess.
 Combining the results with those obtained in Sec.~\ref{sec:2-group},
@@
 Although the result itself is satisfactory, the analysis leading to it is somewhat ad-hoc, 
-so we partially complement it with the more direct computation of fermion anomalies in Sec.~\ref{sec:fermion}.
+so we partially complement it with a more direct computation of fermion anomalies in Sec.~\ref{sec:fermion}.
 Finally, the two appendices provide technical details of the mathematical facts used in the main part;
@@
 and in Appendix~\ref{sec:nonclosedP}, we describe some subtleties concerning the Pontrjagin square.
+
+Before proceeding, we list the obstruction classes we frequently encounter in this paper.
+In general, given a group $G$, a subgroup $\bZ_n$ in the center of $G$,
+and a $G/\bZ_n$ bundle on a manifold $X$, 
+there is a obstruction class $\in H^2(X; \bZ_n)$ controlling whether this bundle lifts to $G$.
+For $G=\Spin(N_c)$ and $G/\bZ_2=\SO(N_c)$ this is the familiar second Stiefel-Whitney class $w_2$.
+The classes we use are listed in Table~\ref{table:w2}.
+
+\begin{table}
+\[
+\begin{array}{c| cc| c|c}
+\text{name} & G/\bZ_n & G & \bZ_n & \text{comments}\\
+\hline 
+w_2 & \SO(2n_c) & \Spin(2n_c) & \bZ_2\\
+v_2 & \SO(2n_c)/\bZ_2 & \SO(2n_c) &\bZ_2\\
+x_2 & \SO(2n_c)/\bZ_2 & \Spin(2n_c) &\bZ_4 & (n_c:\text{odd})\\
+\hline
+a_2 & \SU(2n_f)/\bZ_2 & \SU(2n_f) &\bZ_2\\
+a_2 & \USp(2n_f)/\bZ_2 & \USp(2n_f) &\bZ_2\\
+\end{array}
+\]
+\caption{Our names for the obstruction classes $\in H^2(X,\bZ_n)$ controlling whether a $G/\bZ_n$ bundle
+on $X$ lifts to a $G$ bundle.  \label{table:w2}}
+\end{table}
 

### 2021-07-01 paper.tex
edits on Sec.2.1

@@
 We start by discussing the $\Spin(2n_c)$ gauge theories. 
+The results presented in this section was originally found in \cite[Sec.~4.4]{Hsin:2020nts}.
+
 First, recall that the center of $\Spin(2n_c)$ is $\bZ_2\times \bZ_2$ or $\bZ_4$ depending on whether $n_c$ is even or odd.
@@
 This means that we have the following extension of groups \begin{equation}
-0\to \underbrace{\bZ_2}_{\substack{\text{subgroup of}\\
-\text{rep.~of center of}\\
-\text{flavor $\SU(2n_f)$}}}
+0\to \underbrace{\bZ_2}_{\substack{\text{group of}\\
+\text{charges under}\\
+\text{$\{\pm1\}\in \SU(2n_f)$}}}
 \to \bZ_4 
@@
 \end{equation}
-This means that the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry form the 2-group $H$ fitting in the sequence \begin{equation}
+
+In general, a 2-group $H$ combining a 1-form symmetry $A$ and a 0-form symmetry $G$ of the form \begin{equation}
+0\to A[1]\to H\to G\to 0
+\end{equation} with the extension class $\alpha\in H^3(BG,A)$ is defined as a symmetry whose background field is given by a pair of a degree-2 cochain $E\in C^2(X,A)$ and a background $G$ field $g:X\to BG$ such that $\delta E = g^*(\alpha)$.
+Here $A[1]$ means the Abelian group $A$ regarded as a 1-form symmetry,
+and we drop the pull-back symbol $g^*$ when its presence is clear from the context.
+In our case, we see that the $\bZ_2$ 1-form symmetry and the $\SU(2n_f)/\bZ_2$ 0-form flavor symmetry form the 2-group $H$ fitting in the sequence \begin{equation}
 0\to \bZ_2[1]\to H \to \SU(2n_f)/\bZ_2 \to 0
 \label{group-extension}
-\end{equation} with the Postnikov class being $\beta a_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2)$.
-
-Before proceeding, we note that having the extension of groups of charges of line operators as in \eqref{charge-extension}
+\end{equation} with the extension class being $\beta a_2 \in H^3(B(\SU(2n_f)/\bZ_2);\bZ_2)$.
+
+Note that having the extension of groups of charges of line operators as in \eqref{charge-extension}
 is equivalent to having a nontrivial 2-group extension \eqref{group-extension} 

### 2021-07-01 paper.tex
edits on Sec.2.2

@@
 
-In this paper, we study these issues in the case of 4d $\so(N_c)$ gauge theories with 
+In this paper, we study these issues in the case of 4d $\so$ quantum chromodynamics (QCD),
+i.e.~$\so(N_c)$ gauge theories with 
 $N_f$ flavors of fermion fields in the vector representation.
@@
 but dynamical monopoles can receive flavor/gauge center charges from the fermion zero modes.
+
+\paragraph{Deformations:}
 To study these issues, it is useful to deform the theory and make it simpler
@@
 The fundamental representation still transforms nontrivially under $-1\in \USp(2n_f)$, which is enough for our purposes.
-\item Add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +c.c.$, where $J_{[ij]}$ is the constant matrix for the $\usp(2n_f)$ part.
-\item Give a vacuum expectation value (vev) to $\Phi_{ab}$ to break $\SO(2n_c)$ to $\SO(2)^{n_c}$.
+\item Add an adjoint scalar $\Phi_{[ab]}$ and the interaction $\psi^{ai}_\alpha \psi^{bj}_\beta J_{ij} \Phi_{ab}\epsilon^{\alpha\beta} +c.c.$.
+Here $a,b$ and $i,j$ are vector indices of $\so(2n_c)$ and $\usp(2n_f)$,
+$\alpha,\beta$ are the spinor indices,
+and  $J_{[ij]}$ is the constant matrix for the $\usp(2n_f)$.
+\item Give a generic vacuum expectation value (vev) to $\Phi_{ab}$ to break $\SO(2n_c)$ to $\SO(2)^{n_c}$.
 \end{itemize}
@@
 
+\paragraph{Reduction to  the $\so(4)$ case:}
 For this purpose we need to know slightly more details of the dynamical monopoles.
-The dynamical monopoles associated to the breaking of $G$ to its Cartan were analyzed in many places, 
+The dynamical monopoles associated to the breaking of a gauge group to its Cartan were analyzed in many places, 
 e.g.~in \cite{Weinberg:1979zt}.
@@
 This determines the simple roots $\alpha$.
-Then you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole and have a monopole solution without additional bosonic moduli.
-
-Let us say we chose the standard $\phi$ such that the simple roots are $(1,-1,\ldots,0)$,
-$(0,1,-1,\ldots,0)$, \ldots, $(0,\ldots,1,-1)$ and $(0,\ldots,1,+1)\in \bZ^{n_c}$,
+Then you can embed the standard spherically-symmetric 't Hooft-Polyakov monopole
+using the $\mathfrak{su}(2)$ subalgebra associated to $\alpha$,
+and have a monopole solution without additional bosonic moduli.
+
+Let us say we chose the standard $\phi$ such that the simple roots are 
+\begin{equation}
+(1,-1,\ldots,0),\ 
+(0,1,-1,\ldots,0),\ldots,
+(0,\ldots,1,-1),\ 
+(0,\ldots,1,+1)\in \bZ^{n_c},
+\end{equation}
 which we call simple dynamical monopoles.
@@
 by the subgroup generated by the charges of simple dynamical monopoles,
-which we denote by
-$(1,-1,\ldots, 0; q_1)$, $(0,1,-1,\ldots, 0; q_2)$, \ldots,
-$(0,\ldots, 1,-1; q_{n_c-1})$ and $(0,\ldots,1,+1; q_{n_c})$, respectively.
+which we denote respectively by
+\begin{equation}
+(1,-1,\ldots,0;q_1),\ 
+(0,1,-1,\ldots,0;q_2),\ldots,
+(0,\ldots,1,-1;q_{n_c-1}),\ 
+(0,\ldots,1,+1;q_{n_c}).
+\end{equation}
 
@@
 Then, only $q_{n_c-1}$ and $q_{n_c}$ need to be determined.
-This reduces the study to the case of $n_c=2$ and $\so(4)\simeq \su(2)_1 \times \su(2)_2$,
+This reduces the study to the case of $n_c=2$ and $\so(2n_c)\simeq \su(2)_1 \times \su(2)_2$,
 where the monopoles associated to the simple roots are just 't Hooft-Polyakov monopoles associated to the two factors of $\su(2)$'s.
+
+\paragraph{Analysis of the $\so(4)$ case:}
+
 The vev of the adjoint scalar in this basis can be written as $(a_1,a_2)$, which we assume to be $a_1>a_2>0$.
@@
 Now, the explicit analysis in \cite[Sec.~IV]{Callias:1977kg} concerning the number of zero modes in the 't Hooft-Polyakov monopole says that 
-a doublet coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
+a doublet fermion coupled to an adjoint vev of size $a$ with bare mass $\mu$ has
 a zero mode if $|a|>|\mu|$ and 
@@
 
-Let us determine $q_{n_c}$.
+Let us determine $q_{n_c}$, the center charge of the monopole in $\su(2)_1$.
 We saw that there are two zero modes per flavor; 
@@
 	It is actually broken to $\u(1)$, but keeping $\su(2)_2$ representation is useful in organizing the answer.
-}, and
+}, 
 $R_{2n_f}$ is the fundamental of $\usp(2n_f)$,
@@
 it suffices to consider the case $n_f=1$;
-the general case is given by simply multiplying it by $n_f$.
+the general case is given simply by multiplying it by $n_f$.
 When $n_f=1$, there are $4$ Majorana fermions.
@@
 
-Combining the intermediate steps above, we conclude the following: 
+\paragraph{Summary:}
+Combining the intermediate steps we described above, we conclude the following: 
 for the $\SO(2n_c)_+$ theory,
@@
 \renewcommand{\arraystretch}{1.2}
-\begin{tabular}{rl|ccc}
+\begin{tabular}{r@{\,}l|ccc}
 $(n_c,$&$n_f)$ & $\Spin$ & $\SO_+$ & $\SO_-$\\

### 2021-07-01 paper.tex
edits on Sec.3

@@
 \def\Nequals#1{$\mathcal{N}{=}#1$}
+\def\bQ{\mathbb{Q}}
 \def\bZ{\mathbb{Z}}
@@
 In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
-In a QFT, any symmetry comes with its (possibly trivial) 't Hooft anomaly.
-Here we determine the anomalies of these theories using the $\SL(2,\bZ_2)$ action on the set of QFTs with $\bZ_2$ 1-form symmetry.
+%In a QFT, any symmetry can come with an't Hooft anomaly.
+Here we determine the anomalies of these symmetries, 
+utilizing the $\SL(2,\bZ_2)$ action on the set of QFTs with $\bZ_2$ 1-form symmetry.
 
@@
 
-Let us say that  a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry is given.
+Let us say that we are given a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry.
 We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
@@
 We can show that $S^2=T^2=1$ and $(ST)^3=1$, meaning that they generate $\SL(2,\bZ_2)$.
-This operation was considered in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.
+This operation was introduced in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.
 
@@
 More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
-Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
+Here the theories with $T$ prepended are different from the original ones only by its discrete theta coupling to the background.
 Then we have the following chain of actions: \begin{equation}
@@
 \end{tikzpicture}
+\label{sl2z-on-so}
 \end{equation}
@@
 and we perform the $\SL(2,\bZ_2)$ action  by picking a $\bZ_2$ subgroup.
-The symmetry and the anomaly of the resulting theory can be determined by a formal argument once those of the original theory 
-and the action of the anomaly-free subgroup to be gauged are given \cite{Tachikawa:2017gyf}.
-
-Let us work at the level of anomalies described at the level of cohomology, since we do not need to deal with anomalies more general than that.
+The symmetry and the anomaly of the resulting theory can be determined by a formal argument independent of the dynamics of the theory,
+once the symmetry and the anomaly of the original theory 
+and the action of the anomaly-free subgroup to be gauged are given, as discussed in \cite{Tachikawa:2017gyf}.
+
+Let us work at the level of anomalies described by cohomology, since we do not need to deal with more general anomalies described by bordism.
 We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G;\U(1))$. 
@@
 This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
-by taking $\nu$ to be an arbitrary lift of $\mu$ from $H$ to $G$.
+by taking $\nu$ to be an arbitrary lift of $\mu$ from $H$ to $G$.\footnote{%
+At this stage, the residual identifications $(0,\alpha')\sim (0,\alpha'')$ are of the form 
+$\alpha''=\alpha'+\delta \nu$, where $\nu\in C^{d}(G;U(1))$ is required to satisfy $\nu|_H=0$.
+Their equivalence classes form the relative cohomology group $H^{d+1}(G,H;U(1))$.
+It might be interesting to study anomalies taking values in the relative cohomology groups.
+}
 This is convenient in discussing the $\SL(2,\bZ_2)$ action,
@@
 
+\paragraph{The four choices:}
 Now, what are the possible choices of $(\mu,\alpha)\sim(0,\alpha')$ we need to discuss?
@@
 As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly for 4d spin QFTs with this symmetry is \begin{equation}
-\alpha=2\pi i \cdot \frac12  B\beta E  \label{anom}
-\end{equation} where $B,E\in H^2(Y;\bZ_2)$ are the background fields on the bulk 5d spin manifold $Y$.
+\alpha=%2\pi i \cdot 
+\frac12  B\beta E  \label{anom}
+\end{equation} where $B,E\in H^2(Y;\bZ_2)$ are the background fields on the bulk 5d spin manifold $Y$,
+and we use $\bQ/\bZ$-valued cochains to describe the anomaly.
 Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivial i.e. $\alpha|_{H=\bZ_2} = 0$,
 and thus the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
-\mu = 2\pi i \cdot \frac14 \fP(E).\label{P}
-\end{equation}
-This $\mu$ can be lifted from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ group as a closed cochain.
+\mu =% 2\pi i \cdot
+ \frac14 \fP(E),\label{P}
+\end{equation}
+where $\fP$ is the Pontrjagin square.
+This $\mu$ can be lifted from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ group as a closed cochain, 
+and therefore does not affect the gauging process.
 Therefore, we only have to consider pairs $(0,0)$ and $(0,\alpha)$.
@@
 Next, we consider $\bZ_4$ 1-form symmetry.
-Again in the Appendix~\ref{sec:bordism}, we show that this time there is no anomaly for $\bZ_4$ 1-form symmetry.
-Therefore we can pick $\alpha=0$. Then the possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
+In the Appendix~\ref{sec:bordism}, we show that there is no anomaly for $\bZ_4$ 1-form symmetry.
+Therefore we can pick $\alpha=0$. Then the only possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
 One difference here is that the discrete theta angle \eqref{P} cannot be lifted as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
@@
 one finds \begin{equation}
-\alpha':=\delta \mu = 2\pi i \cdot \frac12 a_2 \beta_2 a_2.\label{anom'}
-\end{equation}
-Therefore, the pairs we need to consider are $(0,0)$ and $(\mu,0)\sim (0,\alpha')$.
+\alpha':=\delta \mu = %2\pi i \cdot 
+\frac12 a_2 \beta_2 a_2,\label{anom'}
+\end{equation}
+where $\beta_2$ is the Bockstein associated to the sequence $0\to \bZ\to \bZ \to \bZ_4\to 0$,
+whose action on $a_2$ can be defined since $a_2$ lifts to a $\bZ_4$-valued cochain.
+Summarizing, the pairs  we need to consider for the $\bZ_4$ one-form symmetry are $(0,0)$ and $(\mu,0)\sim (0,\alpha')$.
 
@@
 
+\paragraph{$\SL(2,\bZ_2)$ action on the four choices:}
 Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
@@
 
-To make  the coupling \eqref{boo}  well-defined, we consider adding a background term to \eqref{boo} so that we have \begin{equation}
+To make  the coupling \eqref{boo}  well-defined, we consider adding a counterterm depending solely on the newly introduced field $B$ to \eqref{boo} so that we have \begin{equation}
 \exp\left[2\pi i\int_X \left( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) \right)\right]
@@
 
+Let us now combine our result in Table~\ref{table:2group},
+which summarizes our knowledge whether the 0-form part and the 1-form part form a nontrivial 2-group,
+and the $SL(2,\bZ_2)$ action on the four choices, \eqref{trivial-chain} and \eqref{nontrivial-chain}, we determined above.
+We first need to double each column of Table~\ref{table:2group},
+since we need to distinguish $\Spin$ from $T\Spin$ and $\SO_\pm$ from $T\SO_\pm$.
+The entry `product' in Table~\ref{table:2group} corresponds to either `none' or `anomaly',
+and the entry `extended' there corresponds to either `extension' or `\Textended'.
+We now demand that the $\SL(2,\bZ_2)$ action \eqref{sl2z-on-so} on $\so$ QCDT to be compatible with the $\SL(2,\bZ_2)$ action on the labels, \eqref{trivial-chain} and \eqref{nontrivial-chain}.
+The only consistent assignment is given in Table~\ref{table:refined}.
+As the way we determined the symmetry structures were somewhat indirect,
+we confirm the symmetry structures of the $\Spin$ case in the next section
+in a different means.
+
 \begin{table}
@@
 \draw[<->,bend left,color=Orange,line width=1.5] (a2.north) to (a5.north);
-\draw[<->,color=Orange,line width=1.5] (a3) to (a4);
-\draw[<->,bend right,color=Orange,line width=1.5] (b1.south) to (b6.south);
-\draw[<->,bend right,color=Orange,line width=1.5] (b2.south) to (b5.south);
-\draw[<->,color=Orange,line width=1.5] (b3.south) to (b4.south);
+\draw[<->,bend left,color=Orange,line width=1.5] (a3.north) to (a4.north);
+\draw[<->,color=Orange,line width=1.5] (b1.north) .. controls +(10:10em) ..  (b6.north);
+\draw[<->,color=Orange,line width=1.5] (b2.north) .. controls +(10:5em) ..  (b5.north);
+\draw[<->,color=Orange,line width=1.5] ([yshift=.2em]b3.west) to ([yshift=.2em]b4.east);
 \draw[<->,color=Orange,line width=1.5] (c1.south) to (d6.north);
@@
 \end{table}
-
-Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
-and Table~\ref{table:2group},
-we see that the anomaly is automatically determined and 
-we obtain the result which was already presented in Table~\ref{table:main}.
-More precisely, we should better distinguish $\Spin$ and $T(\Spin)$ etc.,
-and we find the assignment given in Table~\ref{table:refined}.
-As the way we determined the symmetry structures were somewhat indirect,
-we confirm the symmetry structures of the $\Spin$ case in the next section
-in a different means.
 

### 2021-07-01 paper.tex
edits on Sec.4

@@
 \def\Nequals#1{$\mathcal{N}{=}#1$}
+\def\bR{\mathbb{R}}
 \def\bQ{\mathbb{Q}}
@@
 we find that the anomaly is trivial when $(n_c,n_f)$ is (even,even) or (odd,even),
-while it is $\alpha$ when $(n_c,n_f)$ is (odd,even) and $\alpha'$ when (odd,odd).
+while it is $\alpha$ given in \eqref{anom} when $(n_c,n_f)$ is (odd,even) 
+and $\alpha'$ given in \eqref{anom'} when (odd,odd).
 Since the 1-form symmetry background in the $\Spin$ theory is simply the Stiefel-Whitney class $w_2$ of the $\SO(2n_c)$ gauge bundle, 
 these anomalies should simply come from the anomalies of fermions charged under $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
-Here we use $\USp(2n_f)$ instead of $\SU(2n_f)$, because under the latter we also have perturbative anomalies, which might complicate the analysis.
+Here we use $\USp(2n_f)$ instead of $\SU(2n_f)$, because under the latter we also have perturbative anomalies, which would complicate the analysis.
 
 For even $n_c$, the anomaly should be given by  \begin{equation}
-\alpha= 2\pi i \cdot \frac12 w_2 \beta a_2
+\alpha=% 2\pi i \cdot 
+\frac12 w_2 \beta a_2
 \end{equation}
@@
  \begin{equation}
-\alpha'=2\pi i \cdot \frac12 v_2 \beta_2 v_2
+\alpha'=%2\pi i \cdot
+ \frac12 v_2 \beta_2 v_2
 \end{equation} where $v_2$ is the class in $H^2(X;\bZ_2)$ which is the mod-2 reduction of
@@
 Before proceeding, we have two remarks.
-First, this method was first used in \cite[Sec.~4]{Witten:1995gf} under the name of `a curious minus sign', and recognized as determining an anomaly in \cite[Sec.~2.4.3]{Cordova:2018acb}.
-It was also used in \cite[Sec.~3.1 and Sec.~5.1.2]{Wang:2018qoy}.
+First, this method was first used in \cite[Sec.~4]{Witten:1995gf} to understand `a curious minus sign' 
+appearing in the topologically-twisted Seiberg-Witten theory, 
+which was more recently recognized as determining an anomaly in \cite[Sec.~2.4.3]{Cordova:2018acb}.
+It was also used in \cite[Sec.~3.1 and Sec.~5.1.2]{Wang:2018qoy} to relate the `new' $\SU(2)$ anomaly 
+with the effective interaction in the $\U(1)$ theory.
 Second, in this section we can only say that the effective interaction we find is compatible with the anomalies
@@
 We break $\USp(2n_f)$ down to $\U(n_f)$ using a scalar field,
-such that the fundamental representation of $\USp(2n_f)$ splits to the fundamental plus the anti-fundamental representation of $\U(n_f)$.
+such that the fundamental representation of $\USp(2n_f)$ splits into the fundamental plus the anti-fundamental representation of $\U(n_f)$.
 The monopole charge is given by the first Chern class $c_1$ of the low-energy $\U(n_f)$ flavor symmetry.
@@
 whose quantization leads to the spinor representation.
-This means that there is an effective interaction \begin{equation}
-2\pi i \cdot \frac12 \int_X w_2 c_1.
+
+As first discussed in \cite{Thorngren:2014pza} and also used in \cite[Sec.~3.1]{Wang:2018qoy},
+this means that there is an effective interaction \begin{equation}
+%2\pi i \cdot
+ \frac12 \int_X w_2 c_1.
+ \label{bulk}
 \end{equation} %where $w_2$ is the Stiefel-Whitney class of the $\SO(2n_c)$ bundle
 %and $c_1$ is the first Chern class of $\U(n_f)$.
+One way to understand it is as follows.
+
+We started from a system which has $\SO(2n_c)$ symmetry,
+but the spinor representation is only a projective representation of this symmetry.
+This is an anomaly at the core of the monopole, which needs to flow in from the bulk.
+Indeed, take the spacetime  to be $X=\bR_{\ge 0} \times \bR_t \times S^2$ around the monopole.
+Reducing the bulk term \eqref{bulk} on $S^2$ with $\int_{S^2} c_1=1$, 
+we have the  effective interaction $\int_Y w_2$
+on the half-space $Y=\bR_{\ge 0}\times \bR_t$,
+and the monopole lives on the boundary. 
+Therefore, the degree of freedom on the boundary is in the projective representation characterized by 
+$w_2\in H^2(\SO(2n_c),\bZ_2)$.
 
@@
 $\SO(2n_c)\times \USp(2n_f)$ to $[\SO(2n_c)\times \USp(2n_f)]/\bZ_2$.
-Note that $\pi_1(U(n_f)/\bZ_2)=\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
-
-Furthermore, when $n_f$ is even, $c_1(\U(n_f)) = c_1(\U(n_f)/\bZ_2)$ and $a_2(\U(n_f)/\bZ_2)=a_2(\USp(2n_f))$.
-When $n_f$ is odd, $c_1(\U(n_f)/\bZ_2)=2 c_1(\U(n_f))$ when the latter is well-defined and $a_2(\U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(\U(n_f)/\bZ_2)$.
+Note that $\pi_1(\U(n_f)/\bZ_2)=\bZ\times \bZ_2$  or $\bZ$ depending on whether $n_f$ is even or odd.
+We denote by $a_2$ the obstruction class to lift a $\U(n_f)/\bZ_2$ bundle to a $\U(n_f)$ bundle.
+This implies the following:
+\begin{itemize}
+\item When $n_f$ is even, $c_1(\U(n_f)) = c_1(\U(n_f)/\bZ_2)$ and $a_2(\U(n_f)/\bZ_2)=a_2(\USp(2n_f))$.
+\item When $n_f$ is odd, $c_1(\U(n_f)/\bZ_2)=2 c_1(\U(n_f))$ when the latter is well-defined.
+More generally, $a_2(\U(n_f)/\bZ_2)$ is the mod-2 reduction of $c_1(\U(n_f)/\bZ_2)$.
+\end{itemize}
 We now compute the anomaly cochains in the four cases separately:
 \paragraph{$(n_c,n_f)$=(even,even):}
-$w_2(\SO(2n_c))$ and $c_1(\U(n_f))$ can be generalized without any problem,
+$w_2(\SO(2n_c))$ and $c_1(\U(n_f))$ can be generalized to closed cochains of $\SO(2n_c)/\bZ_2$ 
+and of $\U(n_f)/\bZ_2$
+without any problem,
 and therefore \begin{equation}
@@
 \end{equation}
-When $n_c=2$ and $n_f=1$, we can confirm this is indeed the entire anomaly,
+When $n_c=2$ and $n_f=1$, we can confirm that this is indeed the entire anomaly,
 since we can compute $\mathrm{Hom}(\Omega^\text{spin}_5([\SO(4)\times \USp(2)]/\bZ_2),\U(1))$
@@
 \paragraph{$(n_c,n_f)$=(odd,odd):}
-Now we make the replacement on both sides and the effective interaction is \begin{equation}
+Now we make the replacement on both sides and therefore the effective interaction is \begin{equation}
 \frac18 x_2(\SO(2n_c)/\bZ_2) c_1(\U(n_f)/\bZ_2) 

### 2021-07-01 paper.tex
edits on App. B to make it purely about P(x)

@@
 \newcommand*{\colorD}[1]{\textcolor{colorD}{#1}}
+
+\let\tilde\widetilde
 
@@
 	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(K(\bZ_4,2);\Omega_q^{\text{spin}}\big) && \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_4,2))\vspace{4mm}\\
+		E^2_{p,q}=H_p\big(K(\bZ_4,2);\Omega_q^{\text{spin}}\big) && \tilde\Omega_{p+q}^{\text{spin}}(K(\bZ_4,2))\vspace{4mm}\\
 		\begin{array}{c|c:cccccccccccc}
@@
 		E^2_{p,q}=H_p\big(K(\bZ_2\times \bZ_2,2);\Omega_q^{\text{spin}}\big)
-		&& \widetilde\Omega_{p+q}^{\text{spin}}(K(\bZ_2\times \bZ_2,2))\vspace{4mm}\\
+		&& \tilde\Omega_{p+q}^{\text{spin}}(K(\bZ_2\times \bZ_2,2))\vspace{4mm}\\
 		\begin{array}{c|c:cccccccccccc}
@@
 \subsubsection{Adams SS}
-According to our naive guess, the module $\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
+According to our naive guess, the module $\tilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
 \begin{equation}
@@
 \begin{equation}
-	\widetilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
+	\tilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
 \end{equation}
@@
 \label{sec:nonclosedP}
-By definition, the variation of the Pontrjagin square $\fP : H^\bullet(-;\bZ_{2^m}) \to H^{2\bullet}(-;\bZ_{2^{m+1}})$ term is
+We take the definition of the Pontrjagin square for an element $x\in C^\bullet(-;\bZ_2)$
+to be \begin{equation}
+\fP(x):= \tilde x \cup\tilde x - \tilde x \cup_1 \delta \tilde x
+\end{equation} where $\tilde x $ is an integral cochain which reduces to $x$.
+The variation of the Pontrjagin square is then given by 
 \begin{equation}
@@
 		\delta \left(\dfrac{1}{2^{m+1}}\fP(x)\right)
-		& = & \dfrac{1}{2^{m+1}}\cdot \delta \Big(\widetilde x \cup \widetilde x - \widetilde x \cup_1 \delta \widetilde x\Big)\\
-		& = & \dfrac{1}{2^{m+1}}\cdot\left[\Big(\delta \widetilde x \cup \widetilde x + \widetilde x \cup \delta \widetilde x\Big)
-				- \Big(\widetilde x \cup \delta \widetilde x - \delta \widetilde x \cup \widetilde x + \delta \widetilde x \cup_1 \delta \widetilde x\Big)\right]\vspace{2mm}\\
-		& = & \dfrac{1}{2^{m+1}}\cdot\Big[2\cdot \delta \widetilde x \cup \widetilde x - \delta \widetilde x \cup_1 \delta \widetilde x\Big],\\
-	\end{array}
-\end{equation}
-and thus if $x$ were a $\bZ_{2^m}$-cocycle, 
-its integral lift $\widetilde x \in C^\bullet(-;\bZ)$ would be a cocycle mod $2^m$ \textit{i.e.}~$\delta \widetilde x = 0$ (mod $2^m$),
-and the right hand side would be $0$ mod 1,
-which then means that $\fP(x)$ would be a $\bZ_{2^{m+1}}$-cocycle as desired.
+		& = & \dfrac{1}{2^{m+1}}\cdot \delta \Big(\tilde x \cup \tilde x - \tilde x \cup_1 \delta \tilde x\Big)\\
+		& = & \dfrac{1}{2^{m+1}}\cdot\left[\Big(\delta \tilde x \cup \tilde x + \tilde x \cup \delta \tilde x\Big)
+				- \Big(\tilde x \cup \delta \tilde x - \delta \tilde x \cup \tilde x + \delta \tilde x \cup_1 \delta \tilde x\Big)\right]\vspace{2mm}\\
+		& = & \dfrac{1}{2^{m+1}}\cdot\Big[2\cdot \delta \tilde x \cup \tilde x - \delta \tilde x \cup_1 \delta \tilde x\Big].\\
+	\end{array}
+\end{equation}
+If $x$ is a $\bZ_{2^m}$-cocycle, 
+$\tilde x \in C^\bullet(-;\bZ)$ is a cocycle mod $2^m$ \textit{i.e.}~$\delta \tilde x = 0$ (mod $2^m$),
+and the right hand side is $0$ mod 1,
+which then means that $\fP(x)$ is a $\bZ_{2^{m+1}}$-cocycle as desired, 
+defining a cohomology operation $\fP : H^\bullet(-;\bZ_{2^m}) \to H^{2\bullet}(-;\bZ_{2^{m+1}})$.
+
 However, when $x$ is not a cocycle but merely a cochain,
-$\fP(x)$ is also not a cocycle and it is not clear whether this term is well-defined in the first place.
-
-This problem arises when we consider $SO(2n_c)$ QCD,
-but it turns out that this can be saved somewhat miraculously as follows.
-First, a short exact sequence
+$\fP(x)$ is also not a cocycle.
+For the purpose of this paper, we only need to consider the case when
+\begin{equation}
+\delta x = \beta y
+\end{equation} 
+for a cocycle $y\in Z^2(-;\bZ_2)$.
+In this case, $x$ and $y$ combine to define a cocycle $z\in Z^2(-;\bZ_4)$,
+such that $z = y$ modulo 2 and $\tilde z=2\tilde x$ when $y=0$.
+This motivates us to consider the term \begin{equation}
+\frac 14 \cdot \frac14 \fP(\tilde z) 
+\end{equation} as a replacement for \begin{equation}
+\frac14 \fP(\tilde x).
+\end{equation}
+Using \eqref{deltaPontrjagin}, we find \begin{equation}
+\delta\left(
+\frac14\cdot\frac14 \fP(\tilde z)
+\right)
+ = \frac 12 (\frac14\delta\tilde z) \cup \tilde z
+ = \frac12 \beta_2 y \cup y
+\end{equation} where equalities are all modulo 1.
+
+Here, $\beta_2$ is the higher Bockstein operation
+defined for cocycles $y\in H^2(-;\bZ_2)$ known to be liftable to $z\in H^2(-;\bZ_4)$,
+by the formula \begin{equation}
+\beta_2 y := \frac14 \delta \tilde z
+\end{equation} where $\tilde z$ is a lift to an integral cochain of $z$.
+
+In general,
+%This problem arises when we consider $SO(2n_c)$ QCD,
+%but it turns out that this can be saved somewhat miraculously as follows.
+the short exact sequence
 \begin{equation*}
@@
 	\to
-	\bZ_{2^f}
+	\bZ
 	\overset{\times 2^{f}}{\longrightarrow}
-	\bZ_{2^{2f}}
+	\bZ
 	\overset{p}{\longrightarrow}
@@
 \end{equation*}
-buys us cohomology operations called the higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ_{2^f})$,
-and for the element $y \in C^{\bullet}(-;\bZ_{2^f})$ one has
+buys us a cohomology operation called the higher Bockstein $\beta_f: H^{\bullet}(-;\bZ_{2^f}) \to H^{\bullet+1}(-;\bZ)$, defined for the element $z \in Z^{\bullet}(-;\bZ_{2^f})$ 
+by 
 \begin{equation*}
-	\delta (p^\ast y)
-	=
-	2^f \beta_f (y) \in C^\bullet(-;\bZ_{2^{2f}}).
+	\beta_f (z) := \frac{1}{2^f}
+	\delta (\tilde z)
+	\in C^\bullet(-;\bZ).
 \end{equation*}
-Now, let us consider the case of odd $n_c$.
-Here, the cochain $w_2(c) \in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_2)$
-can be thought of as a mod-2 reduction of $\widetilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
-Dividing the $SO\times SU$ by $\bZ_2$, these cochains become non-closed
-\begin{equation*}
-	\delta \widetilde w_2(c) = 2 \beta v_2(c)
-\end{equation*}
-where $v_2(c)\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
+where $\tilde z$ is a lift of $z$ as an integral cochain.
+Then, $\beta_{n+1} y$  for $y \in H^2(-;\bZ_2)$ is defined only for those $y$ satisfying $\beta_{n}y=0$,
+and is the simplest example of a higher cohomology operation.
+
+%Now, let us consider the case of odd $n_c$.
+%Here, the cochain $w_2(c) \in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_2)$
+%can be thought of as a mod-2 reduction of $\tilde w_2(c)\in C^2(SO(4n'_c+2)\times SU(2n_f); \bZ_4)$.
+%Dividing the $SO\times SU$ by $\bZ_2$, these cochains become non-closed
+%\begin{equation*}
+%	\delta \tilde w_2(c) = 2 \beta v_2(c)
+%\end{equation*}
+%where $v_2(c)\in C^2\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}; \bZ_2\right)$.
 %\begin{equation*}
 %	\begin{array}{ccccccccc}
-%		&& w_2 && \widetilde w_2 & \longmapsto & v_2\\
+%		&& w_2 && \tilde w_2 & \longmapsto & v_2\\
 %		&& \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$} && \rotatebox[]{270}{$\in$}\\
@@
 %		&& \rotatebox[]{90}{$\in$} && \rotatebox[]{90}{$\in$}\\
-%		&& \delta w_2 && \delta \widetilde w_2
+%		&& \delta w_2 && \delta \tilde w_2
 %	\end{array}
 %\end{equation*}
-Since this implies $\delta \widetilde w_2(c) = 0$ or $2$ mod 4
-and furthermore $\delta (2\widetilde w_2(c)) = 0$ mod 4,
-one can safely define the Pontrjagin square $\tfrac{1}{8}\fP\big(2\widetilde w_2(c)\big)$.\footnote{
-	Be careful that this factor $2$ here is not the usual map sending $\{0,1\}=\bZ_2$ to $\{0,2\}\subset \bZ_4$.
-	This time we are \textit{really} multiplying by $2$.
-}
-Note that this can naively be regarded as $2\cdot \tfrac{1}{4}\fP\big(w_2(c)\big)$ at the integral cochain level.
-While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
-$\tfrac{(2^m)^2}{2^{m+1}}\bZ = 2^{m-1}\bZ = 2\bZ$ and dividing by two does not cause any trouble,
-the first term does as it takes value in $\tfrac{2\cdot 2^m}{2^{m+1}}\bZ = \bZ$.
-
+%Since this implies $\delta \tilde w_2(c) = 0$ or $2$ mod 4
+%and furthermore $\delta (2\tilde w_2(c)) = 0$ mod 4,
+%one can safely define the Pontrjagin square $\tfrac{1}{8}\fP\big(2\tilde w_2(c)\big)$.\footnote{
+%	Be careful that this factor $2$ here is not the usual map sending $\{0,1\}=\bZ_2$ to $\{0,2\}\subset \bZ_4$.
+%	This time we are \textit{really} multiplying by $2$.
+%}
+%Note that this can naively be regarded as $2\cdot \tfrac{1}{4}\fP\big(w_2(c)\big)$ at the integral cochain level.
+%While the second term in the last line of \eqref{deltaPontrjagin} together with the overall factor takes value in
+%$\tfrac{(2^m)^2}{2^{m+1}}\bZ = 2^{m-1}\bZ = 2\bZ$ and dividing by two does not cause any trouble,
+%the first term does as it takes value in $\tfrac{2\cdot 2^m}{2^{m+1}}\bZ = \bZ$.
+
+\if0
 Let us take a closer look at the latter.
-The long exact sequence of cochain groups implies that $2\widetilde w_2(c)$ can be replaced by
-$\widetilde v_2(c)$, which is a cocycle mod 4.
+The long exact sequence of cochain groups implies that $2\tilde w_2(c)$ can be replaced by
+$\tilde v_2(c)$, which is a cocycle mod 4.
 Then the term of interest is
 \begin{equation*}
-	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\widetilde v_2 \cup \widetilde v_2.
+	\dfrac{1}{8}\cdot 2\cdot 4\beta_2\tilde v_2 \cup \tilde v_2.
 \end{equation*}
@@
 \end{equation*}
+\fi
 

### 2021-07-01 paper.tex
minor change
appendix A...

@@
 \subsection{$\bZ_4$ 1-form symmetry}
-According to \cite[Appendix C.3]{Clement2002} and \cite[Eq.\,(6.3)]{Wan:2018bns}, it seems that we have
+According to \cite[Appendix C.3]{Clement2002} and \cite[Eq.\,(6.3)]{Wan:2018bns},  we have
 \begin{equation}
@@
 
-The corresponding invariant in 4d is simply \begin{equation}
+Therefore there is no anomaly in 4d,
+and the bordism invariants in 4d are given simply by \begin{equation}
 \exp(2\pi i \frac{p}{4} \int \frac12\fP(a) )
@@
 Exploiting the fact that $K(\bZ_2\times \bZ_2, 2) = K(\bZ_2, 2) \times K(\bZ_2, 2)$,
-it seems that we have
+ we have
 \begin{equation}
@@
 \subsubsection{Leray-Serre SS (preparatory)}
-For the various input of cohomology groups, see Appendix A of our WZW paper.
+For the various input of cohomology groups, see Appendix A of our WZW paper \cite{Lee:2020ojw}.
 For the fibration
 \begin{equation}
-	BSO(3)
+	B\SO(3)
 	\ \to\ 
-	B\left(SO(3)\times SO(3)\right)
+	B\left(\SO(3)\times \SO(3)\right)
 	=
-	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+	B\left(\tfrac{\SO(4)}{\bZ_2}\right)
 	\ \to\ 
-	BSO(3)
+	B\SO(3)
 \end{equation}
@@
 	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(BSO(3);H^q(BSO(3);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		E_2^{p,q}=H^p\big(B\SO(3);H^q(B\SO(3);\bZ)\big) && H^{p+q}(B\left(\tfrac{\SO(4)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
 		\begin{array}{c|ccccccccccccc}
@@
 \begin{equation}
-	BSU(2)
+	B\SU(2)
 	\ \to\ 
-	B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right)
+	B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right)
 	\ \to\ 
-	B\left(\tfrac{SO(4)}{\bZ_2}\right)
+	B\left(\tfrac{\SO(4)}{\bZ_2}\right)
 \end{equation}
@@
 	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(B\left(\tfrac{SO(4)}{\bZ_2}\right);H^q(BSU(2);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		E_2^{p,q}=H^p\big(B\left(\tfrac{\SO(4)}{\bZ_2}\right);H^q(B\SU(2);\bZ)\big) && H^{p+q}(B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
 		\begin{array}{c|ccccccccccccc}
@@
 		\hline
-		H^d(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ) & \bZ & 0 & 0 & \bZ_2^{\oplus 2} & \bZ^{\oplus 3} & 0 & \bZ_2^{\oplus 3} & \cdots\\
+		H^d(B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right);\bZ) & \bZ & 0 & 0 & \bZ_2^{\oplus 2} & \bZ^{\oplus 3} & 0 & \bZ_2^{\oplus 3} & \cdots\\
 		\hline
@@
 	\begin{array}{ccc}
-		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
+		E^2_{p,q}=H_p\big(B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
 		\begin{array}{c|c:cccccccccccc}
@@
 \subsubsection{Adams SS}
-According to our naive guess, the module $\tilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
+According to our naive guess, the module $\tilde H^\ast(B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5}$ consists of
 \begin{equation}
@@
 \begin{equation}
-	\tilde H^\ast(B\left(\tfrac{SO(4)\times SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
+	\tilde H^\ast(B\left(\tfrac{\SO(4)\times \SU(2)}{\bZ_2}\right);\bZ_2)_{\leq 5} = \colorA{J[2]} \oplus \colorC{J[2]} \oplus \colorB{\mathcal{A}_1/\!\!/\mathcal{E}_0[4]} \oplus \colorD{J[5]}.
 \end{equation}
@@
 
-\subsection{$[SO(4n'_c+2)\times SU(2n_f)]/\bZ_2$}
+\subsection{$[\SO(4n'_c+2)\times \SU(2n_f)]/\bZ_2$}
 \label{sec:so(2odd)}
 
-\subsubsection{Cohomology of $BPSO(4n'_c+2)$}
+\subsubsection{Cohomology of $B\SO(4n'_c+2)/\bZ_2$}
 Recalling that the $\bZ_2$ cohomology read off from \cite{KonoMimura1974}
@@
 \end{equation}
-and if we assume the suspension $\bar\theta: H^\ast(PSO(4n'_c+2);\bZ_2) \to H^\ast(BPSO(4n'_c+2);\bZ_2)$
+and if we assume the suspension $\bar\theta: H^\ast(\SO(4n'_c+2)/\bZ_2;\bZ_2) \to H^\ast(B\SO(4n'_c+2)/\bZ_2;\bZ_2)$
 to commute with Steenrod squares (which seems to be true according to Nishimoto-san's notes),
@@
 \begin{equation}
-	BSU(2n_f)
+	B\SU(2n_f)
 	\ \to\ 
-	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
+	B\left(\tfrac{\SO(4n'_c+2)\times \SU(2n_f)}{\bZ_2}\right)
 	\ \to\ 
-	BPSO(4n'_c+2)
+	B\SO(4n'_c+2)/\bZ_2
 \end{equation}
@@
 	\begin{array}{ccc}
-		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
+		E_2^{p,q}=H^p\big(B\SO(4n'_c+2)/\bZ_2;H^q(B\SU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{\SO(4n'_c+2)\times \SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
 		\begin{array}{c|ccccccccccccc}
@@
 	\begin{array}{c}
-		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
+		E^2_{p,q}=H_p\big(B\left(\tfrac{\SO(4n'_c+2)\times \SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
 		\begin{array}{c|c:cccccccccccc}

### 2021-07-02 paper.tex
ref on susy+higher form sym

@@
 It is satisfying to see that the duality action correctly preserves the behaviors `none', `anomaly' and `extension'.
+In the last couple of years, the study of higher symmetries and their anomalies of supersymmetric theories has seen some activity\footnote{%
+See e.g.~\cite{Tachikawa:2019dvq,Eckhard:2019jgg,Morrison:2020ool,Albertini:2020mdx,Apruzzi:2020zot,Cvetic:2020kuw,Gukov:2020btk,DelZotto:2020esg,DelZotto:2020sop,Bhardwaj:2020phs,Bhardwaj:2021pfz,Apruzzi:2021vcu,Cvetic:2021sxm,Apruzzi:2021phx,Bhardwaj:2021zrt,Buican:2021xhs,Braun:2021sex,Cvetic:2021maf}.},
+but mostly from the point of view of string theory or M-theory.
+The authors hope that this paper paves a way toward a more field-theoretical analysis of these matters.
 
